### 2014-06-06 Papers/ms.tex
Paper template

% Every Latex document starts with a documentclass command
\documentclass[a4paper, 11pt]{article}

% Load some packages
\usepackage{graphicx} % This allows you to put figures in
\usepackage{natbib}   % This allows for relatively pain-free reference lists
\usepackage[left=3cm,top=3cm,right=3cm]{geometry} % The way I like the margins

% This helps with figure placement
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\parindent=0cm

% Set values so you can have a title
\title{}
\author{Brendon J. Brewer}
\date{\today}

% Document starts here
\begin{document}

% Actually put the title in
\maketitle

\abstract{This is the abstract}

\section{Introduction}
Blah blah

\end{document}

### 2014-11-20 Papers/ms.tex
Paper

@@
 \title{}
-\author{Brendon J. Brewer}
-\date{\today}
-
+\title{Flexible trans-dimensional modelling of gravitational lenses}
+\author{Brendon J. Brewer and David Huijser}
+\date{Department of Statistics, The University of Auckland\\
+Private Bag 92019, Auckland 1142, New Zealand\\
+\vspace{0.3cm}
+{\tt bj.brewer@auckland.ac.nz}}
 % Document starts here
@@
 
-\abstract{This is the abstract}
+\abstract{Gravitational lensing is a powerful astrophysical tool for measuring
+masses}
 
 \section{Introduction}
-Blah blah
+
+\section{Source and Lens Models}
+
+\section{The Cosmic Horseshoe}
+
+\section{Other Systems}
 

### 2014-11-20 Papers/ms.tex
scattered words

--- 2014-06-06 Papers/ms.tex
@@
 \title{}
-\author{Brendon J. Brewer}
-\date{\today}
-
+\title{Flexible trans-dimensional modelling of gravitational lenses}
+\author{Brendon J. Brewer$^1$, David Huijser$^1$, and
+Geraint F. Lewis$^2$}
+\date{\small $^1$ Department of Statistics, The University of Auckland\\
+Private Bag 92019, Auckland 1142, New Zealand\\
+$^2$ Sydney Institute for Astrophysics\\
+\vspace{1cm}
+{\tt bj.brewer@auckland.ac.nz}}
 % Document starts here
@@
 
-\abstract{This is the abstract}
+\abstract{Gravitational lensing is a powerful astrophysical tool for studying
+the distribution of matter in galaxies.}
 
 \section{Introduction}
-Blah blah
+
+\subsection{The hunt for dark substructures}
+{\bf Review of what's been done in this area. How was it done, and what do
+people believe?}
+
+\section{Source and Lens Models}
+Many different approaches have been applied to gravitational lens modelling.
+Any such method will involve many choices, such as:
+\begin{itemize}
+\item Whether to use a simply parameterized (e.g. Sersic)
+or flexible (e.g. pixellated)
+model for the surface brightness profile of the source
+\item Whether to use a simply parameterized or flexible
+model for the mass profile of the lens
+\item How to compute the results (e.g. optimization methods, Markov Chain
+Monte Carlo)
+\end{itemize}
+
+All such choices involve tradeoffs between convenience and realism.
+
+\section{The Cosmic Horseshoe}
+We demonstrate the method on the Cosmic Horseshoe INT data.
+
+\section{ER 0047-2808}
+We demonstrate the method on the HST images of ER 0047-2808.
 

### 2014-12-08 Papers/ms.tex
David's edits

@@
 \usepackage{graphicx} % This allows you to put figures in
+\usepackage{epstopdf}
 \usepackage{natbib}   % This allows for relatively pain-free reference lists
 \usepackage[left=3cm,top=3cm,right=3cm]{geometry} % The way I like the margins
+
+\usepackage{caption}
+\usepackage{subcaption} % subfigures
+\usepackage{float}
 
@@
 \section{The Cosmic Horseshoe}
-We demonstrate the method on the Cosmic Horseshoe INT data.
+As a demonstration the method is the applied to the Cosmic Horseshoe INT data. 
+The field of view of the image is $15.3180" \times 15.3180"$, and the size is $46 \times 46$ pixels, therefore one pixel is equivalent to $0.33"$. \\
+The method discussed  in the previous section is applied to two models, the first model consist of a flexible source and a Singular Isothermal Elliptical(SIE) model for the lens.
+This model is similar to models used in previous work \cite{Belokurov2007} \cite{Dye2008}.
+The second model has in addition to the flexible source and SIE, also possible satellites. \\
+The amount of added satellites is automatically determined by the program.
+If models the addition of an satellite galaxies gives a higher probability it will be preferred over then model without satellite galaxies.
+\\
+In both models the SIE is specified by the usual parameters: the location of the NIE ($x_c$,$y_c$), b, axis ratio $f$\footnote{in the code denoted with $q$},  the core radius$\zeta$, $\theta$, shear $\gamma$, and $\theta_{\gamma}$ \cite{kormann_schneider_1994}.\\
+One of the firsts step in applying Bayesian analysis is providing good prior distribution for the parameters. 
+The chosen prior probability distributions are displayed in table \ref{table:1}. The parameters which are not listed in table 
+\ref{table:1} depend on parameters which are listed.
+
+\begin{table}
+\centering
+\begin{tabular}{ l l}
+parameter    &  expression        \\  
+\hline 
+b            &  $exp\left(  log_{10}(10^{-3})+  log_{10}(10^{3})\cdot Unif(0,1) \right)\cdot scale  $ \\
+q            &  $0.05 + 0.95\cdot Unif(0,1) $ \\
+$x_c$       &  $0.5\cdot (x_{max} + x_{min}) +   0.1 \cdot(x_{max} - x_{min}) \cdot tan(\pi\cdot ( Unif(0,1) - 0.5)  )$ \\
+$		y_c$  &  $0.5\cdot (y_{max} + y_{min}) + 0.1\cdot (y_{max} - y_{min}) \cdot tan(\pi\cdot (Unif(0,1)  - 0.5)  ) $\\
+%rc           &  if $\left\{
+%  \begin{array}{l l}
+%    \textrm{singular} & \quad bb\\
+ %   \textrm{non-singular} & \quad  bb
+  %\end{array} \right.$
+rc(singular)   & $10^{-7}\cdot scale$ \\
+rc(non-singular)   & $  exp\left(log_{10}(10^{-3})+  log_{10}(10^{3})\cdot Unif(0,1)\right) \cdot scale   $\\
+$\theta$   & $\pi \cdot Unif(0,1)$\\
+shear      & $0.05 \cdot tan(\pi \cdot 0.5 \cdot Unif(0,1)) $\\
+$theta_{shear}$  & $ \pi\cdot Unif(0,1)$ \\
+\end{tabular}
+\parbox{0.75\linewidth}{\caption{Prior probabilities distribution for NIE parameters, where the scale parameter depends on <something> \label{table:1} }}
+
+\end{table}
+
+ \begin{figure}[!h]
+ \hspace{20pt}
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=0.75\linewidth,angle=90]{log_mass_SIE_no_blobs.eps}
+\parbox{0.8\linewidth}{\caption{The log of the SIE mass within the critical curve  for model A.  \label{fig:sub1} }}
+\end{subfigure}%
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=0.75\linewidth,angle=90]{log_mass_SIE.eps}
+   \parbox{0.8\linewidth}{\caption{The log of the SIE mass within the critical curve for model B.   \label{fig:sub2}}}
+\end{subfigure}
+   \end{figure}
+
+After choosing the prior probabilities one has to initialized the Dnest-code, which mean incorporating the problem specific information for
+ example dimensions of the images in pixels, image size in arc-seconds, information on the PSF etc in the metadata file. 
+ Besides these problem specific parameters, there are also several other parameters concerning the performance of code which need to be
+  edited in the OPTION file. After these initialization, we ran a test run to explore the amount of necessary levels, and length of the run.
+ A sufficiently amount of levels correlates with good degree of mixing, and the length of the run is associated with the larger sample
+  size.
+After one test run, the amount levels was adapted to 120, and the amount iterations was change to 5000 iterations, for model A this resulted in the effective sample size of 940, and for model B this resulted in the effective sample size of 757.
+The difference between the effective sample size is not unexpected, since the probability space which can be explored by applying model B much larger.
+\\
+Throughout the paper the standard cosmology was used for the analysis:  $H_0=70 \rm{km~s^{-1} ~pc^{-1}}$,  $\Omega_m = 0.3$,and  $\Omega_\Lambda= 0.7$. 
+The first test would to compare the SIE-mass of the models with the mass obtained in previous  work \cite{Belokurov2007} \cite{Dye2008}.
+Using model A the median  calculated SIE mass within the critical curve in solar masses is  $(5.34 \pm 0.046) \cdot 10^{12} M_\odot$, % (using median + STDDEV)
+which is comparable with previous work which gave the enclosed (cylindriacal) mass $(5.4 \pm 0.09) \cdot 10^{12} M_\odot$ \cite{Belokurov2007} and  mass within the Einstein-ring $(5.02 \pm 0.09) \cdot 10^{12} M_\odot$ \cite{Dye2008}.
+Figure \ref{fig:sub1} displays the histogram of the enclosed mass within an Einstein ring of $5"$, it displays a very well confined probability distribution of the mass.
+\\
+Using model B the median calculated SIE mass within the critical curve in solar masses is  $(5.34 \pm 0.046) \cdot 10^{12} M_\odot$, % (using median + STDDEV)
+which is slightly smaller compared to the masses obtained with model A and the masses from previous work mentioned above.
+Which is also not unexpected, because models where the SIE-mass is smaller can compensate by adding a satellite near by.
+Therefore the distribution is much wider as one can see in figure \ref{fig:sub2}.
+The median of the SIE-mass in model B is $(4.79 \pm 1.66) \cdot 10^{12} M_\odot$, which leaves a large numerical uncertainty.
+However by comparison of the two histograms in figure \ref{fig:1} it is apparent that the distribution has a strong feature at the location.
+\\
+
+\begin{figure}[!h]
+\hspace{5pt}
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=0.7\linewidth,angle=90]{log_total_mass_blob.eps}
+\parbox{0.8\linewidth}{\caption{The log of the total mass of the satellites for model B.   \label{fig:sub3}}}
+\end{subfigure}%
+\hspace{-15pt}
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \vspace{6pt}
+  \includegraphics[width=0.7\linewidth,angle=90]{log_total_mass_blobs_within_ring.eps}
+\parbox{0.8\linewidth}{\caption{The log of the total mass of the satellites within the fixed Einstein-radius for model B.  \label{fig:sub4} }}
+\end{subfigure}
+   \end{figure}
+\vspace{-15pt}
+\noindent Another interesting aspect is the mass of the satellites.
+Figure \ref{fig:sub3} displays a histogram of the logarithm of the total mass of the satellites per sample.
+Figure \ref{fig:sub4} displays histogram of the logarithm of the total mass of the satellites within a radius of $ 5"$ from the centre of images per sample.
+Comparing these two images reveals that large part the massive satellites lie outside the Einstein ring.
+The satellites at a larger distance can only influence the images if they are more massive.
+Figure \ref{fig:sub5} display a histogram of the log of the total mass of the SIE and the satellites within the Einstein radius, which clearly looks very similar to \ref{fig:sub1}.
+Figure \ref{fig:sub6} display a plot of the total mass of the SIE versus mass of the satellites within the Einstein radius whichs  negative correlation of approximately 
+\begin{equation}
+ \sum M_{satellites} = 5\cdot10^{12} - M_{SIE}
+ \end{equation}
+
+The main conclusion of the analysis of the datasets of model A and model B, would be that the application of the DNest code with a free amount of satellite galaxies return a well matching model which is very similar to to the model without any satellites, this proves
+even though the code has the freedom the explore and create all sort of models, it confirms that the already known distribution is very probable.
+This shows how well the code works, and beside that it is also good indication that the well established SIE model for this system doesn't need additional satellites to explain the system.
+
+\begin{figure}
+\hspace{10pt}
+\begin{subfigure}{.5\textwidth}
+\vspace{-12pt}
+  \centering
+  \includegraphics[width=0.75\linewidth,angle=90]{mass_SIE_plus_blob_mass.eps}
+\parbox{0.8\linewidth}{\caption{The log of add mass of the satellites and SIE within the fixed Einstein-radius for model B.   \label{fig:sub5}}}
+\end{subfigure}
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=0.75\linewidth,angle=90]{joint.eps}
+\parbox{0.8\linewidth}{\caption{Plot of the log of the total mass of the satellites within the fixed Einstein-radius versus the 
+log of the SIE mass within the Einstein radius for model B.  \label{fig:sub6} }}
+\end{subfigure}
+
+   \end{figure}
 

### 2014-12-12 MyModel.cpp
Print out unblurred images

@@ -124,6 +124,10 @@ void MyModel::print(std::ostream& out) const
 		for(size_t j=0; j<xs[i].size(); j++)
 			out<<source.evaluate(x[i][j], y[i][j])<<' ';
 
+	for(size_t i=0; i<xs.size(); i++)
+		for(size_t j=0; j<xs[i].size(); j++)
+			out<<surface_brightness[i][j]<<' ';
+
 	for(size_t i=0; i<model_image.size(); i++)
 		for(size_t j=0; j<model_image[i].size(); j++)
 			out<<model_image[i][j]<<' ';

### 2014-12-12 display.py

@@ -52,15 +52,23 @@ for i in xrange(0, output.shape[0]):
 	# Sersic source model parameters are columns 59-65
 	src = x[468:468 + metadata[0]*metadata[1]*metadata[7]**2]
 	src = src.reshape((metadata[0]*metadata[7], metadata[1]*metadata[7]))
-	img = x[468 + (metadata[0]*metadata[1]*metadata[7]**2):-2]
-	img = img.reshape((metadata[0], metadata[1]))
 
-	subplot(2,2,1)
+	img1 = x[468 + metadata[0]*metadata[1]*metadata[7]**2:468 + 2*metadata[0]*metadata[1]*metadata[7]**2]
+	img1 = img1.reshape((metadata[0]*metadata[7], metadata[1]*metadata[7]))
+
+	img2 = x[468 + 2*metadata[0]*metadata[1]*metadata[7]**2:-2]
+	img2 = img2.reshape((metadata[0], metadata[1]))
+
+	subplot(2,3,1)
 	imshow(src, interpolation='nearest')
 	title('Model Source ' + str(i+1))
 
-	subplot(2,2,2)
-	imshow(img, interpolation='nearest')
+	subplot(2,3,2)
+	imshow(img1, interpolation='nearest')
+	title('Unblurred Image ' + str(i+1))
+
+	subplot(2,3,3)
+	imshow(img2, interpolation='nearest')
 	hold(True)
 	# Plot center of NIE
 	plot(x_nie, y_nie, 'yo', markersize=10)
@@ -76,8 +84,8 @@ for i in xrange(0, output.shape[0]):
 	title('Data')
 
 	subplot(2,2,4)
-	sigma = sqrt(sig**2 + x[0]**2 + x[1]*img)
-	imshow((img - data)/sigma, interpolation='nearest')
+	sigma = sqrt(sig**2 + x[0]**2 + x[1]*img2)
+	imshow((img2 - data)/sigma, interpolation='nearest')
 	title('Standardised Residuals')
 	draw()
 
@@ -86,7 +94,7 @@ for i in xrange(0, output.shape[0]):
 		print('Frames/' + '%0.4d'%(i+1) + '.png')
 
 	total += src
-	magnification[i] = 2.5*log10(metadata[7]**2*img.sum()/src.sum())
+	magnification[i] = 2.5*log10(metadata[7]**2*img2.sum()/src.sum())
 
 ioff()
 show()

### 2014-12-13 Papers/ms.tex
MNRAS format

@@
-% Every Latex document starts with a documentclass command
-\documentclass[a4paper, 11pt]{article}
+\documentclass[useAMS,usenatbib]{mn2e}
 
-% Load some packages
-\usepackage{graphicx} % This allows you to put figures in
-\usepackage{epstopdf}
-\usepackage{natbib}   % This allows for relatively pain-free reference lists
-\usepackage[left=3cm,top=3cm,right=3cm]{geometry} % The way I like the margins
+\voffset=-0.8in
+
+% Packages:
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{xspace}
+\usepackage{dsfont}
 
@@
 
-% This helps with figure placement
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\textfraction}{0.1}
-\parindent=0cm
+\title[]
+{Lensing}
 
-% Set values so you can have a title
-\title{}
-\title{Flexible trans-dimensional modelling of gravitational lenses}
-\author{Brendon J. Brewer$^1$, David Huijser$^1$, and
-Geraint F. Lewis$^2$}
-\date{\small $^1$ Department of Statistics, The University of Auckland\\
-Private Bag 92019, Auckland 1142, New Zealand\\
-$^2$ Sydney Institute for Astrophysics\\
-\vspace{1cm}
-{\tt bj.brewer@auckland.ac.nz}}
-% Document starts here
+\author[Brewer, Huijser and Lewis]{%
+  Brendon~J.~Brewer$^{1}$\thanks{bj.brewer@auckland.ac.nz},
+  David Huijser$^{1}$,
+  Geraint F. Lewis$^2$
+  \medskip\\
+  $^1$Department of Statistics, The University of Auckland, Private Bag 92019, Auckland 1142, New Zealand\\
+  $^2$Sydney Institute for Astronomy}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 
-% Actually put the title in
+\date{To be submitted to MNRAS}
+
 \maketitle
 
-\abstract{Gravitational lensing is a powerful astrophysical tool for studying
-the distribution of matter in galaxies.}
+\label{firstpage}
+
+\begin{abstract}
+Gravitational lensing is a powerful astrophysical tool for studying
+the distribution of matter in galaxies.
+\end{abstract}
+
+\begin{keywords}
+methods: data analysis --- methods: statistical
+\end{keywords}
 

### 2014-12-13 Papers/ms.tex
A bit of writing

@@
 \usepackage{dsfont}
-
+\usepackage[utf8]{inputenc}
 \usepackage{caption}
@@
   $^1$Department of Statistics, The University of Auckland, Private Bag 92019, Auckland 1142, New Zealand\\
-  $^2$Sydney Institute for Astronomy}
+  $^2$Sydney Institute for Astronomy, School of Physics, A28,
+  The University of Sydney, NSW 2006, Australia}
 
@@
 \begin{abstract}
-Gravitational lensing is a powerful astrophysical tool for studying
-the distribution of matter in galaxies.
 \end{abstract}
@@
 \section{Introduction}
+Strong gravitational lensing is a powerful astrophysical tool for studying
+the distribution of matter, including dark matter, in galaxies
+\citep{treu}.
 
@@
 \section{Source and Lens Models}
-Many different approaches have been applied to gravitational lens modelling.
-Any such method will involve many choices, such as:
+Many different approaches have been proposed and applied to gravitational lens
+modelling. These approaches 
 \begin{itemize}
-\item Whether to use a simply parameterized (e.g. Sersic)
-or flexible (e.g. pixellated)
-model for the surface brightness profile of the source
-\item Whether to use a simply parameterized or flexible
-model for the mass profile of the lens
+\item Whether to use a simply parameterized (e.g. Sérsic)
+or flexible (e.g. pixellated) model for the surface brightness profile of the source
+\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid)
+or flexible model (e.g. pixellated) for the mass profile of the lens
 \item How to compute the results (e.g. optimization methods, Markov Chain
@@
 All such choices involve tradeoffs between convenience and realism.
+In a previous paper \citep{2011MNRAS.412.2521B} we argued that an ideal
+modelling approach lies somewhere between simply-parameterised and
+pixellated models. Simply parameterized models, such as Sérsic surface
+brightness profiles for the source, and SIE models for the lens, are convenient,
+they are clearly simplifications, and can produce misleading results if the
+simple profiles are not a good approximation to the actual situation. On the
+other hand, pixellated models for the source \citep[e.g.][]{suyu} or the lens
+\citep[e.g.][]{2014MNRAS.445.2181C} can in principle represent ``any''
+source surface brightness profile or lens density profile. However, the prior
+distribution over pixel values is often chosen for mathematical convenience
+\citep{2003ApJ...590..673W} and can assign virtually zero prior probability
+to the hypothesis that the source actually looks like a galaxy.
 
@@
 
+\begin{thebibliography}{99}
+\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
+\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011,
+Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380
+
+\bibitem[\protect\citeauthoryear{Brewer et al.}{2011}]{2011MNRAS.412.2521B} 
+Brewer B.~J., Lewis G.~F., Belokurov V., Irwin M.~J., Bridges T.~J., Evans 
+N.~W., 2011, MNRAS, 412, 2521
+
+\bibitem[\protect\citeauthoryear{Brewer}{2014}]{rjobject} Brewer, B. J., 2014,
+Bayesian Analysis, submitted. ArXiv: 1411.3921
+
+\bibitem[\protect\citeauthoryear{Coles, Read, 
+\& Saha}{2014}]{2014MNRAS.445.2181C} Coles J.~P., Read J.~I., Saha P., 2014, MNRAS, 445, 2181
+
+\bibitem[\protect\citeauthoryear{O'Hagan and Forster}{2004}]{ohagan}
+O'Hagan, A., Forster,~J., 2004, Bayesian inference. London: Arnold.
+
+\bibitem[\protect\citeauthoryear{Sivia \& Skilling}{2006}]{sivia} Sivia, 
+D.~ S., Skilling, J., 2006, Data Analysis: A Bayesian Tutorial, 2nd 
+Edition, Oxford University Press
+
+\bibitem[\protect\citeauthoryear{Skilling}{2006}]{skilling} Skilling, 
+J., 2006, ``Nested Sampling for General Bayesian Computation'', Bayesian 
+Analysis 4, pp. 833-860
+
+\bibitem[\protect\citeauthoryear{Suyu et al.}{2006}]{suyu} 
+Suyu S.~H., Marshall P.~J., Hobson M.~P., Blandford R.~D., 2006, MNRAS, 
+371, 983
+
+\bibitem[\protect\citeauthoryear{Treu}{2010}]{treu} Treu T., 2010, ARA\&A, 48, 87
+
+\bibitem[\protect\citeauthoryear{Warren 
+\& Dye}{2003}]{2003ApJ...590..673W} Warren S.~J., Dye S., 2003, ApJ, 590, 673
+\end{thebibliography}
+
 \end{document}

### 2014-12-13 Papers/ms.tex
Three papers

@@
 \begin{abstract}
+
 \end{abstract}
@@
 \subsection{The hunt for dark substructures}
+In recent years, several galaxy-galaxy lens systems have been discovered which
+are thought to contain at least one dark substructure
+\citep{vegetti1, vegetti2, vegetti3}.
+
 {\bf Review of what's been done in this area. How was it done, and what do
@@
 
+\bibitem[\protect\citeauthoryear{Vegetti et 
+al.}{2012}]{vegetti1} Vegetti S., Lagattuta D.~J., McKean J.~P., 
+Auger M.~W., Fassnacht C.~D., Koopmans L.~V.~E., 2012, Natur, 481, 341
+
+\bibitem[\protect\citeauthoryear{Vegetti et 
+al.}{2010}]{vegetti2} Vegetti S., Koopmans L.~V.~E., Bolton A., 
+Treu T., Gavazzi R., 2010, MNRAS, 408, 1969
+
+\bibitem[\protect\citeauthoryear{Vegetti, Czoske, 
+\& Koopmans}{2010}]{vegetti3} Vegetti S., Czoske O., Koopmans L.~V.~E., 2010, MNRAS, 407, 225
+
 \bibitem[\protect\citeauthoryear{Warren 

### 2015-01-19 Papers/ms.tex
Tinkering

@@
 \section{Introduction}
-Strong gravitational lensing is a powerful astrophysical tool for studying
+Galaxy-galaxy lensing is a powerful astrophysical tool for studying
 the distribution of matter, including dark matter, in galaxies
@@
 
-\subsection{The hunt for dark substructures}
-In recent years, several galaxy-galaxy lens systems have been discovered which
+In recent years, several lens systems have been discovered which
 are thought to contain at least one dark substructure
 \citep{vegetti1, vegetti2, vegetti3}.
+
+In this paper we address the topic of inferring the matter distribution in the
+lens galaxy from the lensed, blurred image.
 

### 2015-02-02 Papers/ms.tex
Put PGM in paper
Blobs

@@
 to the hypothesis that the source actually looks like a galaxy.
+
+\section{The Model}
+The surface brightness profile of the source is assumed to be composed of
+a sum of a finite number of ``blobs'', or circular basis functions.
+The surface brightness of a single blob centered at the origin
+is:
+\begin{eqnarray}
+f(x, y) &=& \left\{
+\begin{array}{lr}
+\frac{A}{2\pi w^2}\left[1 - \left(\frac{r}{w}\right)^2\right], & r \leq w\\
+0, & \textnormal{otherwise}
+\end{array}
+\right.
+\end{eqnarray}
+where $r = \sqrt{x^2 + y^2}$, $w$ is the width of the blob, and $A$ is the
+total flux of the blob (i.e. the integral of the surface brightness).
+These basis functions are faster to evaluate than gaussians, since they do not
+contain an exponential function. In addition, the finite support means that
+each blob will evaluate to zero over a large fraction of the domain which
+confers an additional speed advantage.
+
+\begin{figure*}
+\includegraphics{pgm.pdf}
+\caption{A probabilistic graphical model (PGM) of the dependence structure
+of the prior information.\label{fig:pgm}}
+\end{figure*}
 

### 2015-02-03 Papers/ms.tex
Sum of N Blobs
Lens blobs

@@
 \section{The Model}
+
+\subsection{The Source}
 The surface brightness profile of the source is assumed to be composed of
@@
 
+If our model contains $N_{\rm src}$ such blobs, positioned at
+$\left\{(x_i, y_i)\right\}$ with widths $\{w_i\}$ and total fluxes
+$\{A_i\}$, the overall surface brightness profile is:
+\begin{eqnarray}
+f(x, y) &=& \sum_{i=1}^{N_{\rm src}}\left\{
+\begin{array}{lr}
+\frac{A_i}{2\pi w_i^2}\left[1 - \left(\frac{r_i}{w_i}\right)^2\right], & r_i \leq w_i\\
+0, & \textnormal{otherwise}
+\end{array}
+\right.
+\end{eqnarray}
+where $r_i = \sqrt{(x - x_i)^2 + (y - y_i)^2}$.
+
 \begin{figure*}
@@
 \end{figure*}
+
+\subsection{The Lens}
+
+The NIE parameters...
+
+A lensing blob with mass $M$ and width $v$
+centered at the origin has the following surface mass density profile:
+\begin{eqnarray}
+\rho(x, y) &=& \left\{
+\begin{array}{lr}
+\frac{M}{2\pi v^2}\left[1 - \left(\frac{r}{v}\right)^2\right], & r \leq v\\
+0, & \textnormal{otherwise}
+\end{array}
+\right.
+\end{eqnarray}
+The deflection angles are:
 

### 2015-02-17 Papers/ms.tex
Talking about simply parameterised and freeform models

@@
 the distribution of matter, including dark matter, in galaxies
-\citep{treu}.
-
-In recent years, several lens systems have been discovered which
+\citep{treu}. In recent years, several lens systems have been discovered which
 are thought to contain at least one dark substructure
@@
 pixellated models. Simply parameterized models, such as Sérsic surface
-brightness profiles for the source, and SIE models for the lens, are convenient,
-they are clearly simplifications, and can produce misleading results if the
-simple profiles are not a good approximation to the actual situation. On the
+brightness profiles for the source, and SIE models for the lens, are very
+convenient. They only have a few adjustable parameters, and they capture
+(to ``first order'') relevant prior information that we have about the
+source and lens profiles. Of course, they are clearly simplifications,
+and can produce misleading results if the actual profile is very different
+from any member of the assumed family.
+
+On the
 other hand, pixellated models for the source \citep[e.g.][]{suyu} or the lens
@@
 source surface brightness profile or lens density profile. However, the prior
-distribution over pixel values is often chosen for mathematical convenience
-\citep{2003ApJ...590..673W} and can assign virtually zero prior probability
-to the hypothesis that the source actually looks like a galaxy.
+distribution over pixel values is often chosen to be a multivariate gaussian
+for mathematical reasons, so
+that the source can be analytically marginalized over
+\citep{2003ApJ...590..673W}. Unfortunately, a multivariate gaussian prior
+over pixel intensities can correspond to a very poor model of our prior
+beliefs about the source. It assigns virtually zero prior probability
+to the hypothesis that the source actually looks like a galaxy, and very high
+prior probability to the hypothesis that the source looks like noise (or
+blurred noise).
 

### 2015-02-18 Papers/ms.tex
Another paragraph

@@
 All such choices involve tradeoffs between convenience and realism.
-In a previous paper \citep{2011MNRAS.412.2521B} we argued that an ideal
-modelling approach lies somewhere between simply-parameterised and
-pixellated models. Simply parameterized models, such as Sérsic surface
+Simply parameterized models, such as Sérsic surface
 brightness profiles for the source, and SIE models for the lens, are very
@@
 blurred noise).
+
+In a previous paper \citep{2011MNRAS.412.2521B} we argued that an ideal
+modelling approach lies somewhere between simply-parameterised and
+pixellated models. The source and the lens can be built up from a moderate
+number of simply parameterised components. For the source, this allows
+us to incorporate prior knowledge about the local correlations (the surface
+brightness at any particular point is likely to be similar to that at a
+nearby point) and the fact that most of the sky is dark. For the lens, if
+we are interested in detecting and measuring the properties of dark
+substructures, a superposition of an unknown number of ``blobs'' is the
+relevant model.
 

### 2015-02-18 Papers/ms.tex
Writing in the intro

@@
 are thought to contain at least one dark substructure
-\citep{vegetti1, vegetti2, vegetti3}.
-
-In this paper we address the topic of inferring the matter distribution in the
-lens galaxy from the lensed, blurred image.
-
-{\bf Review of what's been done in this area. How was it done, and what do
-people believe?}
-
-\section{Source and Lens Models}
-Many different approaches have been proposed and applied to gravitational lens
-modelling. These approaches 
-\begin{itemize}
-\item Whether to use a simply parameterized (e.g. Sérsic)
+\citep{vegetti1, vegetti2, vegetti3}. In this paper we address the topic of
+inferring the matter distribution in the lens galaxy from the lensed,
+blurred image. These approaches may be categorized according to
+Whether to use a simply parameterized (e.g. Sérsic)
 or flexible (e.g. pixellated) model for the surface brightness profile of the source
@@
 \item How to compute the results (e.g. optimization methods, Markov Chain
-Monte Carlo)
-\end{itemize}
 
-All such choices involve tradeoffs between convenience and realism.
+Many different approaches have been proposed and applied to
+this problem. The differences between the approaches can be broken down into
+i) different assumptions about the prior information being used, and ii)
+different computational methods used to compute the results.
+Each approach involves tradeoffs between convenience and realism.
 Simply parameterized models, such as Sérsic surface

### 2015-02-24 Papers/ms.tex
Starting to discuss RJObject

@@
 brightness at any particular point is likely to be similar to that at a
-nearby point) and the fact that most of the sky is dark. For the lens, if
-we are interested in detecting and measuring the properties of dark
-substructures, a superposition of an unknown number of ``blobs'' is the
-relevant model.
+nearby point) and the fact that most of the sky is dark.
+
+For the lens, if we are interested in detecting and measuring the properties of
+dark substructures, a superposition of an unknown number of ``blobs'' is the
+relevant model. In addition, if we want to constrain the ``mass function'' of
+these blobs, we will need a hierarchical model which specifies the probability
+distribution for the masses, given some hyperparameters.
+
+Computing the posterior distribution over the parameters of such a model
+requires that we can implement Markov Chain Monte Carlo (MCMC) over the space
+of possible sources and lenses. In a recent paper,
 
@@
 \bibitem[\protect\citeauthoryear{Brewer}{2014}]{rjobject} Brewer, B. J., 2014,
-Bayesian Analysis, submitted. ArXiv: 1411.3921
+preprint. ArXiv: 1411.3921
 

### 2015-05-15 Papers/ms.tex
A little bit of writing

@@
 the distribution of matter, including dark matter, in galaxies
-\citep{treu}. In recent years, several lens systems have been discovered which
-are thought to contain at least one dark substructure
-\citep{vegetti1, vegetti2, vegetti3}. In this paper we address the topic of
+\citep{treu}. It holds substantial potential as a technique for discovering
+and measuring the properties of dark matter substructures \citep{koopmans}.
+In recent years, this potential has been realised in several lens systems
+which are thought to contain at least one dark substructure
+\citep{vegetti1, vegetti2, vegetti3}.
+
+In this paper we address the topic of
 inferring the matter distribution in the lens galaxy from the lensed,
-blurred image. These approaches may be categorized according to
-Whether to use a simply parameterized (e.g. Sérsic)
-or flexible (e.g. pixellated) model for the surface brightness profile of the source
+blurred image. These approaches may be categorized according to the following
+criteria:
+\begin{enumerate}
+\item Whether to use a simply parameterized (e.g. Sérsic), moderately flexible
+(e.g. mixture model, \citet{2011MNRAS.412.2521B})
+or free-form (e.g. pixellated) model for the surface brightness profile of the source
 \item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid)
@@
 
+\bibitem[\protect\citeauthoryear{Koopmans}{2005}]{koopmans} 
+Koopmans L.~V.~E., 2005, MNRAS, 363, 1136
+
 \bibitem[\protect\citeauthoryear{O'Hagan and Forster}{2004}]{ohagan}

### 2015-05-16 Papers/ms.tex
end enumerate
Working title
MOre references

@@
 \title[]
-{Lensing}
+{Trans-Dimensional Inference for Gravitational Lens Substructures}
 
@@
 \item How to compute the results (e.g. optimization methods, Markov Chain
+Monte Carlo with or without source parameters marginalized out).
+\end{enumerate}
 
 Many different approaches have been proposed and applied to
-this problem. The differences between the approaches can be broken down into
+this problem. Recent sophisicated approaches to
+this problem include \citet{2014MNRAS.445.2181C},
+\citet{2015arXiv150500198T}, and
+\citet{2015arXiv150407629B}. {\bf todo: actually comment
+on what's in these papers}.
+
+The differences between the approaches can be broken down into
 i) different assumptions about the prior information being used, and ii)
@@
 requires that we can implement Markov Chain Monte Carlo (MCMC) over the space
-of possible sources and lenses. In a recent paper,
+of possible sources and lenses.
 
@@
 The deflection angles are:
+
+Since the model is not of fixed dimension (the number of source and lens
+``blobs'' is unknown), we implemented the MCMC using the {\tt RJObject}
+\citep{rjobject} software, a C++ library for implementing trans-dimensional
+MCMC with hierarchically-specified priors, and doing the sampling with the
+Diffusive Nested Sampling algorithm \citep{dnest}. Previous astronomical
+applications of {\tt RJObject} include \citet{magnetron}
+and~\ref{exoplanet}.
 
@@
 \begin{thebibliography}{99}
+\bibitem[\protect\citeauthoryear{Birrer, Amara, 
+\& Refregier}{2015}]{2015arXiv150407629B} Birrer S., Amara A., Refregier A., 2015, arXiv, arXiv:1504.07629
+
 \bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
@@
 
+\bibitem[\protect\citeauthoryear{Brewer 
+\& Donovan}{2015}]{exoplanet} Brewer B.~J., Donovan C.~P., 2015, MNRAS, 448, 3206
+
 \bibitem[\protect\citeauthoryear{Coles, Read, 
 \& Saha}{2014}]{2014MNRAS.445.2181C} Coles J.~P., Read J.~I., Saha P., 2014, MNRAS, 445, 2181
+
+\bibitem[\protect\citeauthoryear{Huppenkothen et 
+al.}{2015}]{magnetron} Huppenkothen D., et al., 2015, arXiv, 
+arXiv:1501.05251
 
@@
 
+\bibitem[\protect\citeauthoryear{Tagore 
+\& Jackson}{2015}]{2015arXiv150500198T} Tagore A.~S., Jackson N., 2015, arXiv, arXiv:1505.00198
+
 \bibitem[\protect\citeauthoryear{Treu}{2010}]{treu} Treu T., 2010, ARA\&A, 48, 87

### 2015-05-18 Papers/pgm.py
source --> src

@@ -42,7 +42,7 @@ pgm.add_edge('sigma', 'data')
 pgm.add_edge('nie', 'data')
 
 # Add the plates
-pgm.add_plate(daft.Plate([-1., -1., 2., 2.], label=r'Source Blobs \newline $i=1, ..., N_{\rm source}$'))
+pgm.add_plate(daft.Plate([-1., -1., 2., 2.], label=r'Source Blobs \newline $i=1, ..., N_{\rm src}$'))
 
 # Add the plates
 pgm.add_plate(daft.Plate([3., -1., 2., 2.], label=r'Lens Blobs \newline $i=1, ..., N_{\rm lens}$'))

### 2015-05-18 Papers/ms.tex
citep, not ref
Lists of parameters

@@
 Simply parameterized models, such as Sérsic surface
-brightness profiles for the source, and SIE models for the lens, are very
+brightness profiles for the source, and singular isothermal ellipsoid plus
+external shear (SIE+$\gamma$) models for the lens, are very
 convenient. They only have a few adjustable parameters, and they capture
@@
 \citep[e.g.][]{2014MNRAS.445.2181C} can in principle represent ``any''
-source surface brightness profile or lens density profile. However, the prior
+source surface brightness profile or lens projected density profile. However, the prior
 distribution over pixel values is often chosen to be a multivariate gaussian
@@
 prior probability to the hypothesis that the source looks like noise (or
-blurred noise).
+blurred noise). These priors also assign nonzero probability to negative
+surface brightness or density values.
 
-In a previous paper \citep{2011MNRAS.412.2521B} we argued that an ideal
+\citet{2011MNRAS.412.2521B} argued that an ideal
 modelling approach lies somewhere between simply-parameterised and
@@
 dark substructures, a superposition of an unknown number of ``blobs'' is the
-relevant model. In addition, if we want to constrain the ``mass function'' of
+most natural model. In addition, if we want to constrain the ``mass function'' of
 these blobs, we will need a hierarchical model which specifies the probability
-distribution for the masses, given some hyperparameters.
+distribution for the masses, conditional on some hyperparameters. Inferring the
+mass function of the blobs then reduces to calculating the posterior
+distribution for the hyperparameters.
 
@@
 The surface brightness profile of the source is assumed to be composed of
-a sum of a finite number of ``blobs'', or circular basis functions.
+a sum of a finite number of ``blobs'', or basis functions. The specific choice
+of basis functions we use is motivated primarily by computational speed.
 The surface brightness of a single blob centered at the origin
@@
 where $r = \sqrt{x^2 + y^2}$, $w$ is the width of the blob, and $A$ is the
-total flux of the blob (i.e. the integral of the surface brightness).
+total flux of the blob (i.e. the integral of the surface brightness over the
+entire domain).
 These basis functions are faster to evaluate than gaussians, since they do not
@@
 where $r_i = \sqrt{(x - x_i)^2 + (y - y_i)^2}$.
+
+Under these assumptions, the source can be described by the following
+parameters:
+
+\begin{eqnarray}
+\left\{
+N_{\rm src}, \left\{\mathbf{x}^{\rm src}_i\right\}_{i=1}^N
+\right\}
+\end{eqnarray}
+where $\mathbf{x}^{\rm src}_i$ denotes the parameters for source blob $i$:
+\begin{eqnarray}
+\mathbf{x}^{\rm src}_i &=& \left\{x_i, y_i, A_i, w_i
+\right\}.
+\end{eqnarray}
 
@@
 applications of {\tt RJObject} include \citet{magnetron}
-and~\ref{exoplanet}.
+and~\citep{exoplanet}.
 

### 2015-05-19 Papers/ms.tex
Deflection angles

@@
 If our model contains $N_{\rm src}$ such blobs, positioned at
-$\left\{(x_i, y_i)\right\}$ with widths $\{w_i\}$ and total fluxes
+$\left\{(x_i^{\rm src}, y_i^{\rm src})\right\}$ with widths $\{w_i\}$ and total fluxes
 $\{A_i\}$, the overall surface brightness profile is:
@@
 \end{eqnarray}
-where $r_i = \sqrt{(x - x_i)^2 + (y - y_i)^2}$.
+where $r_i = \sqrt{(x - x_i^{\rm src})^2 + (y - y_i^{\rm src})^2}$.
 
@@
 The deflection angles are:
+
+%Menc = 4.*components[i][2]/widthsq*(0.5*rsq -
+%				rsq*rsq/(4*widthsq));
+
+\begin{eqnarray}
+\alpha_x(x, y) &=&
+\left\{
+\begin{array}{lr}
+-\frac{\left[2(r/v)^2 - (r/v)^4\right]Mx}{r^3}, & r \leq v\\
+-\frac{Mx}{\pi r^3}, & \textnormal{otherwise}
+\end{array}
+\right.\\
+\alpha_y(x, y) &=&
+\left\{
+\begin{array}{lr}
+-\frac{\left[2(r/v)^2 - (r/v)^4\right]My}{r^3}, & r \leq v\\
+-\frac{My}{\pi r^3}, & \textnormal{otherwise}
+\end{array}
+\right.
+\end{eqnarray}
 

### 2015-06-06 Papers/ms.tex
David's figure fixes
RJObject para, Green reference

@@
 \usepackage{xspace}
-\usepackage{dsfont}
+%\usepackage{dsfont}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{float}
+
+\usepackage{epstopdf}
 
@@
 Since the model is not of fixed dimension (the number of source and lens
-``blobs'' is unknown), we implemented the MCMC using the {\tt RJObject}
-\citep{rjobject} software, a C++ library for implementing trans-dimensional
+``blobs'' is unknown), we used a trans-dimensional MCMC sampler based on
+reversible jump MCMC \citep{green}. We implemented the MCMC using the
+{\tt RJObject} software \citep{rjobject}, a C++ library for implementing trans-dimensional
 MCMC with hierarchically-specified priors, and doing the sampling with the
@@
 applications of {\tt RJObject} include \citet{magnetron}
-and~\citep{exoplanet}.
+and~\citep{exoplanet}. Proposal moves for the parameters (positions and masses
+of the source and lens blobs), and birth/death moves to add or remove blobs
+to the source or lens, are handled internally by {\tt RJObject}.
 
@@
 The method discussed  in the previous section is applied to two models, the first model consist of a flexible source and a Singular Isothermal Elliptical(SIE) model for the lens.
-This model is similar to models used in previous work \cite{Belokurov2007} \cite{Dye2008}.
+This model is has been used often  \cite{Dye2008}, \cite{schneider_falcoa_Ehlers_1994},      .
 The second model has in addition to the flexible source and SIE, also possible satellites. \\
@@
 
- \begin{figure}[!h]
- \hspace{20pt}
+ \begin{figure*}
+% \hspace{20pt}
 \begin{subfigure}{.45\textwidth}
@@
 \end{subfigure}
-   \end{figure}
+   \end{figure*}
 
@@
 
+\bibitem[\protect\citeauthoryear{Green}{1995}]{rjmcmc}
+Green, P.~J., 1995, Reversible Jump Markov Chain Monte Carlo Computation and Bayesian Model Determination, Biometrika 82 (4): 711–732.
+
 \bibitem[\protect\citeauthoryear{Huppenkothen et 

### 2015-06-06 Papers/ms.tex
SIE talk

@@
 \subsection{The Lens}
-
-The NIE parameters...
+The surface mass density profile of the lens is modelled as a superposition
+of a singular isothermal ellipsoid plus external shear (SIE+$\gamma$) and
+$N$ circular lens ``blobs''. The SIE+$\gamma$ has nine parameters:
+the (circularized) einstein radius $b$, axis ratio $q$, central position
+$(x_c, y_c)$, orientation angle $\theta$, the external shear $\gamma$, and the
+orientation angle of the external shear, $\theta_{\gamma}$. The SIE+$\gamma$
+is supposed to account for the bulk of the lensing effect. Of course, more
+general and flexible smooth models are possible. Ultimately, concentric
+mixtures of smooth components may be the most useful for realistic inference
+of the density profile of the halo.
 
@@
 \\
-In both models the SIE is specified by the usual parameters: the location of the NIE ($x_c$,$y_c$), b, axis ratio $f$\footnote{in the code denoted with $q$},  the core radius$\zeta$, $\theta$, shear $\gamma$, and $\theta_{\gamma}$ \cite{kormann_schneider_1994}.\\
+In both models the SIE is specified by the usual parameters: the location of the SIE ($x_c$,$y_c$), b, axis ratio $f$\footnote{in the code denoted with $q$},  the core radius$\zeta$, $\theta$, shear $\gamma$, and $\theta_{\gamma}$ \cite{kormann_schneider_1994}.\\
 One of the firsts step in applying Bayesian analysis is providing good prior distribution for the parameters. 
@@
 \end{tabular}
-\parbox{0.75\linewidth}{\caption{Prior probabilities distribution for NIE parameters, where the scale parameter depends on <something> \label{table:1} }}
+\parbox{0.75\linewidth}{\caption{Prior probabilities distribution for SIE parameters, where the scale parameter depends on <something> \label{table:1} }}
 

### 2015-06-08 Papers/pgm.py
mathbf --> boldsymbol

@@ -14,13 +14,13 @@ pgm = daft.PGM([9., 5.], origin=[-2.5, -2.5])
 
 # Create the nodes
 pgm.add_node(daft.Node('alpha', r'$\boldsymbol{\alpha}_{\rm src}$', 0., 2.))
-pgm.add_node(daft.Node('x', r'$\mathbf{x}_i^{\rm src}$', 0., 0.))
-pgm.add_node(daft.Node('data', r'$\mathcal{D}$', 2., 0., observed=True))
+pgm.add_node(daft.Node('x', r'$\boldsymbol{x}_i^{\rm src}$', 0., 0.))
+pgm.add_node(daft.Node('data', r'$\boldsymbol{D}$', 2., 0., observed=True))
 pgm.add_node(daft.Node('N', r'$N_{\rm src}$', -2., 0.))
 pgm.add_node(daft.Node('hidden', r'', -1., 0., scale=0, plot_params={'alpha':0}))
 
 # Right hand side
-pgm.add_node(daft.Node('x2', r'$\mathbf{x}_i^{\rm lens}$', 4., 0.))
+pgm.add_node(daft.Node('x2', r'$\boldsymbol{x}_i^{\rm lens}$', 4., 0.))
 pgm.add_node(daft.Node('alpha2', r'$\boldsymbol{\alpha}_{\rm lens}$', 4., 2.))
 pgm.add_node(daft.Node('N2', r'$N_{\rm lens}$', 6., 0.))
 pgm.add_node(daft.Node('hidden2', r'', 5., 0., scale=0, plot_params={'alpha':0}))

### 2015-06-08 Papers/pgm.py
NIE --> SIE

@@ -27,7 +27,7 @@ pgm.add_node(daft.Node('hidden2', r'', 5., 0., scale=0, plot_params={'alpha':0})
 
 # Top and bottom
 pgm.add_node(daft.Node('sigma', r'$\boldsymbol{\sigma}$', 2., 2.))
-pgm.add_node(daft.Node('nie', r'$\boldsymbol{\theta}_{\rm NIE}$', 2., -2.))
+pgm.add_node(daft.Node('sie', r'$\boldsymbol{\theta}_{\rm SIE}$', 2., -2.))
 
 # Add the edges
 pgm.add_edge('alpha', 'x')
@@ -39,7 +39,7 @@ pgm.add_edge('x2', 'data')
 pgm.add_edge('N2', 'hidden2')
 
 pgm.add_edge('sigma', 'data')
-pgm.add_edge('nie', 'data')
+pgm.add_edge('sie', 'data')
 
 # Add the plates
 pgm.add_plate(daft.Plate([-1., -1., 2., 2.], label=r'Source Blobs \newline $i=1, ..., N_{\rm src}$'))

### 2015-06-08 Papers/ms.tex
mathbf --> boldsymbol
Started table

@@
 \left\{
-N_{\rm src}, \left\{\mathbf{x}^{\rm src}_i\right\}_{i=1}^N
+N_{\rm src}, \left\{\boldsymbol{x}^{\rm src}_i\right\}_{i=1}^N
 \right\}
 \end{eqnarray}
-where $\mathbf{x}^{\rm src}_i$ denotes the parameters for source blob $i$:
+where $\boldsymbol{x}^{\rm src}_i$ denotes the parameters for source blob $i$:
 \begin{eqnarray}
-\mathbf{x}^{\rm src}_i &=& \left\{x_i, y_i, A_i, w_i
+\boldsymbol{x}^{\rm src}_i &=& \left\{x_i, y_i, A_i, w_i
 \right\}.
 \end{eqnarray}
-
-\begin{figure*}
-\includegraphics{pgm.pdf}
-\caption{A probabilistic graphical model (PGM) of the dependence structure
-of the prior information.\label{fig:pgm}}
-\end{figure*}
 
@@
 to the source or lens, are handled internally by {\tt RJObject}.
+
+\section{Prior Probability Distributions}
+We use the following prior probability distributions:
+
+\begin{table*}
+\begin{tabular}{|l|l|l|}
+\hline
+Quantity	&	Meaning		& Prior\\
+\hline
+{\bf Hyperparameters}\\
+$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
+$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
+
+{\bf Lens Blob Parameters}\\
+{\bf Source Blob Parameters}\\
+{\bf Smooth Lens Parameters}\\
+{\bf Noise Parameters}\\
+{\bf Data}\\
+\end{tabular}
+\caption{All of the prior distributions.
+\label{tab:priors}}
+\end{table*}
+
+\begin{figure*}
+\includegraphics{pgm.pdf}
+\caption{A probabilistic graphical model (PGM) of the dependence structure
+of the prior information.\label{fig:pgm}}
+\end{figure*}
 

### 2015-06-08 Papers/ms.tex
Cauchy

@@
 $N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
+$\mu_{\rm src}$ &	Expected mean flux of source blobs	& \\
+$\mu_{\rm lens}$ &	Expected mean mass of lens blobs	& \\
 
@@
 \end{table*}
+
+One might object to the Cauchy priors for the central positions on the
+basis that they do not have rotational symmetry. However, the priors we
+are assigning are prior to the values of the data pixel intensities only, and
+not other facts about the data, such as its dimensions in arc seconds, or its
+rectangular shape. Given these, there is no reason to insist on rotational
+symmetry. The Cauchy priors are intended to enhance the plausibility that the
+lens and source are somewhere near the centre of the image, but in a cautious
+way.
 

### 2015-06-09 Papers/ms.tex
Working on the prior section

--- 2015-06-08 Papers/ms.tex
@@
 $N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
-
+$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & \\
+$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs &\\
+$R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & \\
+$R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& \\
+$\mu_{\rm src}$ &	Typical flux of source blobs	& \\
+$\mu_{\rm lens}$&	Typical mass of lens blobs	& \\
+$W_{\rm src}$ &		Typical width of source blobs	& \\
+$W_{\rm lens}$&		Typical width of lens blobs	& \\
 {\bf Lens Blob Parameters}\\
@@
 \end{table*}
+
+We assign somewhat informative Cauchy priors to the central positions of the
+source and the lens.
+One might object to the Cauchy priors
+for the central positions (and argue instead for gaussians) on the
+basis that they do not have rotational symmetry. However, the priors we
+are assigning are prior only to the values of the data pixel intensities only,
+and not other facts about the data, such as its dimensions in arc seconds, or its
+rectangular shape. Given these, there is no reason to insist on rotational
+symmetry. The Cauchy priors are intended to enhance the plausibility
+(relative to what a uniform prior would imply) that the
+lens and source are somewhere near the centre of the image, but in a cautious
+way.
 

### 2015-06-10 Papers/ms.tex
Abstract and acknowledgement work

@@
 \begin{abstract}
-
+We introduce a Bayesian solution to the problem of inferring the density
+profile of strong gravitational lenses when the lens galaxy may contain
+multiple dark or faint substructures. The source and lens models are based on
+a superposition of an unknown number of non-negative basis functions
+(or ``blobs'') which were chosen with speed as a primary criterion.
+The prior distribution for the blobs' properties is specified hierarchically,
+so the ``mass function'' of substructures is a natural output. We use reversible
+jump Markov Chain Monte Carlo (MCMC) within Diffusive Nested Sampling (DNS) to
+sample the posterior distribution and evaluate the marginal likelihood of the
+model. We demonstrate the method on a simulated data set, and also apply it to
+the Cosmic Horseshoe, finding ...
 \end{abstract}
@@
 {\bf Lens Blob Parameters}\\
+$(x_i^{\rm src}, y_i^{\rm src})$
+$M_i$  &
+$v_i$  &
 {\bf Source Blob Parameters}\\
@@
 
+\section*{Acknowledgements}
+It is a pleasure to thank ...
+
+This work was funded by a Marsden Fast Start grant from the Royal Society of
+New Zealand.
+
 \begin{thebibliography}{99}

### 2015-06-10 Papers/ms.tex
GL keywords
Slight edits

@@
 \begin{keywords}
-methods: data analysis --- methods: statistical
+gravitational lensing --- methods: data analysis --- methods: statistical
 \end{keywords}
@@
 modelling approach lies somewhere between simply-parameterised and
-pixellated models. The source and the lens can be built up from a moderate
-number of simply parameterised components. For the source, this allows
+pixellated models.
+
+The source and the lens can be built up from a mixture of a moderate
+number (from a few to a few hundred) of
+simply parameterised components. For the source, this allows
 us to incorporate prior knowledge about the local correlations (the surface
 brightness at any particular point is likely to be similar to that at a
-nearby point) and the fact that most of the sky is dark.
+nearby point) and the fact that most of the sky is
+dark \citep{2006ApJ...637..608B}.
 
@@
 \section*{Acknowledgements}
-It is a pleasure to thank ...
+It is a pleasure to thank Phil Marshall (Stanford) and Tommaso Treu (UCLA)
+for valuable discussion.
 
@@
 \& Refregier}{2015}]{2015arXiv150407629B} Birrer S., Amara A., Refregier A., 2015, arXiv, arXiv:1504.07629
+
+\bibitem[\protect\citeauthoryear{Brewer 
+\& Lewis}{2006}]{2006ApJ...637..608B} Brewer B.~J., Lewis G.~F., 2006, ApJ, 637, 608
 

### 2015-06-10 Papers/ms.tex
Comparison with Brewer 2011
More entries in the table

@@
 pixellated models.
-
 The source and the lens can be built up from a mixture of a moderate
@@
 nearby point) and the fact that most of the sky is
-dark \citep{2006ApJ...637..608B}.
+dark \citep{2006ApJ...637..608B}. The main differences between the
+\citet{2011MNRAS.412.2521B} and that of the present approach are:
+i) we use a simpler and faster basis set, and ii) we apply it to the lens
+as well as the source. However, in the present paper we do not account for
+multi-band data.
 
@@
 $W_{\rm lens}$&		Typical width of lens blobs	& \\
+{\bf Source Blob Parameters}\\
+$(x_i^{\rm src}, y_i^{\rm src})$ & Blob position & \\
+$A_i$  & Blob flux & Exponential(mean=$\mu_{\rm src}$)\\
+$w_i$  & Blob width & Exponential(mean=$W_{\rm src}$)\\
 {\bf Lens Blob Parameters}\\
-$(x_i^{\rm src}, y_i^{\rm src})$
-$M_i$  &
-$v_i$  &
-{\bf Source Blob Parameters}\\
+$(x_i^{\rm lens}, y_i^{\rm lens})$ & Blob position & \\
+$M_i$  & Blob mass & Exponential(mean=$\mu_{\rm lens}$)\\
+$v_i$  & Blob width & Exponential(mean=$W_{\rm lens}$)\\
 {\bf Smooth Lens Parameters}\\

### 2015-06-11 Papers/ms.tex
Working on the table

--- 2015-06-10 Papers/ms.tex
@@
 {\bf Hyperparameters}\\
+\hline
 $N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
 $N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
-$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & \\
-$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs &\\
+$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=0, scale=0.1$\times$(image width))\\
+$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=0, scale=0.1$\times$(image width))\\
 $R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & \\
@@
 $W_{\rm lens}$&		Typical width of lens blobs	& \\
+\hline
+{\bf Source Blob Parameters}\\
+\hline
+$(x_i^{\rm src}, y_i^{\rm src})$ & Blob position & Circular(location=$(x_c^{\rm src}, y_c^{\rm src})$, scale=$R_{\rm src}$)\\
+$A_i$  & Blob flux & Exponential(mean=$\mu_{\rm src}$)\\
+$w_i$  & Blob width & Exponential(mean=$W_{\rm src}$)\\
+\hline
 {\bf Lens Blob Parameters}\\
-$(x_i^{\rm src}, y_i^{\rm src})$
-$M_i$  &
-$v_i$  &
-{\bf Source Blob Parameters}\\
+\hline
+$(x_i^{\rm lens}, y_i^{\rm lens})$ & Blob position & \\
+$M_i$  & Blob mass & Exponential(mean=$\mu_{\rm lens}$)\\
+$v_i$  & Blob width & Exponential(mean=$W_{\rm lens}$)\\
+\hline
 {\bf Smooth Lens Parameters}\\
+\hline
+$b$\\
+$q$\\
+$(x_c^{\rm SIE}, y_c^{\rm SIE})$\\
+$\theta$\\
+$\gamma$\\
+$\theta_\gamma$\\
+\hline
 {\bf Noise Parameters}\\
+\hline
+$\sigma_0$\\
+$\sigma_1$\\
+\hline
 {\bf Data}\\
+\hline
+$D_{ij}$
 \end{tabular}

### 2015-06-11 Papers/ms.tex
WRITE ALL THE PRIORS!

--- 2015-06-10 Papers/ms.tex
@@
 {\bf Hyperparameters}\\
+\hline
 $N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
 $N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
-$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & \\
-$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs &\\
-$R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & \\
-$R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& \\
-$\mu_{\rm src}$ &	Typical flux of source blobs	& \\
-$\mu_{\rm lens}$&	Typical mass of lens blobs	& \\
-$W_{\rm src}$ &		Typical width of source blobs	& \\
-$W_{\rm lens}$&		Typical width of lens blobs	& \\
+$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=0, scale=0.1$\times$(image width))\\
+$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=0, scale=0.1$\times$(image width))\\
+$R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
+$R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
+$\mu_{\rm src}$ &	Typical flux of source blobs	& $\ln(\mu_{\rm src}) \sim$ Cauchy(0, 1)T(-21, 21)\\
+$\mu_{\rm lens}$&	Typical mass of lens blobs	& $\ln(\mu_{\rm lens}) \sim$ Cauchy(0, 1)T(-21, 21)\\
+$W_{\rm max}^{\rm src}$ &		Maximum width of source blobs	& LogUniform(0.001$\times$(image width), image width)\\
+$W_{\rm min}^{\rm src}$ &		Minimum width of source blobs	& Uniform(0, $W_{\rm max}^{\rm src}$)\\
+$W_{\rm max}^{\rm lens}$ &		Maximum width of lens blobs	& LogUniform(0.001$\times$(image width), image width)\\
+$W_{\rm min}^{\rm lens}$ &		Minimum width of lens blobs	& Uniform(0, $W_{\rm max}^{\rm lens}$)\\
+\hline
+{\bf Source Blob Parameters}\\
+\hline
+$(x_i^{\rm src}, y_i^{\rm src})$ & Blob position & Circular(location=$(x_c^{\rm src}, y_c^{\rm src})$, scale=$R_{\rm src}$)\\
+$A_i$  & Blob flux & Exponential(mean=$\mu_{\rm src}$)\\
+$w_i$  & Blob width & Uniform($W_{\rm min}^{\rm src}$, $W_{\rm max}^{\rm src}$)\\
+\hline
 {\bf Lens Blob Parameters}\\
-$(x_i^{\rm src}, y_i^{\rm src})$
-$M_i$  &
-$v_i$  &
-{\bf Source Blob Parameters}\\
+\hline
+$(x_i^{\rm lens}, y_i^{\rm lens})$ & Blob position & Circular(location=$(x_c^{\rm lens}, y_c^{\rm lens})$, scale=$R_{\rm lens}$) \\
+$M_i$  & Blob mass & Exponential(mean=$\mu_{\rm lens}$)\\
+$v_i$  & Blob width & Uniform($W_{\rm min}^{\rm src}$, $W_{\rm max}^{\rm src}$)\\
+\hline
 {\bf Smooth Lens Parameters}\\
+\hline
+$b$ & SIE Einstein Radius & \\
+$q$ & Axis ratio\\
+$(x_c^{\rm SIE}, y_c^{\rm SIE})$ & Central position\\
+$\theta$ & Orientation angle\\
+$\gamma$ & External shear\\
+$\theta_\gamma$ & External shear angle\\
+\hline
 {\bf Noise Parameters}\\
+\hline
+$\sigma_0$ & Constant component of noise variance\\
+$\sigma_1$ & \\
+\hline
 {\bf Data}\\
+\hline
+$D_{ij}$ & Pixel intensities & Normal()
 \end{tabular}

### 2015-06-11 Papers/ms.tex
SIE apologies

@@
 of a singular isothermal ellipsoid plus external shear (SIE+$\gamma$) and
-$N$ circular lens ``blobs''. The SIE+$\gamma$ has nine parameters:
-the (circularized) einstein radius $b$, axis ratio $q$, central position
-$(x_c, y_c)$, orientation angle $\theta$, the external shear $\gamma$, and the
-orientation angle of the external shear, $\theta_{\gamma}$. The SIE+$\gamma$
-is supposed to account for the bulk of the lensing effect. Of course, more
-general and flexible smooth models are possible. Ultimately, concentric
+$N$ circular lens ``blobs''. The SIE+$\gamma$ is a simple and widely used lens
+model with analytically available deflection angles, and is intended to account
+for the bulk of the lensing effect due to the smooth spatial distribution
+of (visible and dark) matter in the lens galaxy. Unfortunately, along with
+simplicity comes a lack of realism, and generalising the smooth lens model
+is an important future step. Ultimately, concentric
 mixtures of smooth components may be the most useful for realistic inference
@@
 
+The SIE+$\gamma$ has nine parameters:
+the (circularized) einstein radius $b$, axis ratio $q$, central position
+$(x_c, y_c)$, orientation angle $\theta$, the external shear $\gamma$, and the
+orientation angle of the external shear, $\theta_{\gamma}$.
+
+The $N$ lens blobs are intended to model possible dark or faint substructures
+in the projected mass profile of the lens.
 A lensing blob with mass $M$ and width $v$

### 2015-06-11 Papers/ms.tex
Finished the bloody table!

@@
 
-The SIE+$\gamma$ has nine parameters:
+The SIE+$\gamma$ has nine free parameters:
 the (circularized) einstein radius $b$, axis ratio $q$, central position
@@
 $N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
-$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=0, scale=0.1$\times$(image width))\\
-$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=0, scale=0.1$\times$(image width))\\
+$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times$(image width))\\
+$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times$(image width))\\
 $R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
 $R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
-$\mu_{\rm src}$ &	Typical flux of source blobs	& $\ln(\mu_{\rm src}) \sim$ Cauchy(0, 1)T(-21, 21)\\
-$\mu_{\rm lens}$&	Typical mass of lens blobs	& $\ln(\mu_{\rm lens}) \sim$ Cauchy(0, 1)T(-21, 21)\\
+$\mu_{\rm src}$ &	Typical flux of source blobs	& $\ln(\mu_{\rm src}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
+$\mu_{\rm lens}$&	Typical mass of lens blobs	& $\ln(\mu_{\rm lens}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
 $W_{\rm max}^{\rm src}$ &		Maximum width of source blobs	& LogUniform(0.001$\times$(image width), image width)\\
@@
 \hline
-$b$ & SIE Einstein Radius & \\
-$q$ & Axis ratio\\
-$(x_c^{\rm SIE}, y_c^{\rm SIE})$ & Central position\\
-$\theta$ & Orientation angle\\
-$\gamma$ & External shear\\
-$\theta_\gamma$ & External shear angle\\
+$b$ & SIE Einstein Radius & LogUniform(0.001$\times$(image width), image width)\\
+$q$ & Axis ratio & Uniform(0, 0.95)\\
+$(x_c^{\rm SIE}, y_c^{\rm SIE})$ & Central position & iid Cauchy(location=$(0,0)$, scale=0.1$\times$(image width))\\
+$\theta$ & Orientation angle & Uniform$(0, \pi)$\\
+$\gamma$ & External shear & Cauchy$(0, 0.05)T(0, )$\\
+$\theta_\gamma$ & External shear angle & Uniform$(0, \pi)$\\
 \hline
@@
 \hline
-$\sigma_0$ & Constant component of noise variance\\
-$\sigma_1$ & \\
+$\sigma_0$ & Constant component of noise variance & $\ln(\sigma_0) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
+$\sigma_1$ & Proportionality coeff. for variance incr. with flux &
+$\ln(\sigma_1) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
 \hline
@@
 \hline
-$D_{ij}$ & Pixel intensities & Normal()
+$D_{ij}$ & Pixel intensities & Normal$(m_{ij}, s_{ij}^2 + \sigma_0^2 + \sigma_1m_{ij})$
 \end{tabular}

### 2015-06-12 Papers/ms.tex
More work on priors etc

@@
 \section{The Model}
+We now describe the details of our model and its parameterization.
 
@@
 \section{Prior Probability Distributions}
-We use the following prior probability distributions:
+The prior probability distributions for all hyperparameters, parameters, and
+the data, are given in Table~\ref{tab:priors}, and a factorization of the
+joint distribution is displayed in Figure~\ref{fig:pgm}.
 
@@
 $\theta$ & Orientation angle & Uniform$(0, \pi)$\\
-$\gamma$ & External shear & Cauchy$(0, 0.05)T(0, )$\\
+$\gamma$ & External shear & Cauchy$(0, 0.05)T(0, \infty)$\\
 $\theta_\gamma$ & External shear angle & Uniform$(0, \pi)$\\
@@
 \end{tabular}
-\caption{All of the prior distributions.
+\caption{The prior distribution for all hyperparameters, parameters, and the
+data, in our model. Uniform$(a, b)$ is a uniform
+distribution between $a$ and $b$. LogUniform$(a, b)$ is a log-uniform
+distribution (with density $f(x) \propto 1/x$, sometimes erroneously called
+a Jeffreys prior) between $a$ and $b$. The notation $T(\alpha, \beta)$ after
+a distribution denotes truncation to the interval $[\alpha, \beta]$.
 \label{tab:priors}}

### 2015-06-14 Papers/ms.tex
General philosophy for our priors

@@
 the data, are given in Table~\ref{tab:priors}, and a factorization of the
-joint distribution is displayed in Figure~\ref{fig:pgm}.
+joint distribution is displayed in Figure~\ref{fig:pgm}. With these priors,
+we aim to express a large degree of prior uncertainty (hence the liberal use
+of uniform, loguniform, and Cauchy distributions). However, we also specify
+some priors hierarchically to allow (for example)
+blobs to cluster around a typical central
+position, rather than implying a high probability for substructure positions
+being spread uniformly (in a frequency sense) over the sky. We also applied
+hierarchical priors to the substructure masses (and fluxes) so that, while
+the typical order of magnitude of the masses is unknown, the masses
+themselves are likely to be roughly the same order of magnitude.
 

### 2015-06-14 Papers/ms.tex
circular distribution
Forgot the 2pi in the normalising constant
why not normal?

@@
 
+The ``circular'' conditional prior for the blob positions has the following
+density:
+\begin{eqnarray}
+\rho(x, y)\, dx \, dy &=&
+\frac{1}{2\pi W} \frac{1}{r}\exp\left(-\frac{r}{W}\right) \, dx \, dy
+\end{eqnarray}
+where $r = \sqrt{(x-x_c)^2 + (y-y_c)^2}$. This results from an exponential
+distribution (with expectation $W$) for the radial coordinate and a uniform distribution for the angular coordinate in plane polar coordinates. This was
+chosen (as opposed to a more ``obvious'' choice such as a normal distribution)
+for computational reasons: the {\tt RJObject} code requires a function to
+transform from Uniform(0, 1) distributions to this distribution and back, and
+the normal would have required the use of special functions.
+
 \begin{figure*}

### 2015-06-14 Papers/ms.tex
Removed old table

@@
 In both models the SIE is specified by the usual parameters: the location of the SIE ($x_c$,$y_c$), b, axis ratio $f$\footnote{in the code denoted with $q$},  the core radius$\zeta$, $\theta$, shear $\gamma$, and $\theta_{\gamma}$ \cite{kormann_schneider_1994}.\\
-One of the firsts step in applying Bayesian analysis is providing good prior distribution for the parameters. 
-The chosen prior probability distributions are displayed in table \ref{table:1}. The parameters which are not listed in table 
-\ref{table:1} depend on parameters which are listed.
-
-\begin{table}
-\centering
-\begin{tabular}{ l l}
-parameter    &  expression        \\  
-\hline 
-b            &  $exp\left(  log_{10}(10^{-3})+  log_{10}(10^{3})\cdot Unif(0,1) \right)\cdot scale  $ \\
-q            &  $0.05 + 0.95\cdot Unif(0,1) $ \\
-$x_c$       &  $0.5\cdot (x_{max} + x_{min}) +   0.1 \cdot(x_{max} - x_{min}) \cdot tan(\pi\cdot ( Unif(0,1) - 0.5)  )$ \\
-$		y_c$  &  $0.5\cdot (y_{max} + y_{min}) + 0.1\cdot (y_{max} - y_{min}) \cdot tan(\pi\cdot (Unif(0,1)  - 0.5)  ) $\\
-%rc           &  if $\left\{
-%  \begin{array}{l l}
-%    \textrm{singular} & \quad bb\\
- %   \textrm{non-singular} & \quad  bb
-  %\end{array} \right.$
-rc(singular)   & $10^{-7}\cdot scale$ \\
-rc(non-singular)   & $  exp\left(log_{10}(10^{-3})+  log_{10}(10^{3})\cdot Unif(0,1)\right) \cdot scale   $\\
-$\theta$   & $\pi \cdot Unif(0,1)$\\
-shear      & $0.05 \cdot tan(\pi \cdot 0.5 \cdot Unif(0,1)) $\\
-$theta_{shear}$  & $ \pi\cdot Unif(0,1)$ \\
-\end{tabular}
-\parbox{0.75\linewidth}{\caption{Prior probabilities distribution for SIE parameters, where the scale parameter depends on <something> \label{table:1} }}
-
-\end{table}
 

### 2015-06-14 Papers/pgm.py
Calling parameters theta instead of x

@@ -14,13 +14,13 @@ pgm = daft.PGM([9., 5.], origin=[-2.5, -2.5])
 
 # Create the nodes
 pgm.add_node(daft.Node('alpha', r'$\boldsymbol{\alpha}_{\rm src}$', 0., 2.))
-pgm.add_node(daft.Node('x', r'$\boldsymbol{x}_i^{\rm src}$', 0., 0.))
+pgm.add_node(daft.Node('x', r'$\boldsymbol{\theta}_i^{\rm src}$', 0., 0.))
 pgm.add_node(daft.Node('data', r'$\boldsymbol{D}$', 2., 0., observed=True))
 pgm.add_node(daft.Node('N', r'$N_{\rm src}$', -2., 0.))
 pgm.add_node(daft.Node('hidden', r'', -1., 0., scale=0, plot_params={'alpha':0}))
 
 # Right hand side
-pgm.add_node(daft.Node('x2', r'$\boldsymbol{x}_i^{\rm lens}$', 4., 0.))
+pgm.add_node(daft.Node('x2', r'$\boldsymbol{\theta}_i^{\rm lens}$', 4., 0.))
 pgm.add_node(daft.Node('alpha2', r'$\boldsymbol{\alpha}_{\rm lens}$', 4., 2.))
 pgm.add_node(daft.Node('N2', r'$N_{\rm lens}$', 6., 0.))
 pgm.add_node(daft.Node('hidden2', r'', 5., 0., scale=0, plot_params={'alpha':0}))

### 2015-06-16 Papers/ms.tex
Time delay refs

@@
 which are thought to contain at least one dark substructure
-\citep{vegetti1, vegetti2, vegetti3}.
+\citep{vegetti1, vegetti2, vegetti3}. The present paper describes an
+approach we have developed for the inverse problem of detecting dark
+substructures from image data. However, it may also prove useful in other
+galaxy-galaxy lens modelling areas, such as time-delay cosmography, which
+requires realistically flexible lens models, and reliable uncertainty
+quantification
+\citep{2013ApJ...766...70S, 2014ApJ...788L..35S, grillo}.
 
@@
 
+\bibitem[\protect\citeauthoryear{Grillo et al.}{2015}]{grillo} 
+Grillo C., et al., 2015, ApJ, 800, 38
+
 \bibitem[\protect\citeauthoryear{Huppenkothen et 
@@
 
+\bibitem[\protect\citeauthoryear{Suyu et al.}{2014}]{2014ApJ...788L..35S} 
+Suyu S.~H., et al., 2014, ApJ, 788, L35
+
+\bibitem[\protect\citeauthoryear{Suyu et al.}{2013}]{2013ApJ...766...70S} 
+Suyu S.~H., et al., 2013, ApJ, 766, 70
+
 \bibitem[\protect\citeauthoryear{Tagore 

### 2015-06-16 Papers/ms.tex
x --> theta
Table edits

@@
 \left\{
-N_{\rm src}, \left\{\boldsymbol{x}^{\rm src}_i\right\}_{i=1}^N
+N_{\rm src}, \left\{\boldsymbol{\theta}^{\rm src}_i\right\}_{i=1}^N
 \right\}
 \end{eqnarray}
-where $\boldsymbol{x}^{\rm src}_i$ denotes the parameters for source blob $i$:
+where $\boldsymbol{\theta}^{\rm src}_i$ denotes the parameters for source blob $i$:
 \begin{eqnarray}
-\boldsymbol{x}^{\rm src}_i &=& \left\{x_i, y_i, A_i, w_i
+\boldsymbol{\theta}^{\rm src}_i &=& \left\{x_i, y_i, A_i, w_i
 \right\}.
@@
 \hline
-{\bf Hyperparameters}\\
+{\bf Numbers of Blobs}\\
 \hline
@@
 $N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
+\hline
+{\bf Source hyperparameters} ($\boldsymbol{\alpha}_{\rm src}$)\\
+\hline
 $(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times$(image width))\\
-$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times$(image width))\\
-$R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
-$R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
+$R_{\rm src}$   &	Typical distance of blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
 $\mu_{\rm src}$ &	Typical flux of source blobs	& $\ln(\mu_{\rm src}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
-$\mu_{\rm lens}$&	Typical mass of lens blobs	& $\ln(\mu_{\rm lens}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
 $W_{\rm max}^{\rm src}$ &		Maximum width of source blobs	& LogUniform(0.001$\times$(image width), image width)\\
 $W_{\rm min}^{\rm src}$ &		Minimum width of source blobs	& Uniform(0, $W_{\rm max}^{\rm src}$)\\
+\hline
+{\bf Lens hyperparameters} ($\boldsymbol{\alpha}_{\rm lens}$)\\
+\hline
+$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times$(image width))\\
+$R_{\rm lens}$  &	Typical distance of blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
+$\mu_{\rm lens}$&	Typical mass of lens blobs	& $\ln(\mu_{\rm lens}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
 $W_{\rm max}^{\rm lens}$ &		Maximum width of lens blobs	& LogUniform(0.001$\times$(image width), image width)\\
@@
 \hline
-{\bf Source Blob Parameters}\\
+{\bf Source Blob Parameters} ($\boldsymbol{\theta}_i^{\rm src}$)\\
 \hline
@@
 \hline
-{\bf Lens Blob Parameters}\\
+{\bf Lens Blob Parameters} ($\boldsymbol{\theta}_i^{\rm lens}$)\\
 \hline
@@
 \hline
-{\bf Smooth Lens Parameters}\\
+{\bf Smooth Lens Parameters} ($\boldsymbol{\theta}_{\rm SIE}$)\\
 \hline
@@
 \hline
-{\bf Noise Parameters}\\
+{\bf Noise Parameters} ($\boldsymbol{\sigma}$)\\
 \hline
 $\sigma_0$ & Constant component of noise variance & $\ln(\sigma_0) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
-$\sigma_1$ & Proportionality coeff. for variance incr. with flux &
+$\sigma_1$ & Coefficient for variance increasing with flux &
 $\ln(\sigma_1) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
 \hline
-{\bf Data}\\
+{\bf Data} ($\boldsymbol{D}$)\\
 \hline

### 2015-06-16 Papers/ms.tex
Parameter lists

@@
 \end{eqnarray}
-The deflection angles are:
+The deflection angles for a single blob are:
 
@@
 \right.
+\end{eqnarray}
+where $r=\sqrt{x^2 + y^2}$. For $N$ such blobs the deflection angles are
+summed over all blobs. Therefore the lens can be entirely described by
+the following parameters:
+
+\begin{eqnarray}
+\left\{
+\boldsymbol{\theta}_{\rm SIE},
+N_{\rm lens}, \left\{\boldsymbol{\theta}^{\rm lens}_i\right\}_{i=1}^N
+\right\}
+\end{eqnarray}
+where $\boldsymbol{\theta}^{\rm lens}_i$ denotes the parameters for lens blob $i$:
+\begin{eqnarray}
+\boldsymbol{\theta}^{\rm lens}_i &=& \left\{x_i^{\rm lens}, y_i\rm lens}, M_i, v_i
+\right\},
+\end{eqnarray}
+and $\boldsymbol{\theta}_{\rm SIE}$ describes the parameters for the SIE
+component:
+\begin{eqnarray}
+\boldsymbol{\theta}_{\rm SIE} = \left\{
+b, q, (x_c^{\rm SIE}, y_c^{\rm SIE}), \theta, \gamma, \theta_\gamma
+\right\}.
 \end{eqnarray}

### 2015-06-16 Papers/ms.tex
fixed bracket problem
Discussion of assumptions

@@
 \section{The Model}
-We now describe the details of our model and its parameterization.
+We now describe the details of our model and its parameterization. The
+motivation for most of our modelling choices is a compromise between
+computational efficiency, realism, and ease of implementation. None of the
+choices we have made are final in any sense, and we encourage exploration of
+other choices. Since we can compute marginal likelihoods, Bayesian model
+comparison between our choices here and any proposed alternatives should be
+straightforward, provided a mixture of our model and another is considered
+reasonable.
 
@@
 The surface brightness profile of the source is assumed to be composed of
-a sum of a finite number of ``blobs'', or basis functions. The specific choice
-of basis functions we use is motivated primarily by computational speed.
-The surface brightness of a single blob centered at the origin
-is:
+a sum of a finite number of ``blobs'', or basis functions, in order to
+allow some flexibility while incorporating prior information about the
+non-negativity of surface brightness, and the spatial correlation expected
+in real surface brightness profiles.
+
+For computational speed, we choose the following
+functional form for the surface brightness profile
+of a single blob centered at the origin:
 \begin{eqnarray}
@@
 entire domain).
-These basis functions are faster to evaluate than gaussians, since they do not
+These basis functions are inverted paraboloids, which are faster to evaluate
+than gaussians, since they do not
 contain an exponential function. In addition, the finite support means that
@@
 
-Under these assumptions, the source can be described by the following
-parameters:
-
+Under these assumptions, the source can be described in its entirety
+by the following parameters:
 \begin{eqnarray}
@@
 \begin{eqnarray}
-\boldsymbol{\theta}^{\rm lens}_i &=& \left\{x_i^{\rm lens}, y_i\rm lens}, M_i, v_i
+\boldsymbol{\theta}^{\rm lens}_i &=& \left\{x_i^{\rm lens}, y_i^{\rm lens}, M_i, v_i
 \right\},

### 2015-06-16 Papers/ms.tex
Mention potential correction
A complete abstract

@@
 sample the posterior distribution and evaluate the marginal likelihood of the
-model. We demonstrate the method on a simulated data set, and also apply it to
-the Cosmic Horseshoe, finding ...
+model. We demonstrate the method on a simulated data set with a single
+substructure, which is recovered well with moderate uncertainties. We also
+apply the method to an image of the ``Cosmic Horseshoe'' lens, and find some
+hints of potential substructures. However, we caution that such results could
+also be attributed to misspecifications in the model (such as the shape of
+the smooth lens component or the point spread function),
+which are difficult to guard against in full generality.
 \end{abstract}
@@
 mixtures of smooth components may be the most useful for realistic inference
-of the density profile of the halo.
+of the density profile of the halo. A common approach in the lensing
+community, that is similar in spirit, is a superposition of an elliptical
+power law, external shear, and a pixellated potential correction. However, the
+direct use of blobs is closer to the scientific question at hand
+when investigating postential dark substructures.
 

### 2015-06-16 Papers/ms.tex
Computation section

@@
 
+\section{Computation}
+To compute the posterior distribution for the parameters
+(of which there are 24--464, depending on the values of $N_{\rm src}$ and
+$N_{\rm lens}$), we use Diffusive Nested Sampling \citep{dnest}, a form
+of Nested Sampling \citep{skilling} that uses the Metropolis algorithm
+to move around the parameter space.
+
+The proposal distributions for the blob parameters (both source and lens) are
+handled by the {\tt RJObject} library \citep{rjobject}. This includes
+birth and death proposals that increase or decrease either $N_{\rm src}$,
+or $N_{\rm lens}$, as well as proposals that move the blobs (in their parameter
+space) while keeping the number of blobs fixed. {\tt RJObject} also
+facilitates proposals that change the hyperparameters (either for the lens
+or the source) while keeping the actual blobs in place, as well as proposals
+that change the hyperparameters and shift all of the relevant blobs in
+so they are appropriate for the new values of the hyperparameters.
+
 \section{The Cosmic Horseshoe}

### 2015-06-16 Papers/ms.tex
Simulated data section

@@
 applications of {\tt RJObject} include \citet{magnetron}
-and~\citep{exoplanet}. Proposal moves for the parameters (positions and masses
+and~\citet{exoplanet}. Proposal moves for the parameters (positions and masses
 of the source and lens blobs), and birth/death moves to add or remove blobs
@@
 so they are appropriate for the new values of the hyperparameters.
+
+\section{Simulated Data}
+To demonstrate the method, we generated a simulated dataset with a single
+substructure. The image is shown in Figure X.
 

### 2015-06-17 Papers/images.py
Simulated data image

@@ -1,0 +1,13 @@
+from pylab import *
+rc("font", size=16, family="serif", serif="Computer Sans")
+rc("text", usetex=True)
+
+img = loadtxt("../Data/mock_image.txt")
+
+imshow(img, interpolation="nearest", cmap="Oranges")
+gca().set_xticklabels("")
+gca().set_yticklabels("")
+title("Simulated Dataset")
+savefig("simulated_image.pdf", bbox_inches="tight")
+show()
+

### 2015-06-17 Papers/ms.tex
Simulated data image
Horseshoe image

@@
 To demonstrate the method, we generated a simulated dataset with a single
-substructure. The image is shown in Figure X.
+substructure. The image is shown in Figure~\ref{fig:simulated_image}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{simulated_image.pdf}
+\caption{\label{fig:simulated_image}}
+\end{center}
+\end{figure}
 
 \section{The Cosmic Horseshoe}
-As a demonstration the method is the applied to the Cosmic Horseshoe INT data. 
-The field of view of the image is $15.3180" \times 15.3180"$, and the size is $46 \times 46$ pixels, therefore one pixel is equivalent to $0.33"$. \\
-The method discussed  in the previous section is applied to two models, the first model consist of a flexible source and a Singular Isothermal Elliptical(SIE) model for the lens.
+As a further demonstration the method, we apply it to the X-band INT
+image of the Cosmic Horseshoe \citep{}, which is shown in
+Figure~\ref{fig:horseshoe_image}.
+
+%The field of view of the image is $15.3180" \times 15.3180"$, and the size is $46 \times 46$ pixels, therefore one pixel is equivalent to $0.33"$. \\
+%The method discussed  in the previous section is applied to two models, the first model consist of a flexible source and a Singular Isothermal Elliptical(SIE) model for the lens.
 This model is has been used often  \cite{Dye2008}, \cite{schneider_falcoa_Ehlers_1994},      .
-The second model has in addition to the flexible source and SIE, also possible satellites. \\
-The amount of added satellites is automatically determined by the program.
+%The second model has in addition to the flexible source and SIE, also possible satellites. \\
+%The amount of added satellites is automatically determined by the program.
 If models the addition of an satellite galaxies gives a higher probability it will be preferred over then model without satellite galaxies.
 \\
-In both models the SIE is specified by the usual parameters: the location of the SIE ($x_c$,$y_c$), b, axis ratio $f$\footnote{in the code denoted with $q$},  the core radius$\zeta$, $\theta$, shear $\gamma$, and $\theta_{\gamma}$ \cite{kormann_schneider_1994}.\\
+%In both models the SIE is specified by the usual parameters: the location of the SIE ($x_c$,$y_c$), b, axis ratio $f$\footnote{in the code denoted with $q$},  the core radius$\zeta$, $\theta$, shear $\gamma$, and $\theta_{\gamma}$ \cite{kormann_schneider_1994}.\\
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{horseshoe_image.pdf}
+\caption{\label{fig:horseshoe_image}}
+\end{center}
+\end{figure}
 

### 2015-06-17 Papers/images.py

@@ -3,11 +3,22 @@ rc("font", size=16, family="serif", serif="Computer Sans")
 rc("text", usetex=True)
 
 img = loadtxt("../Data/mock_image.txt")
-
 imshow(img, interpolation="nearest", cmap="Oranges")
 gca().set_xticklabels("")
 gca().set_yticklabels("")
 title("Simulated Dataset")
 savefig("simulated_image.pdf", bbox_inches="tight")
+show()
+
+img = loadtxt("../Data/horseshoe_image.txt")
+imshow(img, interpolation="nearest", cmap="Oranges")
+gca().set_xticks([-0.5, 0.5*img.shape[1], img.shape[1] - 0.5])
+gca().set_yticks([-0.5, 0.5*img.shape[0], img.shape[0] - 0.5])
+gca().set_xticklabels([-7.66, 0, 7.66])
+gca().set_yticklabels([-7.66, 0, 7.66])
+xlabel("$x$ (arcseconds)")
+ylabel("$y$ (arcseconds)")
+title("Cosmic Horseshoe")
+savefig("horseshoe_image.pdf", bbox_inches="tight")
 show()
 

### 2015-06-17 Papers/ms.tex
A bit of writing

@@
 
+Evaluating likelihood function requires that we compute a ``mock'' image from
+the current setting of the parameters. This mock image is calculated using
+standard ray-tracing methods with a uniform grid of $n \times n$ rays
+fired per image pixel. However, certain kinds of proposals do not affect the
+image in any way, such as those that change the noise parameters.
+
 \section{Simulated Data}
 To demonstrate the method, we generated a simulated dataset with a single
-substructure. The image is shown in Figure~\ref{fig:simulated_image}.
+substructure. The image is shown in Figure~\ref{fig:simulated_image}, and
+consists of 100 $\times$ 100 pixels. The PSF was compact and was
+defined on a 5 $\times$ 5 grid. The data was created by firing only one ray
+per pixel, and the inference was also carried out under the same level of
+approximation. Since the model assumptions are all correct for this image, the
+demonstration here is purely to illustrate the computational tractability of
+the problem, and the kind of outputs we are capable of producing.
 

### 2015-06-22 Papers/ms.tex
Caption

@@
 demonstration here is purely to illustrate the computational tractability of
-the problem, and the kind of outputs we are capable of producing.
+the problem, and the kind of outputs the method can produce.
 
@@
 \includegraphics[scale=0.5]{simulated_image.pdf}
-\caption{\label{fig:simulated_image}}
+\caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
+lens plus a single dark substructure. The image was blurred by a PSF and had
+some noise added.\label{fig:simulated_image}}
 \end{center}

### 2015-06-22 Papers/ms.tex
Paragraphs

@@
 \section{The Cosmic Horseshoe}
-As a further demonstration the method, we apply it to the X-band INT
-image of the Cosmic Horseshoe \citep{}, which is shown in
-Figure~\ref{fig:horseshoe_image}.
+As a further demonstration the method, we apply it to the X-band data
+from the Isaac Newton Telescope (INT). This image of the Cosmic Horseshoe
+\citep{}, which is shown in Figure~\ref{fig:horseshoe_image}. For this system,
+more data is available (Y and Z band data, as well as more recent
+Hubble Space Telescope (HST) imaging). Unfortunately our current implementation
+doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
+is quite slow when running on the larger HST image. Therefore this section
+should be considered a further demonstration of the technique, and not a
+thorough study of this system.
 
@@
 \bibitem[\protect\citeauthoryear{Huppenkothen et 
-al.}{2015}]{magnetron} Huppenkothen D., et al., 2015, arXiv, 
-arXiv:1501.05251
+al.}{2015}]{magnetron} Huppenkothen D., et al., 2015,
+accepted for publication in ApJ. arXiv:1501.05251
 

### 2015-06-23 Papers/ms.tex
Paragraph on computation time etc.

@@
 
+We executed the code to generate 3,000 samples from the ``mixture of
+constrained priors'' distribution of DNest. Our thinning factor was $10^5$,
+so $3 \times 10^8$ MCMC iterations were actually performed, taking approximately
+30 hours on a PC purchased new in 2012. After resampling these samples to
+reflect the posterior distribution, we were left with 318
+(equally weighted) posterior samples.
+
 \section{The Cosmic Horseshoe}

### 2015-06-24 Papers/ms.tex
Editing in rjobject paragraph

@@
 reversible jump MCMC \citep{green}. We implemented the MCMC using the
-{\tt RJObject} software \citep{rjobject}, a C++ library for implementing trans-dimensional
-MCMC with hierarchically-specified priors, and doing the sampling with the
-Diffusive Nested Sampling algorithm \citep{dnest}. Previous astronomical
+{\tt RJObject} software \citep{rjobject}, a C++ library for implementing trans-dimensional MCMC with hierarchically-specified priors when the model is
+a ``mixture model'' or similar, as is the case here.
+The {\tt RJObject} library uses the
+Diffusive Nested Sampling algorithm \citep{dnest} for its sampling, but the
+trans-dimensionality is handled by the MCMC moves. Therefore, the marginal
+likelihood we obtain is one that involves a sum over the hypothesis space
+for $N_{\rm src}$ and $N_{\rm lens}$. In other words, we do not need
+separate runs with different trial values of $N_{\rm src}$ and $N_{\rm lens}$.
+Previous astronomical
 applications of {\tt RJObject} include \citet{magnetron}

### 2015-06-24 Papers/ms.tex
Some paras, discuss summaries

@@
 for computational reasons: the {\tt RJObject} code requires a function to
-transform from Uniform(0, 1) distributions to this distribution and back, and
-the normal would have required the use of special functions.
+transform from Uniform(0, 1) distributions to this distribution and back
+(making use of cumulative distribution functions and their inverses), and
+the normal would have required the use of special functions for this.
 
@@
 (equally weighted) posterior samples.
+
+The posterior distributions for complex models, such as the mixture models used here, are often challenging and unintuitive to summarise. One effective way
+to visualise the uncertainty in the inferences is to play a movie where each
+frame is a sample from the posterior distribution. The degree to which the
+frames differ from each other conveys the uncertainty remaining after taking
+the data into account.
+
+The {\it empirical measure} of the substructure positions is a function that
+takes the substructure positions $()$
 

### 2015-06-24 Papers/ms.tex
Define empirical measure

@@
 
-The {\it empirical measure} of the substructure positions is a function that
-takes the substructure positions $()$
+The {\it empirical measure} of the substructure positions is a functional that
+takes the substructure positions $(x_i^{\rm lens}, y_i^{\rm lens})$ and
+produces a ``density function'' over two dimensions, composed of delta
+functions at the positions themselves:
+
+\begin{eqnarray}
+\left\{
+(x_i^{\rm lens}, y_i^{\rm lens})
+\right\}_{i=1}^{N_{\rm lens}}
+\Longrightarrow
+\sum_{i=1}^{N_{\rm lens}}
+\delta\left(x - x_i^{\rm lens}, y_i^{\rm lens}, y - y_i^{\rm lens}\right).
+\end{eqnarray}
 

### 2015-06-24 Papers/ms.tex
Expected value of the em

--- 2015-06-24 Papers/ms.tex
@@
 The {\it empirical measure} of the substructure positions is a function that
-takes the substructure positions $()$
+takes the substructure positions $(x_i^{\rm lens}, y_i^{\rm lens})$ and
+produces a ``density function'' over two dimensions, composed of delta
+functions at the positions themselves:
+
+\begin{eqnarray}
+\left\{
+(x_i^{\rm lens}, y_i^{\rm lens})
+\right\}_{i=1}^{N_{\rm lens}}
+\Longrightarrow
+\sum_{i=1}^{N_{\rm lens}}
+\delta\left(x - x_i^{\rm lens}, y - y_i^{\rm lens}\right).
+\end{eqnarray}
+
+The empirical measure, being a function of the actual substructure positions,
+is not available to us since we do not know those positions with certainty.
+However, we have samples from the posterior distribution for those positions,
+and can use these (trivially) to create samples from the posterior distribution
+for the empirical measure. We can also summarise this posterior, for example,
+by taking its expected value.
+
+The posterior expected value of the empirical measure is:
+\begin{eqnarray}
+\int p(\boldsymbol{\theta} | \boldsymbol{D})
+\sum_{i=1}^{N_{\rm lens}}
+\delta\left(x - x_i^{\rm lens}, y_i^{\rm lens} - y_i^{\rm lens}\right)
+\, d\boldsymbol{\theta}
+\end{eqnarray}
+where $\boldsymbol{\theta}$ denotes all parameters and hyperparameters
+(including the $N$s) and ``$\int \,d\boldsymbol{\theta}$'' is an integral and summation over the entire parameter space.
 

### 2015-06-24 Papers/ms.tex
Monte carlo, fixed mistake
More empirical measure talk

@@
 functions at the positions themselves:
-
 \begin{eqnarray}
@@
 
-The empirical measure, being a function of the actual substructure positions,
+Intuitively, the empirical measure is a mathematical object that is like
+an ``infinite resolution histogram'', in this case a two dimensional histogram,
+of the substructure positions.
+Being a function of the actual substructure positions, the empirical measure
 is not available to us since we do not know those positions with certainty.
@@
 \sum_{i=1}^{N_{\rm lens}}
-\delta\left(x - x_i^{\rm lens}, y_i^{\rm lens} - y_i^{\rm lens}\right)
+\delta^2\left(x - x_i^{\rm lens}, y_i^{\rm lens} - y_i^{\rm lens}\right)
 \, d\boldsymbol{\theta}
@@
 (including the $N$s) and ``$\int \,d\boldsymbol{\theta}$'' is an integral and summation over the entire parameter space.
+
+Since we can approximate posterior expectations using Monte Carlo, we can
+obtain the expected value of the empirical measure using:
+\begin{eqnarray}
+\sum_{k=1}^n
+\sum_{i=1}^{N_{\rm lens}}
+\delta^2\left(x - x_i^{\rm lens}, y_i^{\rm lens} - y_i^{\rm lens}\right)
+\, d\boldsymbol{\theta}
+\end{eqnarray}
+where $n$ is the number of posterior samples. The resulting function is
+an ``image'' with a point mass wherever a substructure occurred. For
+visualisation purposes the image can be blurred, or calculated at a lower
+resolution by replacing the Dirac-delta function with a discrete version
+which returns a nonzero constant
+if a substructure appears in a pixel or zero otherwise.
 

### 2015-06-25 display.py
New figure

@@ -110,3 +110,13 @@ xlabel('Magnification (magnitudes)')
 title('Magnification = {a:.3f} +- {b:.3f}'.format(a=magnification.mean(), b=magnification.std()))
 show()
 
+figure(3)
+rc("font", size=16, family="serif", serif="Computer Sans")
+rc("text", usetex=True)
+plot(output[:,2]**2, output[:,39:48].sum(axis=1), 'bo', markersize=5,\
+                       alpha=0.2)
+xlabel('SIE mass (within critical ellipse)')
+ylabel('Total substructure mass')
+savefig('masses.pdf', bbox_inches='tight')
+show()
+

### 2015-06-25 display.py
Histogram of N_lens

@@ -120,3 +120,11 @@ ylabel('Total substructure mass')
 savefig('masses.pdf', bbox_inches='tight')
 show()
 
+hist(output[:,18], bins=arange(0, 11) - 0.5*0.3, width=0.3, alpha=0.3)
+xlim([-0.2, 10.2])
+gca().set_xticks(arange(0, 11))
+xlabel('$N_{\\rm lens}$')
+ylabel('Number of Posterior Samples')
+savefig('N_lens.pdf', bbox_inches='tight')
+show()
+

### 2015-06-25 Papers/ms.tex
New figure
delta squared for 2d delta function
Fixed probs in Monte Carlo average
Histogram for N

@@
 \sum_{i=1}^{N_{\rm lens}}
-\delta\left(x - x_i^{\rm lens}, y - y_i^{\rm lens}\right).
+\delta^2\left(x - x_i^{\rm lens}, y - y_i^{\rm lens}\right).
 \end{eqnarray}
@@
 \begin{eqnarray}
+\frac{1}{n}
 \sum_{k=1}^n
@@
 \delta^2\left(x - x_i^{\rm lens}, y_i^{\rm lens} - y_i^{\rm lens}\right)
-\, d\boldsymbol{\theta}
 \end{eqnarray}
@@
 if a substructure appears in a pixel or zero otherwise.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{simdata_masses.pdf}
+\caption{The joint posterior distribution for the SIE mass (integrated within
+its critical ellipse, which is not the critical curve of the lens overall),
+and the total mass in substructures.\label{fig:simdata_masses}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{N_lens.pdf}
+\caption{The marginal posterior distribution for $N_{\rm lens}$, the
+number of substructures in the lens.\label{fig:N_lens}}
+\end{center}
+\end{figure}
 

### 2015-06-26 Papers/ms.tex
long caption

@@
 \caption{The marginal posterior distribution for $N_{\rm lens}$, the
-number of substructures in the lens.\label{fig:N_lens}}
+number of substructures in the lens. The prior was uniform and the true
+value used to generate the data was 1. However, the data is only informative
+enough to suppress the probability of values above 1 slightly, since it
+is possible (given this data) that low mass substructures might exist somewhere,
+or that what we think is one substructure might actually be two close together,
+and other such possibilities.
+\label{fig:N_lens}}
 \end{center}

### 2015-06-26 Papers/ms.tex
SIE mass

@@
 
+The masses of the smooth and substructure components of the lens are usually
+of interest. Since the total mass of an SIE lens is infinite, the question
+needs to be redefined, so we ask about the mass within some aperture of finite
+area. For an SIE, the mass (in dimensionless units) within the critical
+ellipse is simply $b^2$.
+
 \begin{figure}

### 2015-06-26 Papers/ms.tex
Bit more

@@
 area. For an SIE, the mass (in dimensionless units) within the critical
-ellipse is simply $b^2$.
+ellipse is simply $b^2$. However, the blobs have finite total masses
+$\{M_i\}$. To obtain the posterior distribution for the lens masses, one must
+be clear about exactly which mass they are talking about, and many definitions
+are possible, although some might be more meaningful or well constrained than
+others.
+
+In Figure~\ref{fig:simdata_masses}, we plot the joint posterior distribution
+for the SIE mass within its critical ellipse and the total substructure mass
+over the entire domain.
 

### 2015-06-29 display.py
Image with substructures on it

@@ -16,6 +16,8 @@ metadata = loadtxt('Data/mock_metadata.txt')
 
 total = zeros((metadata[0]*metadata[7], metadata[1]*metadata[7]))
 magnification = zeros(output.shape[0])
+all_substructures_x = array([])
+all_substructures_y = array([])
 
 figure(figsize=(12, 8))
 ion()
@@ -96,6 +98,10 @@ for i in xrange(0, output.shape[0]):
 	total += src
 	magnification[i] = 2.5*log10(metadata[7]**2*img2.sum()/src.sum())
 
+	# Accumulate these before converting to pixels
+	all_substructures_x = hstack([all_substructures_x, x_substructures])
+	all_substructures_y = hstack([all_substructures_y, y_substructures])
+
 ioff()
 show()
 
@@ -126,5 +132,17 @@ gca().set_xticks(arange(0, 11))
 xlabel('$N_{\\rm lens}$')
 ylabel('Number of Posterior Samples')
 savefig('N_lens.pdf', bbox_inches='tight')
+show()
+
+figure(4, figsize=(8, 8))
+imshow(data, interpolation="nearest", cmap="Oranges")
+hold(True)
+plot(all_substructures_x, all_substructures_y, 'k.', markersize=3)
+gca().set_xticks([])
+gca().set_yticks([])
+xlim([-0.5, metadata[1] - 0.5])
+ylim([metadata[0] - 0.5, -0.5])
+title('Substructure Positions')
+savefig('substructures.pdf', bbox_inches='tight')
 show()
 

### 2015-06-29 Papers/ms.tex
comment on mass posterior
Include the substructure figure

@@
 for the SIE mass within its critical ellipse and the total substructure mass
-over the entire domain.
+over the entire domain. As one would expect, there is a strong dependence
+between these two quantities in the posterior distribution, as mass in the
+SIE can be traded off with mass in substructures to some extent, while
+the model remains (loosely speaking) ``consistent with the data''.
 
@@
 \label{fig:N_lens}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{substructures.pdf}
+\caption{The simulated data, with substructure positions overlaid (a
+Monte Carlo approximation to the posterior expectation of the empirical
+measure).
+\label{fig:substructures}}
 \end{center}

### 2015-06-29 Papers/ms.tex
Horseshoe figures
Comment out old stuff

@@
 
- \begin{figure*}
-% \hspace{20pt}
-\begin{subfigure}{.45\textwidth}
-  \centering
-  \includegraphics[width=0.75\linewidth,angle=90]{log_mass_SIE_no_blobs.eps}
-\parbox{0.8\linewidth}{\caption{The log of the SIE mass within the critical curve  for model A.  \label{fig:sub1} }}
-\end{subfigure}%
-\begin{subfigure}{.45\textwidth}
-  \centering
-  \includegraphics[width=0.75\linewidth,angle=90]{log_mass_SIE.eps}
-   \parbox{0.8\linewidth}{\caption{The log of the SIE mass within the critical curve for model B.   \label{fig:sub2}}}
-\end{subfigure}
-   \end{figure*}
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{masses2.pdf}
+\caption{The joint posterior distribution for the SIE mass (integrated within
+its critical ellipse, which is not the critical curve of the lens overall),
+and the total mass in substructures.\label{fig:simdata_masses}}
+\end{center}
+\end{figure}
 
-After choosing the prior probabilities one has to initialized the Dnest-code, which mean incorporating the problem specific information for
- example dimensions of the images in pixels, image size in arc-seconds, information on the PSF etc in the metadata file. 
- Besides these problem specific parameters, there are also several other parameters concerning the performance of code which need to be
-  edited in the OPTION file. After these initialization, we ran a test run to explore the amount of necessary levels, and length of the run.
- A sufficiently amount of levels correlates with good degree of mixing, and the length of the run is associated with the larger sample
-  size.
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{N_lens2.pdf}
+\caption{\label{fig:N_lens2}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{substructures2.pdf}
+\caption{\label{fig:substructures2}}
+\end{center}
+\end{figure}
+
+% \begin{figure*}
+%% \hspace{20pt}
+%\begin{subfigure}{.45\textwidth}
+%  \centering
+%  \includegraphics[width=0.75\linewidth,angle=90]{log_mass_SIE_no_blobs.eps}
+%\parbox{0.8\linewidth}{\caption{The log of the SIE mass within the critical curve  for model A.  \label{fig:sub1} }}
+%\end{subfigure}%
+%\begin{subfigure}{.45\textwidth}
+%  \centering
+%  \includegraphics[width=0.75\linewidth,angle=90]{log_mass_SIE.eps}
+%   \parbox{0.8\linewidth}{\caption{The log of the SIE mass within the critical curve for model B.   \label{fig:sub2}}}
+%\end{subfigure}
+%   \end{figure*}
+
+%After choosing the prior probabilities one has to initialized the Dnest-code, which mean incorporating the problem specific information for
+% example dimensions of the images in pixels, image size in arc-seconds, information on the PSF etc in the metadata file. 
+% Besides these problem specific parameters, there are also several other parameters concerning the performance of code which need to be
+%  edited in the OPTION file. After these initialization, we ran a test run to explore the amount of necessary levels, and length of the run.
+% A sufficiently amount of levels correlates with good degree of mixing, and the length of the run is associated with the larger sample
+%  size.
 After one test run, the amount levels was adapted to 120, and the amount iterations was change to 5000 iterations, for model A this resulted in the effective sample size of 940, and for model B this resulted in the effective sample size of 757.
@@
 \\
-Throughout the paper the standard cosmology was used for the analysis:  $H_0=70 \rm{km~s^{-1} ~pc^{-1}}$,  $\Omega_m = 0.3$,and  $\Omega_\Lambda= 0.7$. 
-The first test would to compare the SIE-mass of the models with the mass obtained in previous  work \cite{Belokurov2007} \cite{Dye2008}.
-Using model A the median  calculated SIE mass within the critical curve in solar masses is  $(5.34 \pm 0.046) \cdot 10^{12} M_\odot$, % (using median + STDDEV)
-which is comparable with previous work which gave the enclosed (cylindriacal) mass $(5.4 \pm 0.09) \cdot 10^{12} M_\odot$ \cite{Belokurov2007} and  mass within the Einstein-ring $(5.02 \pm 0.09) \cdot 10^{12} M_\odot$ \cite{Dye2008}.
+%Throughout the paper the standard cosmology was used for the analysis:  $H_0=70 \rm{km~s^{-1} ~pc^{-1}}$,  $\Omega_m = 0.3$,and  $\Omega_\Lambda= 0.7$. 
+%The first test would to compare the SIE-mass of the models with the mass obtained in previous  work \cite{Belokurov2007} \cite{Dye2008}.
+%Using model A the median  calculated SIE mass within the critical curve in solar masses is  $(5.34 \pm 0.046) \cdot 10^{12} M_\odot$, % (using median + STDDEV)
+%which is comparable with previous work which gave the enclosed (cylindriacal) mass $(5.4 \pm 0.09) \cdot 10^{12} M_\odot$ \cite{Belokurov2007} and  mass within the Einstein-ring $(5.02 \pm 0.09) \cdot 10^{12} M_\odot$ \cite{Dye2008}.
 Figure \ref{fig:sub1} displays the histogram of the enclosed mass within an Einstein ring of $5"$, it displays a very well confined probability distribution of the mass.
 \\
-Using model B the median calculated SIE mass within the critical curve in solar masses is  $(5.34 \pm 0.046) \cdot 10^{12} M_\odot$, % (using median + STDDEV)
-which is slightly smaller compared to the masses obtained with model A and the masses from previous work mentioned above.
+%Using model B the median calculated SIE mass within the critical curve in solar masses is  $(5.34 \pm 0.046) \cdot 10^{12} M_\odot$, % (using median + STDDEV)
+%which is slightly smaller compared to the masses obtained with model A and the masses from previous work mentioned above.
 Which is also not unexpected, because models where the SIE-mass is smaller can compensate by adding a satellite near by.
@@
 \\
-
-\begin{figure}[!h]
-\hspace{5pt}
-\begin{subfigure}{.45\textwidth}
-  \centering
-  \includegraphics[width=0.7\linewidth,angle=90]{log_total_mass_blob.eps}
-\parbox{0.8\linewidth}{\caption{The log of the total mass of the satellites for model B.   \label{fig:sub3}}}
-\end{subfigure}%
-\hspace{-15pt}
-\begin{subfigure}{.45\textwidth}
-  \centering
-  \vspace{6pt}
-  \includegraphics[width=0.7\linewidth,angle=90]{log_total_mass_blobs_within_ring.eps}
-\parbox{0.8\linewidth}{\caption{The log of the total mass of the satellites within the fixed Einstein-radius for model B.  \label{fig:sub4} }}
-\end{subfigure}
-   \end{figure}
-\vspace{-15pt}
-\noindent Another interesting aspect is the mass of the satellites.
+% 
+%\begin{figure}[!h]
+%\hspace{5pt}
+%\begin{subfigure}{.45\textwidth}
+%  \centering
+%  \includegraphics[width=0.7\linewidth,angle=90]{log_total_mass_blob.eps}
+%\parbox{0.8\linewidth}{\caption{The log of the total mass of the satellites for model B.   \label{fig:sub3}}}
+%\end{subfigure}%
+%\hspace{-15pt}
+%\begin{subfigure}{.45\textwidth}
+%  \centering
+%  \vspace{6pt}
+%  \includegraphics[width=0.7\linewidth,angle=90]{log_total_mass_blobs_within_ring.eps}
+%\parbox{0.8\linewidth}{\caption{The log of the total mass of the satellites within the fixed Einstein-radius for model B.  \label{fig:sub4} }}
+%\end{subfigure}
+%   \end{figure}
+%\vspace{-15pt}
+%\noindent Another interesting aspect is the mass of the satellites.
 Figure \ref{fig:sub3} displays a histogram of the logarithm of the total mass of the satellites per sample.
@@
 Figure \ref{fig:sub5} display a histogram of the log of the total mass of the SIE and the satellites within the Einstein radius, which clearly looks very similar to \ref{fig:sub1}.
-Figure \ref{fig:sub6} display a plot of the total mass of the SIE versus mass of the satellites within the Einstein radius whichs  negative correlation of approximately 
-\begin{equation}
- \sum M_{satellites} = 5\cdot10^{12} - M_{SIE}
- \end{equation}
+%Figure \ref{fig:sub6} display a plot of the total mass of the SIE versus mass of the satellites within the Einstein radius whichs  negative correlation of approximately 
+%\begin{equation}
+% \sum M_{satellites} = 5\cdot10^{12} - M_{SIE}
+% \end{equation}
 
-The main conclusion of the analysis of the datasets of model A and model B, would be that the application of the DNest code with a free amount of satellite galaxies return a well matching model which is very similar to to the model without any satellites, this proves
-even though the code has the freedom the explore and create all sort of models, it confirms that the already known distribution is very probable.
+%The main conclusion of the analysis of the datasets of model A and model B, would be that the application of the DNest code with a free amount of satellite galaxies return a well matching model which is very similar to to the model without any satellites, this proves
+%even though the code has the freedom the explore and create all sort of models, it confirms that the already known distribution is very probable.
 This shows how well the code works, and beside that it is also good indication that the well established SIE model for this system doesn't need additional satellites to explain the system.
+% 
+%\begin{figure}
+%\hspace{10pt}
+%\begin{subfigure}{.5\textwidth}
+%\vspace{-12pt}
+%  \centering
+%  \includegraphics[width=0.75\linewidth,angle=90]{mass_SIE_plus_blob_mass.eps}
+%\parbox{0.8\linewidth}{\caption{The log of add mass of the satellites and SIE within the fixed Einstein-radius for model B.   \label{fig:sub5}}}
+%\end{subfigure}
+%\begin{subfigure}{.5\textwidth}
+%  \centering
+%  \includegraphics[width=0.75\linewidth,angle=90]{joint.eps}
+%\parbox{0.8\linewidth}{\caption{Plot of the log of the total mass of the satellites within the fixed Einstein-radius versus the 
+%log of the SIE mass within the Einstein radius for model B.  \label{fig:sub6} }}
+%\end{subfigure}
 
-\begin{figure}
-\hspace{10pt}
-\begin{subfigure}{.5\textwidth}
-\vspace{-12pt}
-  \centering
-  \includegraphics[width=0.75\linewidth,angle=90]{mass_SIE_plus_blob_mass.eps}
-\parbox{0.8\linewidth}{\caption{The log of add mass of the satellites and SIE within the fixed Einstein-radius for model B.   \label{fig:sub5}}}
-\end{subfigure}
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=0.75\linewidth,angle=90]{joint.eps}
-\parbox{0.8\linewidth}{\caption{Plot of the log of the total mass of the satellites within the fixed Einstein-radius versus the 
-log of the SIE mass within the Einstein radius for model B.  \label{fig:sub6} }}
-\end{subfigure}
+%   \end{figure}
 
-   \end{figure}
+%  
+%
 
-\section{ER 0047-2808}
-We demonstrate the method on the HST images of ER 0047-2808.
+%\section{ER 0047-2808}
+%We demonstrate the method on the HST images of ER 0047-2808.
 

### 2015-06-30 Papers/ms.tex
linking sentence

@@
 
-In Figure~\ref{fig:simdata_masses}, we plot the joint posterior distribution
+We do not address the question of exactly which quantities related to the
+\density profile of the lens are most scientifically interesting. Nevertheless,
+we can verify that the results of the inference do behave in understandable
+ways. For example, in Figure~\ref{fig:simdata_masses},
+we plot the joint posterior distribution
 for the SIE mass within its critical ellipse and the total substructure mass
@@
 the model remains (loosely speaking) ``consistent with the data''.
-
 \begin{figure}

### 2015-06-30 Papers/ms.tex
Paragraph on N posterior

@@
 
+The posterior distribution for $N_{\rm lens}$ is also clearly of interest, and
+is displayed in Figure~\ref{fig:N_lens}. The prior for this parameter was
+uniform from 0 to 10 (inclusive), and the possibility $N=0$ has been
+(loosely speaking) ``ruled out'' by the image data. The true solution ($N=1$)
+has the highest probability. However, the possibilities with $N > 1$ are
+still fairly plausible, since it's possible that a very small substructure
+exists, and it's also possible that two substructures near each other could
+mimic the effect of one. The degree to which these possibilities are plausible
+is related to the choice of prior for the blob amplitudes and positions.
+
 \begin{figure}

### 2015-06-30 Papers/ms.tex
Z and H

@@
 We do not address the question of exactly which quantities related to the
-\density profile of the lens are most scientifically interesting. Nevertheless,
+density profile of the lens are most scientifically interesting. Nevertheless,
 we can verify that the results of the inference do behave in understandable
@@
 \end{figure}
+
+The estimated marginal likelihood of our model
+(averaged over all parameters including $N_{\rm lens}$ and $N_{\rm src}$)
+is
+$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -14249$, and
+the information (Kullback-Leibler divergence from the prior to the posterior)
+is $\mathcal{H} \approx 100$ nats.
 

### 2015-07-01 Papers/ms.tex
horseshoe numbers
Going through the paper making edits from the top

@@
 \title[]
-{Trans-Dimensional Inference for Gravitational Lens Substructures}
+{Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures}
 
@@
 a superposition of an unknown number of non-negative basis functions
-(or ``blobs'') which were chosen with speed as a primary criterion.
+(or ``blobs'') whose form was chosen with speed as a primary criterion.
 The prior distribution for the blobs' properties is specified hierarchically,
-so the ``mass function'' of substructures is a natural output. We use reversible
+so the ``mass function'' of substructures is a natural output of the method.
+We use reversible
 jump Markov Chain Monte Carlo (MCMC) within Diffusive Nested Sampling (DNS) to
 sample the posterior distribution and evaluate the marginal likelihood of the
-model. We demonstrate the method on a simulated data set with a single
+model parameters including the number of blobs in the source and the lens.
+We demonstrate the method on a simulated data set with a single
 substructure, which is recovered well with moderate uncertainties. We also
-apply the method to an image of the ``Cosmic Horseshoe'' lens, and find some
+apply the method to an image of the ``Cosmic Horseshoe'' system, and find some
 hints of potential substructures. However, we caution that such results could
-also be attributed to misspecifications in the model (such as the shape of
+also be caused by misspecifications in the model (such as the shape of
 the smooth lens component or the point spread function),
@@
 which are thought to contain at least one dark substructure
-\citep{vegetti1, vegetti2, vegetti3}. The present paper describes an
-approach we have developed for the inverse problem of detecting dark
-substructures from image data. However, it may also prove useful in other
-galaxy-galaxy lens modelling areas, such as time-delay cosmography, which
-requires realistically flexible lens models, and reliable uncertainty
-quantification
+\citep{vegetti1, vegetti2, vegetti3}. In these studies, the lens was modelled
+as a superposition of a smooth component (such as an elliptical power-law
+matter distribution) plus a pixellized ``non-parametric'' correction term.
+The estimated spatial structure of the correction term provides clues about
+the locations of possible substructures. In a second modelling step, the lens
+is assumed to be a smooth overall component plus a compact ``blob'' near any
+locations suggested by the correction term.
+
+We have developed an approach for solving this same problem (inferring the
+number and properties of dark substructures given an image) in a more direct
+fashion. However, with appropriate modifications, it may also prove useful in other
+galaxy-galaxy lens modelling areas. One example is time-delay cosmography, which
+requires realistically flexible lens models, and reliable quantification
+of the uncertainties
 \citep{2013ApJ...766...70S, 2014ApJ...788L..35S, grillo}.
@@
 
-We do not address the question of exactly which quantities related to the
+In the present paper we do not address the question of exactly which quantities
+related to the
 density profile of the lens are most scientifically interesting. Nevertheless,
@@
 \end{figure}
+
+The estimated marginal likelihood of our model
+is
+$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -6968$, and
+the information (Kullback-Leibler divergence from the prior to the posterior)
+is $\mathcal{H} \approx 129$ nats.
 

### 2015-07-01 Papers/ms.tex
More editing

@@
 
-In this paper we address the topic of
-inferring the matter distribution in the lens galaxy from the lensed,
-blurred image. These approaches may be categorized according to the following
-criteria:
+Lens modelling has been a topic of much interest over the last two decades.
+Most approaches are based on Bayesian inference or maximum likelihood or
+variations thereof. These approaches may be categorized according to the
+following criteria:
 \begin{enumerate}
-\item Whether to use a simply parameterized (e.g. Sérsic), moderately flexible
-(e.g. mixture model, \citet{2011MNRAS.412.2521B})
+\item Whether to use a simply parameterized (e.g. a Sérsic profile),
+moderately flexible (e.g. a mixture model, \citet{2011MNRAS.412.2521B})
 or free-form (e.g. pixellated) model for the surface brightness profile of the source
@@
 \item How to compute the results (e.g. optimization methods, Markov Chain
-Monte Carlo with or without source parameters marginalized out).
+Monte Carlo with source parameters marginalized out analytically, or
+with the source parameters included).
 \end{enumerate}
 
-Many different approaches have been proposed and applied to
-this problem. Recent sophisicated approaches to
+Recent sophisicated approaches to
 this problem include \citet{2014MNRAS.445.2181C},

### 2015-07-02 Papers/ms.tex
Longer caption

@@
 \caption{A probabilistic graphical model (PGM) of the dependence structure
-of the prior information.\label{fig:pgm}}
+of the prior information, produced using DAFT ({\tt www.daft-pgm.org}).
+The prior for the source and lens blob parameters are specified conditional
+on hyperparameters. The purpose of this is to induce dependence in the prior
+distribution for the blob parameters, implying (for example) that the mass of
+one blob is slightly informative about the mass of another, and that the
+locations might be clustered around a certain typical location.
+\label{fig:pgm}}
 \end{figure*}

### 2015-07-02 Papers/ms.tex
Para about computational cost

@@
 
+We generated 5,000 samples from the DNest target distribution and thinned
+by a factor of $10^5$, so $5 \times 10^8$ MCMC iterations were actually
+performed, taking approximately 36 hours. After resampling, this resulted in 805
+equally weighted posterior samples. Although this image is smaller than the
+simulated data ($46 \times 46$ pixels), we fired $2 \times 2$ rays per pixel
+for greater accuracy.
+
 %The field of view of the image is $15.3180" \times 15.3180"$, and the size is $46 \times 46$ pixels, therefore one pixel is equivalent to $0.33"$. \\

### 2015-07-03 Papers/ms.tex
Important reminder
SIE reference

@@
 
-The differences between the approaches can be broken down into
-i) different assumptions about the prior information being used, and ii)
-different computational methods used to compute the results.
 Each approach involves tradeoffs between convenience and realism.
 Simply parameterized models, such as Sérsic surface
-brightness profiles for the source, and singular isothermal ellipsoid plus
-external shear (SIE+$\gamma$) models for the lens, are very
+brightness profiles for the source,
+and singular isothermal ellipsoid plus
+external shear (SIE+$\gamma$) models for the lens \citep{1994A&A...284..285K},
+are very
 convenient. They only have a few adjustable parameters, and they capture
@@
 
+\bibitem[\protect\citeauthoryear{Kormann, Schneider, 
+\& Bartelmann}{1994}]{1994A&A...284..285K} Kormann R., Schneider P., Bartelmann M., 1994, A\&A, 284, 285
+
 \bibitem[\protect\citeauthoryear{O'Hagan and Forster}{2004}]{ohagan}

### 2015-07-03 Papers/ms.tex
Discussing other papers

@@
 Lens modelling has been a topic of much interest over the last two decades.
-Most approaches are based on Bayesian inference or maximum likelihood or
+Most approaches are based on Bayesian inference, maximum likelihood or
 variations thereof. These approaches may be categorized according to the
@@
 blurred noise). These priors also assign nonzero probability to negative
-surface brightness or density values.
+surface brightness or density values; in fact, the marginal prior probability
+that any pixel is negative is 0.5.
 
@@
 modelling approach lies somewhere between simply-parameterised and
-pixellated models.
+pixellated models. One way of achieving this is with mixture models.
 The source and the lens can be built up from a mixture of a moderate
@@
 nearby point) and the fact that most of the sky is
-dark \citep{2006ApJ...637..608B}. The main differences between the
-\citet{2011MNRAS.412.2521B} and that of the present approach are:
-i) we use a simpler and faster basis set, and ii) we apply it to the lens
-as well as the source. However, in the present paper we do not account for
+dark \citep{2006ApJ...637..608B}. The \citet{2011MNRAS.412.2521B} model also
+allowed for multi-band data, and allowed for our expectation that the image
+may or may not be similar in different bands.
+
+The present paper is similar in approach to \citet{2011MNRAS.412.2521B}.
+The main differences are:
+i) we use a simpler and faster set of basis functions,
+ii) we apply it to the lens as well as the source, and
+iii) the implementation is based on a C++ template library developed by
+\citet{rjobject} which allows for hierarchical priors and trans-dimensional
+MCMC to be implemented in a relatively straightforward manner.
+However, in the present paper we do not account for
 multi-band data.

### 2015-07-03 Papers/ms.tex
Mass function talk edits

@@
 The prior distribution for the blobs' properties is specified hierarchically,
-so the ``mass function'' of substructures is a natural output of the method.
+so the mass function of substructures is a natural output of the method.
 We use reversible
@@
 
-For the lens, if we are interested in detecting and measuring the properties of
-dark substructures, a superposition of an unknown number of ``blobs'' is the
-most natural model. In addition, if we want to constrain the ``mass function'' of
-these blobs, we will need a hierarchical model which specifies the probability
-distribution for the masses, conditional on some hyperparameters. Inferring the
+\section{Finding dark substructures}
+If we are interested in detecting and measuring the properties of
+possible dark substructures in a lens galaxy,
+a superposition of an unknown number of ``blobs'' is the
+most natural model. In addition, if we want to constrain the mass function of
+these blobs \citep[e.g.][]{2009MNRAS.400.1583V, 2014MNRAS.442.2017V},
+we will need a hierarchical model which specifies the prior probability
+distribution for the masses conditional on some hyperparameters. Inferring the
 mass function of the blobs then reduces to calculating the posterior
@@
 
+\bibitem[\protect\citeauthoryear{Vegetti 
+\& Koopmans}{2009}]{2009MNRAS.400.1583V} Vegetti S., Koopmans L.~V.~E., 2009, MNRAS, 400, 1583
+
 \bibitem[\protect\citeauthoryear{Vegetti et 
@@
 Auger M.~W., Fassnacht C.~D., Koopmans L.~V.~E., 2012, Natur, 481, 341
+
+\bibitem[\protect\citeauthoryear{Vegetti, Czoske, 
+\& Koopmans}{2010}]{vegetti3} Vegetti S., Czoske O., Koopmans L.~V.~E., 2010, MNRAS, 407, 225
 
@@
 
-\bibitem[\protect\citeauthoryear{Vegetti, Czoske, 
-\& Koopmans}{2010}]{vegetti3} Vegetti S., Czoske O., Koopmans L.~V.~E., 2010, MNRAS, 407, 225
+\bibitem[\protect\citeauthoryear{Vegetti et 
+al.}{2014}]{2014MNRAS.442.2017V} Vegetti S., Koopmans L.~V.~E., Auger 
+M.~W., Treu T., Bolton A.~S., 2014, MNRAS, 442, 2017
 

### 2015-07-03 Papers/ms.tex
Dimensionality of the source parameter space

@@
 distribution for the hyperparameters.
-
 Computing the posterior distribution over the parameters of such a model
@@
 \end{eqnarray}
+
+The dimensionality of the parameter space for the source depends on the
+minimum and maximum values of $N_{\rm src}$, which we set to 0 and 100
+respectively (more detail about priors is given in Section~\ref{sec:priors}).
+Therefore the source is described by 1 -- 401 parameters.
 
@@
 
-\section{Prior Probability Distributions}
+\section{Prior Probability Distributions}\label{sec:priors}
 The prior probability distributions for all hyperparameters, parameters, and

### 2015-07-03 Papers/ms.tex
conditional prior

@@
 
+The conditional prior for the data given the parameters
+is a product of independent gaussian distributions, one for each pixel.
+This is conventionally called the ``sampling distribution'', or sometimes just the ``likelihood''. However, sampling distribution is misleading since no
+physical frequency distribution exists which is being sampled from. The term
+likelihood is also usually used to refer to the scalar function of the parameters
+obtained when the data are known. For a discussion of the view that this
+object is really a prior distribution, see \citet[][pp. 33--35]{caticha}.
+
 \section{Computation}
@@
 
+\newpage
+The conditional prior for the data given the parameters
+is a product of independent gaussian distributions, one for each pixel.
+This is conventionally called the ``sampling distribution'', or sometimes just the ``likelihood''. However, sampling distribution is misleading since no
+physical frequency distribution exists which is being sampled from. The term
+likelihood is also usually used to refer to the scalar function of the parameters
+obtained when the data are known. For a discussion of the view that this
+object is really a prior distribution, see \citet[][pp. 33--35]{caticha}.
+
 \section*{Acknowledgements}
@@
 \& Donovan}{2015}]{exoplanet} Brewer B.~J., Donovan C.~P., 2015, MNRAS, 448, 3206
+
+\bibitem[Caticha(2008)]{caticha} Caticha, A.\ 2008.\ Lectures 
+on Probability, Entropy, and Statistical Physics.\ ArXiv e-prints 
+arXiv:0808.0012.
 

### 2015-07-03 Papers/ms.tex
Removed duplicate para
Editing and writing about noise variances

@@
 distribution for the hyperparameters.
-Computing the posterior distribution over the parameters of such a model
-requires that we can implement Markov Chain Monte Carlo (MCMC) over the space
-of possible sources and lenses.
 
@@
 
+\subsection{Conditional prior for the data}
 The conditional prior for the data given the parameters
 is a product of independent gaussian distributions, one for each pixel.
-This is conventionally called the ``sampling distribution'', or sometimes just the ``likelihood''. However, sampling distribution is misleading since no
+The mean of the gaussian is given by the ``mock'' noise-free image we would
+expect based on the parameters. The standard deviation of the gaussian is
+a combination of three terms; the first (denoted $s_{ij}$) is a ``noise map''
+which is loaded from a file, the second is an unknown constant $\sigma_0$
+which applies to the whole image, and the third is proportional to the
+square root of the mock image, with proportionality constant $\sigma_1$.
+
+This is usually called the ``sampling distribution'', or sometimes just the
+``likelihood''. However, sampling distribution is misleading since no
 physical frequency distribution exists which is being sampled from. The term
@@
 \section{Computation}
+Computing the posterior distribution over the parameters of such a model
+requires that we can implement Markov Chain Monte Carlo (MCMC) over the space
+of possible sources and lenses.
+
 To compute the posterior distribution for the parameters
@@
 
-\newpage
-The conditional prior for the data given the parameters
-is a product of independent gaussian distributions, one for each pixel.
-This is conventionally called the ``sampling distribution'', or sometimes just the ``likelihood''. However, sampling distribution is misleading since no
-physical frequency distribution exists which is being sampled from. The term
-likelihood is also usually used to refer to the scalar function of the parameters
-obtained when the data are known. For a discussion of the view that this
-object is really a prior distribution, see \citet[][pp. 33--35]{caticha}.
-
 \section*{Acknowledgements}

### 2015-07-03 Papers/ms.tex
(image width) --> {\tt imageWidth}

@@
 \hline
-$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times$(image width))\\
-$R_{\rm src}$   &	Typical distance of blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
+$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times${\tt imageWidth})\\
+$R_{\rm src}$   &	Typical distance of blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & LogUniform(0.01$\times${\tt imageWidth}, 10$\times${\tt imageWidth})\\
 $\mu_{\rm src}$ &	Typical flux of source blobs	& $\ln(\mu_{\rm src}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
-$W_{\rm max}^{\rm src}$ &		Maximum width of source blobs	& LogUniform(0.001$\times$(image width), image width)\\
+$W_{\rm max}^{\rm src}$ &		Maximum width of source blobs	& LogUniform(0.001$\times${\tt imageWidth}, {\tt imageWidth})\\
 $W_{\rm min}^{\rm src}$ &		Minimum width of source blobs	& Uniform(0, $W_{\rm max}^{\rm src}$)\\
@@
 \hline
-$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times$(image width))\\
-$R_{\rm lens}$  &	Typical distance of blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
+$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times${\tt imageWidth})\\
+$R_{\rm lens}$  &	Typical distance of blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& LogUniform(0.01$\times${\tt imageWidth}, 10$\times${\tt imageWidth})\\
 $\mu_{\rm lens}$&	Typical mass of lens blobs	& $\ln(\mu_{\rm lens}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
-$W_{\rm max}^{\rm lens}$ &		Maximum width of lens blobs	& LogUniform(0.001$\times$(image width), image width)\\
+$W_{\rm max}^{\rm lens}$ &		Maximum width of lens blobs	& LogUniform(0.001$\times${\tt imageWidth}, {\tt imageWidth})\\
 $W_{\rm min}^{\rm lens}$ &		Minimum width of lens blobs	& Uniform(0, $W_{\rm max}^{\rm lens}$)\\
@@
 \hline
-$b$ & SIE Einstein Radius & LogUniform(0.001$\times$(image width), image width)\\
+$b$ & SIE Einstein Radius & LogUniform(0.001$\times${\tt imageWidth}, {\tt imageWidth})\\
 $q$ & Axis ratio & Uniform(0, 0.95)\\
-$(x_c^{\rm SIE}, y_c^{\rm SIE})$ & Central position & iid Cauchy(location=$(0,0)$, scale=0.1$\times$(image width))\\
+$(x_c^{\rm SIE}, y_c^{\rm SIE})$ & Central position & iid Cauchy(location=$(0,0)$, scale=0.1$\times${\tt imageWidth})\\
 $\theta$ & Orientation angle & Uniform$(0, \pi)$\\

### 2015-07-03 Papers/ms.tex
fixed problem

@@
 $M_i$  & Blob mass & Exponential(mean=$\mu_{\rm lens}$)\\
-$v_i$  & Blob width & Uniform($W_{\rm min}^{\rm src}$, $W_{\rm max}^{\rm src}$)\\
+$v_i$  & Blob width & Uniform($W_{\rm min}^{\rm lens}$, $W_{\rm lens}^{\rm src}$)\\
 \hline
@@
 
+{\bf Comment on the (non-ideal)
+reproducibility of the results from the sampling and the effective sample size}.
+
 % \begin{figure*}

### 2015-07-03 Papers/ms.tex
Fixed fix :)

@@
 $M_i$  & Blob mass & Exponential(mean=$\mu_{\rm lens}$)\\
-$v_i$  & Blob width & Uniform($W_{\rm min}^{\rm lens}$, $W_{\rm lens}^{\rm src}$)\\
+$v_i$  & Blob width & Uniform($W_{\rm min}^{\rm lens}$, $W_{\rm max}^{\rm lens}$)\\
 \hline

### 2015-07-07 Papers/ms.tex
KL divergence def

@@
 the information (Kullback-Leibler divergence from the prior to the posterior)
-is $\mathcal{H} \approx 100$ nats.
+is $\mathcal{H} \approx 100$ nats. The definition of the information is:
+\begin{eqnarray}
+\mathcal{H} = \int p(\boldsymbol{\theta} | \boldsymbol{D})
+\ln\left[\frac{p(\boldsymbol{\theta} | \boldsymbol{D})}{p(\boldsymbol{\theta})}\right]
+\, d\boldsymbol{\theta}
+\end{eqnarray}
+and we can build intuition about its meaning based on some simple examples. One
+such example is a uniform prior over a volume $V_0$ and a posterior which is
+uniform over a smaller volume $V_1$ contained within $V_0$. In this case
+$\mathcal{H} = \ln(V_0/V_1)$ nats. Therefore, a value of $\mathcal{H}=100$ nats
+implies the posterior distribution occupies roughly $e^{-100}$ of the prior
+volume.
 

### 2015-07-07 Papers/ms.tex
Fadely
More about KL

@@
 is assumed to be a smooth overall component plus a compact ``blob'' near any
-locations suggested by the correction term.
+locations suggested by the correction term. This kind of inference has also
+been done with point-like multiple images of QSOs \citep{2012MNRAS.419..936F}.
 
@@
 the information (Kullback-Leibler divergence from the prior to the posterior)
-is $\mathcal{H} \approx 100$ nats. The definition of the information is:
+is $\mathcal{H} \approx 100$ nats. The information represents the degree of
+compression of the posterior distribution with respect to the prior, and can
+be interpreted quite literally as how much was learned about the parameters from
+the data. It is also straightforward to estimate from Nested Sampling
+\citep{skilling}. Its definition is:
 \begin{eqnarray}
@@
 
-{\bf Comment on the (non-ideal)
+\subsection{Reproducibility of the results}
+The ``effective sample size'' returned by DNest, which we have described as the
+number of posterior samples
 reproducibility of the results from the sampling and the effective sample size}.
@@
 
+\bibitem[\protect\citeauthoryear{Fadely 
+\& Keeton}{2012}]{2012MNRAS.419..936F} Fadely R., Keeton C.~R., 2012, MNRAS, 419, 936
+
 \bibitem[\protect\citeauthoryear{Green}{1995}]{rjmcmc}

### 2015-07-09 Papers/ms.tex
reproducibility

@@
 The ``effective sample size'' returned by DNest, which we have described as the
-number of posterior samples
-reproducibility of the results from the sampling and the effective sample size}.
+number of posterior samples, takes into account the fact DNest's target
+distribution is not the posterior. However, it does not take autocorrelation
+into account, and thus can present an optimistic picture of the accuracy of
+any Monte Carlo estimates of posterior expectations. Most standard diagnostic
+techniques used in MCMC can be applied here. The simplest of these is a
+check of reproducibility. If different runs yield substantially different
+results, the MCMC output should be treated with caution.
 

### 2015-07-15 lens_plots.jl
Started julia script to calculate critical curves etc

@@ -1,0 +1,23 @@
+# So we can use matplotlib
+using PyCall
+@pyimport matplotlib.pyplot as plt
+
+# Load the posterior samples
+posterior_sample = readdlm("posterior_sample.txt")
+# Size of the 2D array
+M = size(posterior_sample)[1]
+N = size(posterior_sample)[2]
+
+# Loop over samples
+for(i in 1:M)
+	# Get NIE parameters
+	b = posterior_sample[i, 3]
+	q = posterior_sample[i, 4]
+	rc = posterior_sample[i, 5]
+	xc = posterior_sample[i, 6]
+	yc = posterior_sample[i, 7]
+	theta = posterior_sample[i, 8]
+	shear = posterior_sample[i, 9]
+	theta_shear = posterior_sample[i, 10]
+end
+

### 2015-07-15 Lenses/BlobbyNIE.jl
Working on BlobbyNIE functions in Julia

@@ -1,0 +1,73 @@
+# Function to compute the deflection angles
+# at position (x, y), for the lens specified by
+# the parameters array (a row from sample.txt or posterior_sample.txt)
+function alpha(parameters, x, y)
+	# Get NIE parameters
+	b = posterior_sample[i, 3]
+	q = posterior_sample[i, 4]
+	rc = posterior_sample[i, 5]
+	xc = posterior_sample[i, 6]
+	yc = posterior_sample[i, 7]
+	theta = posterior_sample[i, 8]
+	shear = posterior_sample[i, 9]
+	theta_shear = posterior_sample[i, 10]
+
+	cos_theta = cos(theta)
+	sin_theta = sin(theta)
+	cos_theta_shear = cos(theta_shear)
+	sin_theta_shear = sin(theta_shear)
+
+	# Rotate and center
+	xx =  (x - xc)*cos_theta + (y - yc)*sin_theta
+	yy = -(x - xc)*sin_theta + (y - yc)*cos_theta
+
+	psi = sqrt(qq*qq*(xx*xx + rc*rc) + yy*yy)
+	alphax = bb/q_term*atan(q_term*xx/(psi + rc))
+	alphay = bb/q_term*atanh(q_term*yy/(psi + qq*qq*rc))
+
+	# Rotate back
+	ax = alphax*cos_theta - alphay*sin_theta;
+	ay = alphax*sin_theta + alphay*cos_theta;
+
+	# Go into shear coordinate system
+	xx =  x*cos_theta_shear + y*sin_theta_shear
+	yy = -x*sin_theta_shear + y*cos_theta_shear;
+
+	# Calculate external shear
+	alphax = -shear*xx;
+	alphay = shear*yy;
+
+	# Add external shear
+	ax += alphax*cos_theta_shear - alphay*sin_theta_shear;
+	ay += alphax*sin_theta_shear + alphay*cos_theta_shear;
+
+	return [ax, ay]
+end
+
+#void BlobbyNIE::alpha(double x, double y, double& ax, double& ay) const
+#{
+
+#	// Add blobs
+#	if(BlobbyNIE::disable_blobs)
+#		return;
+
+#	const vector< vector<double> >& components = blobs.get_components();
+#	double rsq, widthsq, Menc;
+#	for(size_t i=0; i<components.size(); i++)
+#	{
+#		rsq = pow(x - components[i][0], 2)
[…]

### 2015-07-15 lens_plots.jl

@@ -2,6 +2,8 @@
 using PyCall
 @pyimport matplotlib.pyplot as plt
 
+include("Lenses/BlobbyNIE.jl")
+
 # Load the posterior samples
 posterior_sample = readdlm("posterior_sample.txt")
 # Size of the 2D array
@@ -10,14 +12,6 @@ N = size(posterior_sample)[2]
 
 # Loop over samples
 for(i in 1:M)
-	# Get NIE parameters
-	b = posterior_sample[i, 3]
-	q = posterior_sample[i, 4]
-	rc = posterior_sample[i, 5]
-	xc = posterior_sample[i, 6]
-	yc = posterior_sample[i, 7]
-	theta = posterior_sample[i, 8]
-	shear = posterior_sample[i, 9]
-	theta_shear = posterior_sample[i, 10]
+	
 end
 

### 2015-07-15 Lenses/BlobbyNIE.jl
Finished (?) alpha function

@@ -1,21 +1,27 @@
 # Function to compute the deflection angles
 # at position (x, y), for the lens specified by
 # the parameters array (a row from sample.txt or posterior_sample.txt)
-function alpha(parameters, x, y)
+function alpha(parameters, x, y, cos_theta=cos(parameters[8]),
+								 sin_theta=sin(parameters[8]),
+								 cos_theta_shear=cos(parameters[10]),
+								 sin_theta_shear=sin(parameters[10]))
 	# Get NIE parameters
-	b = posterior_sample[i, 3]
-	q = posterior_sample[i, 4]
-	rc = posterior_sample[i, 5]
-	xc = posterior_sample[i, 6]
-	yc = posterior_sample[i, 7]
-	theta = posterior_sample[i, 8]
-	shear = posterior_sample[i, 9]
-	theta_shear = posterior_sample[i, 10]
+	b = posterior_sample[3]
+	q = posterior_sample[4]
+	rc = posterior_sample[5]
+	xc = posterior_sample[6]
+	yc = posterior_sample[7]
+	theta = posterior_sample[8]
+	shear = posterior_sample[9]
+	theta_shear = posterior_sample[10]
 
-	cos_theta = cos(theta)
-	sin_theta = sin(theta)
-	cos_theta_shear = cos(theta_shear)
-	sin_theta_shear = sin(theta_shear)
+	# Stuff derived from b and q
+	qq = q;
+	if(qq == 1.)
+		qq = 0.99999
+	end
+	q_term = sqrt(1. - qq*qq)
+	bb = b*sqrt(qq) # Minor axis
 
 	# Rotate and center
 	xx =  (x - xc)*cos_theta + (y - yc)*sin_theta
@@ -26,48 +32,35 @@ function alpha(parameters, x, y)
 	alphay = bb/q_term*atanh(q_term*yy/(psi + qq*qq*rc))
 
 	# Rotate back
-	ax = alphax*cos_theta - alphay*sin_theta;
-	ay = alphax*sin_theta + alphay*cos_theta;
+	ax = alphax*cos_theta - alphay*sin_theta
+	ay = alphax*sin_theta + alphay*cos_theta
 
 	# Go into shear coordinate system
 	xx =  x*cos_theta_shear + y*sin_theta_shear
-	yy = -x*sin_theta_shear + y*cos_theta_shear;
[…]

### 2015-07-15 lens_plots.jl

@@ -12,6 +12,6 @@ N = size(posterior_sample)[2]
 
 # Loop over samples
 for(i in 1:M)
-	
+	println(alpha(posterior_sample[i, :], 0., 0.,))
 end
 

### 2015-07-16 Lenses/BlobbyNIE.jl
Makes an image of magnifications, but it seems wrong

@@ -64,3 +64,28 @@ function alpha(parameters, x, y, cos_theta=cos(parameters[8]),
 	return [ax, ay]
 end
 
+function fire_ray(parameters, x, y)
+	(ax, ay) = alpha(parameters, x, y)
+	xs = x - ax
+	ys = y - ay
+	return [xs, ys]
+end
+
+# Compute the magnification at position (x, y).
+# h is the spacing for numerical differentiation
+function magnification(parameters, x, y, h=1E-6)
+	(xs1, ys1) = fire_ray(parameters, x + h, y)
+	(xs2, ys2) = fire_ray(parameters, x - h, y)
+
+	J11 = (xs1 - xs2)/(2*h)
+	J12 = (ys1 - ys2)/(2*h)
+
+	(xs1, ys1) = fire_ray(parameters, x, y + h)
+	(xs2, ys2) = fire_ray(parameters, x, y - h)
+
+	J21 = (xs1 - xs2)/(2*h)
+	J22 = (ys1 - ys2)/(2*h)
+
+	return -2.5*log10(abs(J11*J22 - J12*J21))
+end
+

### 2015-07-16 lens_plots.jl

@@ -10,8 +10,25 @@ posterior_sample = readdlm("posterior_sample.txt")
 M = size(posterior_sample)[1]
 N = size(posterior_sample)[2]
 
+# Make a grid
+x = linspace(-1, 1, 501)
+y = linspace(-1, 1, 501)
+
+# Function to calculate magnification on a grid
+function magnification_image(parameters, x, y)
+	mag = zeros(length(y), length(x))
+	for(j in 1:length(y))
+		for(i in 1:length(x))
+			mag[i, j] = magnification(parameters, x[i], y[j])
+		end
+	end
+	return mag
+end
+
 # Loop over samples
 for(i in 1:M)
-	println(alpha(posterior_sample[i, :], 0., 0.,))
+	mag = magnification_image(posterior_sample[i, :], x, y)
+	plt.imshow(mag, interpolation="nearest")
+	plt.show()
 end
 

### 2015-07-16 lens_plots.jl
The problem was just the image range

@@ -11,8 +11,8 @@ M = size(posterior_sample)[1]
 N = size(posterior_sample)[2]
 
 # Make a grid
-x = linspace(-1, 1, 501)
-y = linspace(-1, 1, 501)
+x = linspace(-10,  10, 501)
+y = linspace( 10, -10, 501)
 
 # Function to calculate magnification on a grid
 function magnification_image(parameters, x, y)

### 2015-07-16 lens_plots.jl
ion, draw, etc

@@ -6,6 +6,7 @@ include("Lenses/BlobbyNIE.jl")
 
 # Load the posterior samples
 posterior_sample = readdlm("posterior_sample.txt")
+
 # Size of the 2D array
 M = size(posterior_sample)[1]
 N = size(posterior_sample)[2]
@@ -26,9 +27,14 @@ function magnification_image(parameters, x, y)
 end
 
 # Loop over samples
+plt.ion()
+plt.hold(false)
 for(i in 1:M)
 	mag = magnification_image(posterior_sample[i, :], x, y)
-	plt.imshow(mag, interpolation="nearest")
-	plt.show()
+	plt.imshow(mag, interpolation="nearest", vmin=-10.0, vmax=10.0)
+	plt.title(i)
+	plt.draw()
 end
+plt.ioff()
+plt.show()
 

### 2015-07-16 Lenses/BlobbyNIE.jl
Fixed bug

@@ -6,21 +6,21 @@ function alpha(parameters, x, y, cos_theta=cos(parameters[8]),
 								 cos_theta_shear=cos(parameters[10]),
 								 sin_theta_shear=sin(parameters[10]))
 	# Get NIE parameters
-	b = posterior_sample[3]
-	q = posterior_sample[4]
-	rc = posterior_sample[5]
-	xc = posterior_sample[6]
-	yc = posterior_sample[7]
-	theta = posterior_sample[8]
-	shear = posterior_sample[9]
-	theta_shear = posterior_sample[10]
+	b = parameters[3]
+	q = parameters[4]
+	rc = parameters[5]
+	xc = parameters[6]
+	yc = parameters[7]
+	theta = parameters[8]
+	shear = parameters[9]
+	theta_shear = parameters[10]
 
 	# Stuff derived from b and q
 	qq = q;
-	if(qq == 1.)
+	if(qq == 1.0)
 		qq = 0.99999
 	end
-	q_term = sqrt(1. - qq*qq)
+	q_term = sqrt(1.0 - qq*qq)
 	bb = b*sqrt(qq) # Minor axis
 
 	# Rotate and center

### 2015-07-16 Papers/ms.tex
Updated things for new Horseshoe run

@@
 by a factor of $10^5$, so $5 \times 10^8$ MCMC iterations were actually
-performed, taking approximately 36 hours. After resampling, this resulted in 805
+performed, taking approximately 40 hours. The first 1/3 of the run was
+excluded as burn-in. After resampling, this resulted in 632
 equally weighted posterior samples. Although this image is smaller than the
@@
 is
-$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -6968$, and
+$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -6967$, and
 the information (Kullback-Leibler divergence from the prior to the posterior)
@@
 into account, and thus can present an optimistic picture of the accuracy of
-any Monte Carlo estimates of posterior expectations. Most standard diagnostic
+any Monte Carlo approximations to posterior quantities. Most standard diagnostic
 techniques used in MCMC can be applied here. The simplest of these is a

### 2015-07-16 Lenses/BlobbyNIE.jl
New functions

@@ -89,3 +89,31 @@ function magnification(parameters, x, y, h=1E-6)
 	return -2.5*log10(abs(J11*J22 - J12*J21))
 end
 
+# A version that keeps magnification less than 10
+function magnification2(parameters, x, y, h=1E-6)
+	mag = magnification(parameters, x, y, h)
+	if mag > 10.0
+		mag = 10.0
+	end
+	return mag
+end
+
+# Current terrible implementation: numerically differentiate
+# magnification (which itself involves numerical derivatives).
+# Better: actually do second derivatives properly
+function magnification_derivs(parameters, x, y, h=1E-6)
+	dmdx = (magnification2(parameters, x+h, y) -
+				magnification2(parameters, x-h, y))/(2*h)
+	dmdy = (magnification2(parameters, x, y+h) -
+				magnification2(parameters, x, y-h))/(2*h)
+	return [dmdx, dmdy]
+end
+
+# Do one step of a leapfrog integrator
+# on the position (x, y) in the lens plane,
+# treating the magnification as a potential
+function update!(parameters, x, y, current_mag=magnification2(parameters, x, y),
+					dt=1E-3)
+	
+end
+

### 2015-07-16 Lenses/BlobbyNIE.jl
Leapfrog

@@ -112,8 +112,11 @@ end
 # Do one step of a leapfrog integrator
 # on the position (x, y) in the lens plane,
 # treating the magnification as a potential
-function update!(parameters, x, y, current_mag=magnification2(parameters, x, y),
-					dt=1E-3)
-	
+function update(parameters, pos, vel, dt=1E-3)
+	pos = pos + 0.5*dt*vel
+	accel = magnification_derivs(parameters, pos[1], pos[2])
+	vel = vel + dt*accel
+	pos = pos + 0.5*dt*vel
+	return [pos, vel]
 end
 

### 2015-07-16 Lenses/BlobbyNIE.jl
Not really working but fixed a couple of issues

@@ -114,9 +114,25 @@ end
 # treating the magnification as a potential
 function update(parameters, pos, vel, dt=1E-3)
 	pos = pos + 0.5*dt*vel
-	accel = magnification_derivs(parameters, pos[1], pos[2])
+	accel = -magnification_derivs(parameters, pos[1], pos[2])
 	vel = vel + dt*accel
 	pos = pos + 0.5*dt*vel
-	return [pos, vel]
+	return (pos, vel)
+end
+
+function dynamics(parameters, pos=[0.0, 0.0], vel = [0.0, 0.0],
+						steps=10000, skip=10, dt=1E-3)
+	keep = Array(Float64, div(steps, skip), 2)
+
+	for(i in 1:steps)
+		(pos, vel) = update(parameters, pos, vel, dt)
+
+		if rem(i, skip) == 0
+			keep[div(i, skip), :] = pos
+			println(i)
+		end
+	end
+
+	return keep
 end
 

### 2015-07-17 Lenses/BlobbyNIE.jl
Plot trajectory on the magnification map

@@ -120,18 +120,37 @@ function update(parameters, pos, vel, dt=1E-3)
 	return (pos, vel)
 end
 
-function dynamics(parameters, pos=[0.0, 0.0], vel = [0.0, 0.0],
+# So we can use matplotlib
+using PyCall
+@pyimport matplotlib.pyplot as plt
+
+function dynamics(parameters; pos=[0.0, 0.0], vel=[0.0, 0.0],
 						steps=10000, skip=10, dt=1E-3)
+	# Output array
 	keep = Array(Float64, div(steps, skip), 2)
 
+	# Show the magnification map
+	plt.ion()
+	plt.hold(true)
+	plt.imshow(magnification_image(parameters, linspace(-10, 10, 501),
+												linspace(10, -10, 501)),
+				interpolation="nearest", extent=[-10, 10, -10, 10])
+	plt.draw()
+
+	# Move the par
 	for(i in 1:steps)
 		(pos, vel) = update(parameters, pos, vel, dt)
 
 		if rem(i, skip) == 0
+			plt.plot(pos[1], pos[2], "ko", markersize=1)
+			plt.draw()
 			keep[div(i, skip), :] = pos
 			println(i)
 		end
 	end
+
+	plt.ioff()
+	plt.show()
 
 	return keep
 end

### 2015-07-17 lens_plots.jl

@@ -11,10 +11,6 @@ posterior_sample = readdlm("posterior_sample.txt")
 M = size(posterior_sample)[1]
 N = size(posterior_sample)[2]
 
-# Make a grid
-x = linspace(-10,  10, 501)
-y = linspace( 10, -10, 501)
-
 # Function to calculate magnification on a grid
 function magnification_image(parameters, x, y)
 	mag = zeros(length(y), length(x))
@@ -26,15 +22,20 @@ function magnification_image(parameters, x, y)
 	return mag
 end
 
-# Loop over samples
-plt.ion()
-plt.hold(false)
-for(i in 1:M)
-	mag = magnification_image(posterior_sample[i, :], x, y)
-	plt.imshow(mag, interpolation="nearest", vmin=-10.0, vmax=10.0)
-	plt.title(i)
-	plt.draw()
-end
-plt.ioff()
-plt.show()
+## Loop over samples
+## Make a grid
+#x = linspace(-10,  10, 501)
+#y = linspace( 10, -10, 501)
+#plt.ion()
+#plt.hold(false)
+#for(i in 1:M)
+#	mag = magnification_image(posterior_sample[i, :], x, y)
+#	plt.imshow(mag, interpolation="nearest", vmin=-10.0, vmax=10.0)
+#	plt.title(i)
+#	plt.draw()
+#end
+#plt.ioff()
+#plt.show()
+
+dynamics(posterior_sample[1, :], pos=[0, 5], skip=10, dt=0.01)
 

### 2015-07-17 Lenses/BlobbyNIE.jl
Abandon that idea -- we only need a contour

@@ -89,69 +89,3 @@ function magnification(parameters, x, y, h=1E-6)
 	return -2.5*log10(abs(J11*J22 - J12*J21))
 end
 
-# A version that keeps magnification less than 10
-function magnification2(parameters, x, y, h=1E-6)
-	mag = magnification(parameters, x, y, h)
-	if mag > 10.0
-		mag = 10.0
-	end
-	return mag
-end
-
-# Current terrible implementation: numerically differentiate
-# magnification (which itself involves numerical derivatives).
-# Better: actually do second derivatives properly
-function magnification_derivs(parameters, x, y, h=1E-6)
-	dmdx = (magnification2(parameters, x+h, y) -
-				magnification2(parameters, x-h, y))/(2*h)
-	dmdy = (magnification2(parameters, x, y+h) -
-				magnification2(parameters, x, y-h))/(2*h)
-	return [dmdx, dmdy]
-end
-
-# Do one step of a leapfrog integrator
-# on the position (x, y) in the lens plane,
-# treating the magnification as a potential
-function update(parameters, pos, vel, dt=1E-3)
-	pos = pos + 0.5*dt*vel
-	accel = -magnification_derivs(parameters, pos[1], pos[2])
-	vel = vel + dt*accel
-	pos = pos + 0.5*dt*vel
-	return (pos, vel)
-end
-
-# So we can use matplotlib
-using PyCall
-@pyimport matplotlib.pyplot as plt
-
-function dynamics(parameters; pos=[0.0, 0.0], vel=[0.0, 0.0],
-						steps=10000, skip=10, dt=1E-3)
-	# Output array
-	keep = Array(Float64, div(steps, skip), 2)
-
-	# Show the magnification map
-	plt.ion()
-	plt.hold(true)
-	plt.imshow(magnification_image(parameters, linspace(-10, 10, 501),
-												linspace(10, -10, 501)),
-				interpolation="nearest", extent=[-10, 10, -10, 10])
-	plt.draw()
-
-	# Move the par
-	for(i in 1:steps)
-		(pos, vel) = update(parameters, pos, vel, dt)
-
-		if rem(i, skip) == 0
-			plt.plot(pos[1], pos[2], "ko", markersize=1)
-			plt.draw()
-			keep[div(i, skip), :] = pos
-			println(i)
-		end
-	end
-
-	plt.ioff()
-	plt.show()
-
-	return keep
-end
-

### 2015-07-17 lens_plots.jl

@@ -22,6 +22,15 @@ function magnification_image(parameters, x, y)
 	return mag
 end
 
+x = linspace(-10,  10, 1001)
+y = linspace( 10, -10, 1001)
+mag = magnification_image(posterior_sample[1, :], x, y)
+plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
+					vmin=-10.0, vmax=10.0)
+plt.show()
+
+
+
 ## Loop over samples
 ## Make a grid
 #x = linspace(-10,  10, 501)
@@ -36,6 +45,4 @@ end
 #end
 #plt.ioff()
 #plt.show()
-
-dynamics(posterior_sample[1, :], pos=[0, 5], skip=10, dt=0.01)
 

### 2015-07-17 Lenses/BlobbyNIE.jl
Getting there, need to consider angles etc properly

@@ -89,3 +89,23 @@ function magnification(parameters, x, y, h=1E-6)
 	return -2.5*log10(abs(J11*J22 - J12*J21))
 end
 
+# Current terrible implementation: numerically differentiate
+# magnification (which itself involves numerical derivatives).
+# Better: actually do second derivatives properly
+function magnification_derivs(parameters, x, y, h=1E-6)
+	dmdx = (magnification(parameters, x+h, y) -
+				magnification(parameters, x-h, y))/(2*h)
+	dmdy = (magnification(parameters, x, y+h) -
+				magnification(parameters, x, y-h))/(2*h)
+	return (dmdx, dmdy)
+end
+
+function move_along_contour(parameters, x, y, distance=0.1)
+	(dmdx, dmdy) = magnification_derivs(parameters, x, y)
+	tan_theta = -dmdx/dmdy
+	theta = atan(tan_theta)
+	x = x + distance*cos(theta)
+	y = y + distance*sin(theta)
+	return (x, y)
+end
+

### 2015-07-17 lens_plots.jl

@@ -25,8 +25,17 @@ end
 x = linspace(-10,  10, 1001)
 y = linspace( 10, -10, 1001)
 mag = magnification_image(posterior_sample[1, :], x, y)
+plt.ion()
+plt.hold(true)
 plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
 					vmin=-10.0, vmax=10.0)
+pos = [5.0, 7.0]
+for(i in 1:1000)
+	(pos[1], pos[2]) = move_along_contour(posterior_sample[1, :],
+							pos[1], pos[2], 0.03)
+	plt.plot(pos[1], pos[2], "ro")
+	plt.draw()
+end
 plt.show()
 
 

### 2015-07-17 Lenses/BlobbyNIE.jl
Try to do it with contours

@@ -89,23 +89,3 @@ function magnification(parameters, x, y, h=1E-6)
 	return -2.5*log10(abs(J11*J22 - J12*J21))
 end
 
-# Current terrible implementation: numerically differentiate
-# magnification (which itself involves numerical derivatives).
-# Better: actually do second derivatives properly
-function magnification_derivs(parameters, x, y, h=1E-6)
-	dmdx = (magnification(parameters, x+h, y) -
-				magnification(parameters, x-h, y))/(2*h)
-	dmdy = (magnification(parameters, x, y+h) -
-				magnification(parameters, x, y-h))/(2*h)
-	return (dmdx, dmdy)
-end
-
-function move_along_contour(parameters, x, y, distance=0.1)
-	(dmdx, dmdy) = magnification_derivs(parameters, x, y)
-	tan_theta = -dmdx/dmdy
-	theta = atan(tan_theta)
-	x = x + distance*cos(theta)
-	y = y + distance*sin(theta)
-	return (x, y)
-end
-

### 2015-07-17 lens_plots.jl

@@ -25,33 +25,14 @@ end
 x = linspace(-10,  10, 1001)
 y = linspace( 10, -10, 1001)
 mag = magnification_image(posterior_sample[1, :], x, y)
-plt.ion()
-plt.hold(true)
 plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
-					vmin=-10.0, vmax=10.0)
-pos = [5.0, 7.0]
-for(i in 1:1000)
-	(pos[1], pos[2]) = move_along_contour(posterior_sample[1, :],
-							pos[1], pos[2], 0.03)
-	plt.plot(pos[1], pos[2], "ro")
-	plt.draw()
-end
+					vmin=-10.0, vmax=10.0, cmap="coolwarm")
 plt.show()
 
-
-
-## Loop over samples
-## Make a grid
-#x = linspace(-10,  10, 501)
-#y = linspace( 10, -10, 501)
-#plt.ion()
-#plt.hold(false)
-#for(i in 1:M)
-#	mag = magnification_image(posterior_sample[i, :], x, y)
-#	plt.imshow(mag, interpolation="nearest", vmin=-10.0, vmax=10.0)
-#	plt.title(i)
-#	plt.draw()
-#end
-#plt.ioff()
-#plt.show()
+# http://stackoverflow.com/questions/5666056/matplotlib-extracting-data-from-contour-lines
+contour = plt.contour(x, y, mag, [3.0, 4.0])
+contour = contour[:collections][:1]
+contour = contour[:get_paths]()[1][:vertices]
+plt.plot(contour[:,1], contour[:,2])
+plt.show()
 

### 2015-07-17 lens_plots.jl
Capturing the big critical curve

@@ -22,17 +22,18 @@ function magnification_image(parameters, x, y)
 	return mag
 end
 
-x = linspace(-10,  10, 1001)
-y = linspace( 10, -10, 1001)
+x = linspace(-10,  10, 3001)
+y = linspace( 10, -10, 3001)
 mag = magnification_image(posterior_sample[1, :], x, y)
-plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
-					vmin=-10.0, vmax=10.0, cmap="coolwarm")
-plt.show()
 
+# Use matplotlib's contour function to get the critical curve
 # http://stackoverflow.com/questions/5666056/matplotlib-extracting-data-from-contour-lines
-contour = plt.contour(x, y, mag, [3.0, 4.0])
+contour = plt.contour(x, y, mag, [5.5, 5.51])
+plt.clf()
+plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
+					vmin=-7.0, vmax=7.0, cmap="coolwarm")
 contour = contour[:collections][:1]
 contour = contour[:get_paths]()[1][:vertices]
-plt.plot(contour[:,1], contour[:,2])
+plt.plot(contour[:,1], contour[:,2], "k", linewidth=2)
 plt.show()
 

### 2015-07-17 Lenses/BlobbyNIE.jl
Explicit types

@@ -1,10 +1,10 @@
 # Function to compute the deflection angles
 # at position (x, y), for the lens specified by
 # the parameters array (a row from sample.txt or posterior_sample.txt)
-function alpha(parameters, x, y, cos_theta=cos(parameters[8]),
-								 sin_theta=sin(parameters[8]),
-								 cos_theta_shear=cos(parameters[10]),
-								 sin_theta_shear=sin(parameters[10]))
+function alpha(parameters::Array{Float64, 2}, x::Float64, y::Float64, cos_theta::Float64=cos(parameters[8]),
+								 sin_theta::Float64=sin(parameters[8]),
+								 cos_theta_shear::Float64=cos(parameters[10]),
+								 sin_theta_shear::Float64=sin(parameters[10]))
 	# Get NIE parameters
 	b = parameters[3]
 	q = parameters[4]
@@ -64,7 +64,7 @@ function alpha(parameters, x, y, cos_theta=cos(parameters[8]),
 	return [ax, ay]
 end
 
-function fire_ray(parameters, x, y)
+function fire_ray(parameters::Array{Float64, 2}, x::Float64, y::Float64)
 	(ax, ay) = alpha(parameters, x, y)
 	xs = x - ax
 	ys = y - ay
@@ -73,7 +73,7 @@ end
 
 # Compute the magnification at position (x, y).
 # h is the spacing for numerical differentiation
-function magnification(parameters, x, y, h=1E-6)
+function magnification(parameters::Array{Float64, 2}, x::Float64, y::Float64, h::Float64=1E-6)
 	(xs1, ys1) = fire_ray(parameters, x + h, y)
 	(xs2, ys2) = fire_ray(parameters, x - h, y)
 

### 2015-07-17 lens_plots.jl

@@ -12,7 +12,7 @@ M = size(posterior_sample)[1]
 N = size(posterior_sample)[2]
 
 # Function to calculate magnification on a grid
-function magnification_image(parameters, x, y)
+function magnification_image(parameters::Array{Float64, 2}, x::Array{Float64, 1}, y::Array{Float64, 1})
 	mag = zeros(length(y), length(x))
 	for(j in 1:length(y))
 		for(i in 1:length(x))

### 2015-07-18 lens_plots.jl
Choose a row

@@ -7,6 +7,9 @@ include("Lenses/BlobbyNIE.jl")
 # Load the posterior samples
 posterior_sample = readdlm("posterior_sample.txt")
 
+# Specify a row
+which = 1
+
 # Size of the 2D array
 M = size(posterior_sample)[1]
 N = size(posterior_sample)[2]
@@ -24,7 +27,7 @@ end
 
 x = linspace(-10,  10, 3001)
 y = linspace( 10, -10, 3001)
-mag = magnification_image(posterior_sample[1, :], x, y)
+mag = magnification_image(posterior_sample[which, :], x, y)
 
 # Use matplotlib's contour function to get the critical curve
 # http://stackoverflow.com/questions/5666056/matplotlib-extracting-data-from-contour-lines

### 2015-07-18 lens_plots.jl
Compute caustics and save to file

@@ -40,3 +40,23 @@ contour = contour[:get_paths]()[1][:vertices]
 plt.plot(contour[:,1], contour[:,2], "k", linewidth=2)
 plt.show()
 
+# Fire the contour through to the source plane
+xs = contour[:,1]
+ys = contour[:,2]
+for(i in 1:size(xs)[1])
+	(xs[i], ys[i]) = fire_ray(posterior_sample[which, :],
+									contour[i, 1], contour[i, 2])
+end
+
+plt.figure(figsize=(8, 8))
+plt.plot(xs, ys, "k-")
+plt.xlabel("x_s")
+plt.ylabel("y_s")
+rays = zeros(size(xs)[1], 4)
+rays[:,1] = contour[:,1]
+rays[:,2] = contour[:,2]
+rays[:,3] = xs
+rays[:,4] = ys
+writedlm("rays.txt", rays)
+plt.show()
+

### 2015-07-18 lens_plots.jl
Maybe just areas?

@@ -29,24 +29,27 @@ x = linspace(-10,  10, 3001)
 y = linspace( 10, -10, 3001)
 mag = magnification_image(posterior_sample[which, :], x, y)
 
-# Use matplotlib's contour function to get the critical curve
-# http://stackoverflow.com/questions/5666056/matplotlib-extracting-data-from-contour-lines
-contour = plt.contour(x, y, mag, [5.5, 5.51])
-plt.clf()
-plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
-					vmin=-7.0, vmax=7.0, cmap="coolwarm")
-contour = contour[:collections][:1]
-contour = contour[:get_paths]()[1][:vertices]
-plt.plot(contour[:,1], contour[:,2], "k", linewidth=2)
-plt.show()
+## Use matplotlib's contour function to get the critical curve
+## http://stackoverflow.com/questions/5666056/matplotlib-extracting-data-from-contour-lines
+#contour = plt.contour(x, y, mag, [5.5, 5.51])
+#plt.clf()
+#plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
+#					vmin=-7.0, vmax=7.0, cmap="coolwarm")
+#contour = contour[:collections][:1]
+#contour = contour[:get_paths]()[1][:vertices]
+#plt.plot(contour[:,1], contour[:,2], "k", linewidth=2)
+#plt.show()
 
-# Fire the contour through to the source plane
-xs = contour[:,1]
-ys = contour[:,2]
-for(i in 1:size(xs)[1])
-	(xs[i], ys[i]) = fire_ray(posterior_sample[which, :],
-									contour[i, 1], contour[i, 2])
-end
+## Fire the contour through to the source plane
+#xs = contour[:,1]
+#ys = contour[:,2]
+#for(i in 1:size(xs)[1])
+#	(xs[i], ys[i]) = fire_ray(posterior_sample[which, :],
+#									contour[i, 1], contour[i, 2])
+#end
+
+plt.imshow(mag .> 5., interpolation="nearest", cmap="gray")
+plt.show()
 
 plt.figure(figsize=(8, 8))
 plt.plot(xs, ys, "k-")

### 2015-07-18 Papers/ms.tex
New simdata figures

@@
 
-We executed the code to generate 3,000 samples from the ``mixture of
+We executed the code to generate 5,000 samples from the ``mixture of
 constrained priors'' distribution of DNest. Our thinning factor was $10^5$,
-so $3 \times 10^8$ MCMC iterations were actually performed, taking approximately
-30 hours on a PC purchased new in 2012. After resampling these samples to
-reflect the posterior distribution, we were left with 318
+so $5 \times 10^8$ MCMC iterations were actually performed, taking approximately
+48 hours on a PC purchased new in 2012. After resampling these samples to
+reflect the posterior distribution, we were left with 537
 (equally weighted) posterior samples.
@@
 is
-$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -14249$, and
+$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -14248$, and
 the information (Kullback-Leibler divergence from the prior to the posterior)
-is $\mathcal{H} \approx 100$ nats. The information represents the degree of
+is $\mathcal{H} \approx 99$ nats. The information represents the degree of
 compression of the posterior distribution with respect to the prior, and can

### 2015-07-19 lens_plots.jl
Trying to compute caustics...ugh

@@ -48,16 +48,36 @@ mag = magnification_image(posterior_sample[which, :], x, y)
 #									contour[i, 1], contour[i, 2])
 #end
 
-plt.imshow(mag .> 5., interpolation="nearest", cmap="gray")
+plt.imshow(-(mag .> 5.5), interpolation="nearest", cmap="gray")
 plt.show()
 
+xx = zeros(size(y)[1], size(x)[1])
+yy = zeros(size(y)[1], size(x)[1])
+for(j in 1:size(yy)[1])
+	for(i in 1:size(xx)[1])
+		xx[i, j] = x[j]
+		yy[i, j] = y[i]
+	end
+end
+
+xx = xx[mag .> 5.5]
+yy = yy[mag .> 5.5]
+xs = xx
+ys = yy
+for(i in 1:size(xs)[1])
+	(xs[i], ys[i]) = fire_ray(posterior_sample[which, :],
+									xx[i], yy[i])
+end
+
+
+
 plt.figure(figsize=(8, 8))
-plt.plot(xs, ys, "k-")
+plt.plot(xs, ys, "k.", markersize=1)
 plt.xlabel("x_s")
 plt.ylabel("y_s")
 rays = zeros(size(xs)[1], 4)
-rays[:,1] = contour[:,1]
-rays[:,2] = contour[:,2]
+rays[:,1] = xx
+rays[:,2] = yy
 rays[:,3] = xs
 rays[:,4] = ys
 writedlm("rays.txt", rays)

### 2015-07-20 Papers/ms.tex
Minor editing

@@
 \author[Brewer, Huijser and Lewis]{%
-  Brendon~J.~Brewer$^{1}$\thanks{bj.brewer@auckland.ac.nz},
+  Brendon~J.~Brewer$^{1}$\thanks{To whom correspondence should be addressed. Email: {\tt bj.brewer@auckland.ac.nz}},
   David Huijser$^{1}$,
@@
 or free-form (e.g. pixellated) model for the surface brightness profile of the source
-\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid)
-or flexible model (e.g. pixellated) for the mass profile of the lens
+\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid
+[SIE]) or flexible model (e.g. pixellated) for the mass profile of the lens
 \item How to compute the results (e.g. optimization methods, Markov Chain

### 2015-07-20 Papers/ms.tex
More minor edits

@@
 \end{enumerate}
-
-Recent sophisicated approaches to
-this problem include \citet{2014MNRAS.445.2181C},
+Recent sophisicated approaches investigating different prior assumptions
+and computational approaches include \citet{2014MNRAS.445.2181C},
 \citet{2015arXiv150500198T}, and
-\citet{2015arXiv150407629B}. {\bf todo: actually comment
-on what's in these papers}.
+\citet{2015arXiv150407629B}.
 
@@
 modelling approach lies somewhere between simply-parameterised and
-pixellated models. One way of achieving this is with mixture models.
+pixellated models, which is also a motivation behind
+\citet{2015arXiv150500198T}'s investigation of shapelets.
+One way of achieving this is with mixture models.
 The source and the lens can be built up from a mixture of a moderate
@@
 i) we use a simpler and faster set of basis functions,
-ii) we apply it to the lens as well as the source, and
+ii) we apply it to the lens as well as the source, allowing for the
+possibility of substructure, and
 iii) the implementation is based on a C++ template library developed by
@@
 \section{Finding dark substructures}
+If possible, it is best
 If we are interested in detecting and measuring the properties of
@@
 computational efficiency, realism, and ease of implementation. None of the
-choices we have made are final in any sense, and we encourage exploration of
+choices we have made are final in any sense; rather, this model should be
+considered a proof of concept. We encourage exploration of
 other choices. Since we can compute marginal likelihoods, Bayesian model
@@
 straightforward, provided a mixture of our model and another is considered
-reasonable.
+a reasonable model of prior beliefs.
 

### 2015-07-21 Papers/ms.tex
More writing and editing

@@
 of the source and lens blobs), and birth/death moves to add or remove blobs
-to the source or lens, are handled internally by {\tt RJObject}.
+to the source or lens, are handled internally by {\tt RJObject} and
+fit into the general framework described in \citet{rjobject}.
 
@@
 being spread uniformly (in a frequency sense) over the sky. We also applied
-hierarchical priors to the substructure masses (and fluxes) so that, while
+hierarchical priors to the substructure masses (and source fluxes) so that, while
 the typical order of magnitude of the masses is unknown, the masses
-themselves are likely to be roughly the same order of magnitude.
+themselves are likely to be roughly the same order of magnitude. The
+hyperparameters of these distributions can also be interpreted as
+straightforward answers to questions about the substructure mass function.
 
@@
 
-We assign somewhat informative Cauchy priors to the central positions of the
-source and the lens.
+We assign somewhat informative (but heavy-tailed)
+Cauchy priors to the central positions of the source and the lens.
 One might object to the Cauchy priors
@@
 object is really a prior distribution, see \citet[][pp. 33--35]{caticha}.
+
+It is common to provide a ``variance image'' to lens modelling software,
+which specifies the standard deviations used in the likelihood function.
+However, telescopes do not provide variance images. It also does not make
+sense to specify vague priors prior to the image pixel values but posterior to
+the variance image (which usually resembles the image itself, and therefore
+would be highly informative). Allowing the standard deviation of the gaussian in the
+likelihood to depend on the mock image brightness is a more principled way
+of modelling our actual inferential situation. Nevertheless, we allow for an
+input variance image as well, which can be used for ad-hoc masking of
+troublesome regions (such as unmodelled flux from other sources).
 

### 2015-07-21 Papers/ms.tex
Three new references

@@
 mass function of the blobs then reduces to calculating the posterior
-distribution for the hyperparameters.
+distribution for the hyperparameters. This is related to the general principle
+that we should (ideally) construct our inference methods so that the
+quantities we infer directly answer our scientific questions
+\citep{2015arXiv150507840A, 2015ApJ...807...87S, pancoast}.
 
@@
 \section*{Acknowledgements}
-It is a pleasure to thank Phil Marshall (Stanford) and Tommaso Treu (UCLA)
+It is a pleasure to thank Phil Marshall (Stanford), Tommaso Treu (UCLA),
+Ross Fadely (NYU), and Alan Heavens (Edinburgh)
 for valuable discussion.
@@
 \begin{thebibliography}{99}
+\bibitem[\protect\citeauthoryear{Alsing et al.}{2015}]{2015arXiv150507840A} 
+Alsing J., Heavens A., Jaffe A.~H., Kiessling A., Wandelt B., Hoffmann T., 
+2015, arXiv, arXiv:1505.07840
+
 \bibitem[\protect\citeauthoryear{Birrer, Amara, 
@@
 
+\bibitem[\protect\citeauthoryear{Pancoast, Brewer, 
+\& Treu}{2011}]{pancoast} Pancoast A., Brewer B.~J., Treu T., 2011, ApJ, 730, 139
+
+\bibitem[\protect\citeauthoryear{Schneider et 
+al.}{2015}]{2015ApJ...807...87S} Schneider M.~D., Hogg D.~W., Marshall 
+P.~J., Dawson W.~A., Meyers J., Bard D.~J., Lang D., 2015, ApJ, 807, 87
+
 \bibitem[\protect\citeauthoryear{Sivia \& Skilling}{2006}]{sivia} Sivia, 

### 2015-07-21 Papers/ms.tex
Writing about the patchiness

@@
 check of reproducibility. If different runs yield substantially different
-results, the MCMC output should be treated with caution.
+results, the MCMC output should be treated with caution. For example, in
+Figure~\ref{fig:masses2}, there is a correlation between the mass attributed
+to the SIE component and that attributed to substructures. However, the
+distribution also appears somewhat ``lumpy'' or multimodal. This is probably
+not a feature of the actual posterior distribution, but rather appears due to
+imperfect sampling. Whereas a standard Metropolis sampler would move around
+very slowly in the hypothesis space, the DNS algorithm naturally spends some
+of the time sampling the prior. Therefore, a particle exploring the parameter
+space can ``forget'' its good fitting position, move somewhere completely
+different, and find another good fitting model in a different location. This
+is a natural feature of the algorithm (and is also present in related
+algorithms such as parallel tempering). Despite this feature, the patchy
+nature of Figure~\ref{fig:masses2} suggests that posterior exploration is
+still challenging in this problem.
 

### 2015-07-22 Papers/ms.tex
Dye et al

@@
 As a further demonstration the method, we apply it to the X-band data
-from the Isaac Newton Telescope (INT). This image of the Cosmic Horseshoe
-\citep{}, which is shown in Figure~\ref{fig:horseshoe_image}. For this system,
+of the Cosmic Horseshoe \citep{2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
+For this system,
 more data is available (Y and Z band data, as well as more recent
@@
 thorough study of this system.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{horseshoe_image.pdf}
+\caption{The X-band INT image of the Cosmic Horseshoe.
+\label{fig:horseshoe_image}}
+\end{center}
+\end{figure}
 
@@
 for greater accuracy.
-
-%The field of view of the image is $15.3180" \times 15.3180"$, and the size is $46 \times 46$ pixels, therefore one pixel is equivalent to $0.33"$. \\
-%The method discussed  in the previous section is applied to two models, the first model consist of a flexible source and a Singular Isothermal Elliptical(SIE) model for the lens.
-This model is has been used often  \cite{Dye2008}, \cite{schneider_falcoa_Ehlers_1994},      .
-%The second model has in addition to the flexible source and SIE, also possible satellites. \\
-%The amount of added satellites is automatically determined by the program.
-If models the addition of an satellite galaxies gives a higher probability it will be preferred over then model without satellite galaxies.
-\\
-%In both models the SIE is specified by the usual parameters: the location of the SIE ($x_c$,$y_c$), b, axis ratio $f$\footnote{in the code denoted with $q$},  the core radius$\zeta$, $\theta$, shear $\gamma$, and $\theta_{\gamma}$ \cite{kormann_schneider_1994}.\\
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.5]{horseshoe_image.pdf}
-\caption{\label{fig:horseshoe_image}}
-\end{center}
-\end{figure}
 
@@
 
+\bibitem[\protect\citeauthoryear{Dye et al.}{2008}]{2008MNRAS.388..384D} 
+Dye S., Evans N.~W., Belokurov V., Warren S.~J., Hewett P., 2008, MNRAS, 
+388, 384
+
 \bibitem[\protect\citeauthoryear{Fadely 

### 2015-07-22 Papers/ms.tex
Belokurov, names of bands

@@
 \section{The Cosmic Horseshoe}
-As a further demonstration the method, we apply it to the X-band data
-of the Cosmic Horseshoe \citep{2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
+As a further demonstration the method, we apply it to the g-band data
+of the Cosmic Horseshoe \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
 For this system,
-more data is available (Y and Z band data, as well as more recent
+more data is available (i and U band data, as well as more recent
 Hubble Space Telescope (HST) imaging). Unfortunately our current implementation
@@
 \includegraphics[scale=0.5]{horseshoe_image.pdf}
-\caption{The X-band INT image of the Cosmic Horseshoe.
+\caption{The g-band INT image of the Cosmic Horseshoe.
 \label{fig:horseshoe_image}}
@@
 
-% \begin{figure*}
-%% \hspace{20pt}
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-%  \includegraphics[width=0.75\linewidth,angle=90]{log_mass_SIE_no_blobs.eps}
-%\parbox{0.8\linewidth}{\caption{The log of the SIE mass within the critical curve  for model A.  \label{fig:sub1} }}
-%\end{subfigure}%
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-%  \includegraphics[width=0.75\linewidth,angle=90]{log_mass_SIE.eps}
-%   \parbox{0.8\linewidth}{\caption{The log of the SIE mass within the critical curve for model B.   \label{fig:sub2}}}
-%\end{subfigure}
-%   \end{figure*}
-
-%After choosing the prior probabilities one has to initialized the Dnest-code, which mean incorporating the problem specific information for
-% example dimensions of the images in pixels, image size in arc-seconds, information on the PSF etc in the metadata file. 
-% Besides these problem specific parameters, there are also several other parameters concerning the performance of code which need to be
-%  edited in the OPTION file. After these initialization, we ran a test run to explore the amount of necessary levels, and length of the run.
-% A sufficiently amount of levels correlates with good degree of mixing, and the length of the run is associated with the larger sample
-%  size.
-After one test run, the amount levels was adapted to 120, and the amount iterations was change to 5000 iterations, for model A this resulted in the effective sample size of 940, and for model B this resulted in the effective sample size of 757.
-The difference between the effective sample size is not unexpected, since the probability space which can be explored by applying model B much larger.
-\\
-%Throughout the paper the standard cosmology was used for the analysis:  $H_0=70 \rm{km~s^{-1} ~pc^{-1}}$,  $\Omega_m = 0.3$,and  $\Omega_\Lambda= 0.7$. 
-%The first test would to compare the SIE-mass of the models with the mass obtained in previous  work \cite{Belokurov2007} \cite{Dye2008}.
-%Using model A the median  calculated SIE mass within the critical curve in solar masses is  $(5.34 \pm 0.046) \cdot 10^{12} M_\odot$, % (using median + STDDEV)
-%which is comparable with previous work which gave the enclosed (cylindriacal) mass $(5.4 \pm 0.09) \cdot 10^{12} M_\odot$ \cite{Belokurov2007} and  mass within the Einstein-ring $(5.02 \pm 0.09) \cdot 10^{12} M_\odot$ \cite{Dye2008}.
-Figure \ref{fig:sub1} displays the histogram of the enclosed mass within an Einstein ring of $5"$, it displays a very well confined probability distribution of the mass.
-\\
-%Using model B the median calculated SIE mass within the critical curve in solar masses is  $(5.34 \pm 0.046) \cdot 10^{12} M_\odot$, % (using median + STDDEV)
-%which is slightly smaller compared to the masses obtained with model A and the masses from previous work mentioned above.
-Which is also not unexpected, because models where the SIE-mass is smaller can compensate by adding a satellite near by.
-Therefore the distribution is much wider as one can see in figure \ref{fig:sub2}.
-The median of the SIE-mass in model B is $(4.79 \pm 1.66) \cdot 10^{12} M_\odot$, which leaves a large numerical uncertainty.
-However by comparison of the two histograms in figure \ref{fig:1} it is apparent that the distribution has a strong feature at the location.
-\\
-% 
-%\begin{figure}[!h]
-%\hspace{5pt}
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-%  \includegraphics[width=0.7\linewidth,angle=90]{log_total_mass_blob.eps}
-%\parbox{0.8\linewidth}{\caption{The log of the total mass of the satellites for model B.   \label{fig:sub3}}}
-%\end{subfigure}%
-%\hspace{-15pt}
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-%  \vspace{6pt}
-%  \includegraphics[width=0.7\linewidth,angle=90]{log_total_mass_blobs_within_ring.eps}
-%\parbox{0.8\linewidth}{\caption{The log of the total mass of the satellites within the fixed Einstein-radius for model B.  \label{fig:sub4} }}
-%\end{subfigure}
-%   \end{figure}
-%\vspace{-15pt}
-%\noindent Another interesting aspect is the mass of the satellites.
-Figure \ref{fig:sub3} displays a histogram of the logarithm of the total mass of the satellites per sample.
-Figure \ref{fig:sub4} displays histogram of the logarithm of the total mass of the satellites within a radius of $ 5"$ from the centre of images per sample.
-Comparing these two images reveals that large part the massive satellites lie outside the Einstein ring.
-The satellites at a larger distance can only influence the images if they are more massive.
-Figure \ref{fig:sub5} display a histogram of the log of the total mass of the SIE and the satellites within the Einstein radius, which clearly looks very similar to \ref{fig:sub1}.
-%Figure \ref{fig:sub6} display a plot of the total mass of the SIE versus mass of the satellites within the Einstein radius whichs  negative correlation of approximately 
-%\begin{equation}
-% \sum M_{satellites} = 5\cdot10^{12} - M_{SIE}
-% \end{equation}
-
-%The main conclusion of the analysis of the datasets of model A and model B, would be that the application of the DNest code with a free amount of satellite galaxies return a well matching model which is very similar to to the model without any satellites, this proves
-%even though the code has the freedom the explore and create all sort of models, it confirms that the already known distribution is very probable.
-This shows how well the code works, and beside that it is also good indication that the well established SIE model for this system doesn't need additional satellites to explain the system.
-% 
-%\begin{figure}
-%\hspace{10pt}
-%\begin{subfigure}{.5\textwidth}
-%\vspace{-12pt}
-%  \centering
-%  \includegraphics[width=0.75\linewidth,angle=90]{mass_SIE_plus_blob_mass.eps}
-%\parbox{0.8\linewidth}{\caption{The log of add mass of the satellites and SIE within the fixed Einstein-radius for model B.   \label{fig:sub5}}}
-%\end{subfigure}
-%\begin{subfigure}{.5\textwidth}
-%  \centering
-%  \includegraphics[width=0.75\linewidth,angle=90]{joint.eps}
-%\parbox{0.8\linewidth}{\caption{Plot of the log of the total mass of the satellites within the fixed Einstein-radius versus the 
-%log of the SIE mass within the Einstein radius for model B.  \label{fig:sub6} }}
-%\end{subfigure}
-
-%   \end{figure}
-
-%  
-%
-
-%\section{ER 0047-2808}
-%We demonstrate the method on the HST images of ER 0047-2808.
-
 \section*{Acknowledgements}
@@
 2015, arXiv, arXiv:1505.07840
+
+\bibitem[\protect\citeauthoryear{Belokurov et 
+al.}{2007}]{belokurov} Belokurov V., et al., 2007, ApJ, 671, L9
 

### 2015-07-22 Papers/ms.tex
Two sentences
Talking a bit about results

@@
 
+The joint posterior distribution for the SIE mass total substructure mass
+for the Cosmic Horseshoe is given in Figure~\ref{fig:masses2}. As with
+the simulated data (Figure~\ref{fig:masses}), we see an expected negative
+correlation between these two quantities. However, the points are not as
+smoothly distributed in this case (we discuss this issue further
+in Section~\ref{sec:convergence}). The posterior distribution for
+$N_{\rm lens}$ also shows some evidence for more than zero substructures.
+In particular, the prior probability for $N_{\rm lens} > 0$ was 10/11
+$\approx$ 0.91, whereas the posterior probability is approximately 0.97.
+This corresponds to a Bayes Factor of approximately 3 in favour of
+$N_{\rm lens} > 0$ versus the alternative $N_{\rm lens} = 0$.
+
 \begin{figure}
@@
 
-\subsection{Reproducibility of the results}
+\subsection{Reproducibility of the results}\label{sec:convergence}
 The ``effective sample size'' returned by DNest, which we have described as the

### 2015-07-22 Papers/ms.tex
Paragraph and caption

@@
 
+Despite weak evidence for the existence of substructure, when we examine the
+expected value of the empirical measure of substructure positions
+(Figure~\ref{fig:substructures2}) we find no consistency in their positions,
+unlike for the simulated data (Figure~\ref{fig:substructures}). This situation
+is not uncommon. For example, \citet{exoplanet} found evidence for a large
+number of Keplerian signals in a time series, but the number of such signals
+with well constrained properties was much lower.
+
 \begin{figure}
@@
 \includegraphics[scale=0.4]{substructures2.pdf}
-\caption{\label{fig:substructures2}}
+\caption{The positions of substructures encountered in the MCMC sampling
+for the Cosmic Horseshoe; technically a Monte Carlo approximation to the
+posterior expected value of the empirical measure of substructure
+positions. Unlike Figure~\ref{fig:substructures}, for the Cosmic Horseshoe
+there is little consistency in the positions of the substructures.
+\label{fig:substructures2}}
 \end{center}

### 2015-07-22 Papers/ms.tex
Another paragraph

@@
 
+{\tt Upper limits on mass}
+
+As with any inference, the results presented here may be sensitive to many of
+the input modelling assumptions, and a slightly different (yet still
+``reasonable'') set of choices might yield different results. For example, if
+the density profile of the lens was smooth but not of the SIE form, and the
+data were informative enough to show this, the current
+model would only be able to explain the data by adding substructures.
+Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within
+the SIE family. One way of investigating this is to use a different family of
+smooth lens models and doing model selection based on the marginal likelihoods.
+
 \begin{figure}

### 2015-07-22 Papers/ms.tex
DNest --> DNS

@@
 The {\tt RJObject} library uses the
-Diffusive Nested Sampling algorithm \citep{dnest} for its sampling, but the
+Diffusive Nested Sampling algorithm \citep[DNS][]{dnest} for its sampling, but the
 trans-dimensionality is handled by the MCMC moves. Therefore, the marginal
@@
 We executed the code to generate 5,000 samples from the ``mixture of
-constrained priors'' distribution of DNest. Our thinning factor was $10^5$,
+constrained priors'' distribution of DNS. Our thinning factor was $10^5$,
 so $5 \times 10^8$ MCMC iterations were actually performed, taking approximately
@@
 
-We generated 5,000 samples from the DNest target distribution and thinned
+We generated 5,000 samples from the DNS target distribution and thinned
 by a factor of $10^5$, so $5 \times 10^8$ MCMC iterations were actually
@@
 \subsection{Reproducibility of the results}\label{sec:convergence}
-The ``effective sample size'' returned by DNest, which we have described as the
-number of posterior samples, takes into account the fact DNest's target
+The ``effective sample size'' returned by DNS, which we have described as the
+number of posterior samples, takes into account the fact DNS's target
 distribution is not the posterior. However, it does not take autocorrelation

### 2015-07-22 Papers/ms.tex
PSF paragraph

@@
 smooth lens models and doing model selection based on the marginal likelihoods.
+Another option which we defer to future work is to implement a more flexible
+model (such as a concentric mixture of concentric elliptical lenses).
+
+Another potential inadequacy of our model is the assumption that the PSF is
+known. In practice, the PSF is often estimated from the image of nearby star(s),
+or from theoretical knowledge of the telescope (especially in the case of
+space based imaging). However, if the PSF is misspecified, or in fact varies
+across the image, this could induce subtle effects in the imaging which our
+current model could only explain using substructure.
 

### 2015-07-23 Papers/ms.tex
Posterior for total mass

@@
 number of Keplerian signals in a time series, but the number of such signals
-with well constrained properties was much lower.
-
-{\tt Upper limits on mass}
+with well constrained properties was much lower. Related to this, we can
+compute posterior probabilities for any hypothesis about the substructure
+masses. With 95\% probability the substructure mass is less than 88 units
+and with 75\% probability it is less than 54 units.
 
@@
 Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within
-the SIE family. One way of investigating this is to use a different family of
+the SIE family. One way of further investigating this is to use a different family of
 smooth lens models and doing model selection based on the marginal likelihoods.

### 2015-07-23 Papers/ms.tex
Geraint comments

@@
 However, in the present paper we do not account for
-multi-band data.
+multi-band data; this will be reserved for a future contribution.
 
@@
 we aim to express a large degree of prior uncertainty (hence the liberal use
-of uniform, loguniform, and Cauchy distributions). However, we also specify
+of uniform, log-uniform, and Cauchy distributions). However, we also specify
 some priors hierarchically to allow (for example)
@@
 so $5 \times 10^8$ MCMC iterations were actually performed, taking approximately
-48 hours on a PC purchased new in 2012. After resampling these samples to
+48 hours on a modest desktop PC\footnote{The computer was purchased in 2012
+and has a second-generation intel i7 processor, and the process was run on
+8 threads.}. After resampling these samples to
 reflect the posterior distribution, we were left with 537
@@
 Monte Carlo approximation to the posterior expectation of the empirical
-measure).
+measure). The density of black points in any region is proportional to the
+expected number of substructures whose centers lie within that region. In this
+case, there is strong evidence for a substructure close to the top-left image
+(where one was actually placed).
 \label{fig:substructures}}

### 2015-07-23 Papers/ms.tex
Started conclusions

@@
 
+\section{Conclusions}
+We have developed a trans-dimensional Bayesian approach motivated directly by
+the question of whether dark substructures exist in a lens galaxy, given image
+data. By making use of the Diffusive Nested Sampling algorithm \citep{dnest}
+and the {\tt RJObject} library \citep{rjobject}, we outsource the difficulties
+associated with choosing Metropolis proposals for a hierarchical model of
+non-fixed dimension. The model allows for source and lens ``blobs'' to appear
+as needed to explain the data.
+
 \section*{Acknowledgements}
@@
 for valuable discussion.
-
 This work was funded by a Marsden Fast Start grant from the Royal Society of
@@
 
-\bibitem[\protect\citeauthoryear{Green}{1995}]{rjmcmc}
+\bibitem[\protect\citeauthoryear{Green}{1995}]{green}
 Green, P.~J., 1995, Reversible Jump Markov Chain Monte Carlo Computation and Bayesian Model Determination, Biometrika 82 (4): 711–732.

### 2015-07-23 Papers/ms.tex
More conclusion

@@
 more data is available (i and U band data, as well as more recent
-Hubble Space Telescope (HST) imaging). Unfortunately our current implementation
+Hubble Space Telescope (HST) imaging), although the g-band image is the highest
+signal-to-noise of the INT images. Unfortunately our current implementation
 doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
@@
 non-fixed dimension. The model allows for source and lens ``blobs'' to appear
-as needed to explain the data.
+as needed to explain the data. The prior for the blobs' properties is
+specified hierarchically, to more realistically model sensible prior beliefs,
+and to tie the model parameters directly to questions of scientific interest
+such as the mass function of substructures.
+
+As a proof of concept, we demonstrated the successful recovery of a single
+substructure from simulated data for which all of the model assumptions were
+true. We then applied the method to an image of the Cosmic Horseshoe system
+and found mild evidence in favour of the existence of a substructure, or at
+the very least, a departure from a simple SIE+$\gamma$ lens profile.
 

### 2015-07-23 Papers/ms.tex
Cosmic Horseshoe phone number, and consistency with Dye

@@
 As a further demonstration the method, we apply it to the g-band data
-of the Cosmic Horseshoe \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
+of the Cosmic Horseshoe J1004+4112 \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
 For this system,
@@
 Another option which we defer to future work is to implement a more flexible
-model (such as a concentric mixture of concentric elliptical lenses).
+model (such as a concentric mixture of concentric elliptical lenses). This
+result is consistent with that of \citet{2008MNRAS.388..384D}, who found a slight preference for an elliptical power law profile over the SIE
+(which is a specific case of an elliptical power law).
 

### 2015-07-23 Papers/ms.tex
Various little bits of work

@@
 \usepackage[utf8]{inputenc}
-\usepackage{caption}
 \usepackage{subcaption} % subfigures
@@
 fired per image pixel. However, certain kinds of proposals do not affect the
-image in any way, such as those that change the noise parameters.
+image in any way, such as those which change the noise parameters. For efficiency
+we do not recompute the mock image in these cases.
 
@@
 Hubble Space Telescope (HST) imaging), although the g-band image is the highest
-signal-to-noise of the INT images. Unfortunately our current implementation
+signal-to-noise of the INT images. The source redshift is $z_s=2.379$, and the
+lens is a massive luminous red galaxy at $z_l=0.4457$.
+Unfortunately our current implementation
 doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
@@
 \includegraphics[scale=0.5]{horseshoe_image.pdf}
-\caption{The g-band INT image of the Cosmic Horseshoe.
+\caption{The g-band INT image of the Cosmic Horseshoe, with the lens galaxy
+subtracted.
 \label{fig:horseshoe_image}}
@@
 for the Cosmic Horseshoe is given in Figure~\ref{fig:masses2}. As with
-the simulated data (Figure~\ref{fig:masses}), we see an expected negative
+the simulated data (Figure~\ref{fig:simdata_masses}), we see an expected negative
 correlation between these two quantities. However, the points are not as
@@
 its critical ellipse, which is not the critical curve of the lens overall),
-and the total mass in substructures.\label{fig:simdata_masses}}
+and the total mass in substructures.\label{fig:masses2}}
 \end{center}
@@
 \includegraphics[scale=0.4]{N_lens2.pdf}
-\caption{\label{fig:N_lens2}}
+\caption{The posterior distribution for the number of lens substructures
+in the Cosmic Horseshoe system. There is mild evidence in favour of the
+hypothesis that $N_{\rm lens} \neq 0$.\label{fig:N_lens2}}
 \end{center}

### 2015-07-23 Papers/ms.tex
Various small edits and fixes

@@
 Lens modelling has been a topic of much interest over the last two decades.
-Most approaches are based on Bayesian inference, maximum likelihood or
+Most approaches are based on Bayesian inference \citep{sivia, ohagan}, maximum
+likelihood \citep{millar} or
 variations thereof. These approaches may be categorized according to the
@@
 we can verify that the results of the inference do behave in understandable
-ways. For example, in Figure~\ref{fig:simdata_masses},
+ways. For example, in Figure~\ref{fig:masses},
 we plot the joint posterior distribution
@@
 \begin{center}
-\includegraphics[scale=0.4]{simdata_masses.pdf}
+\includegraphics[scale=0.4]{masses.pdf}
 \caption{The joint posterior distribution for the SIE mass (integrated within
 its critical ellipse, which is not the critical curve of the lens overall),
-and the total mass in substructures.\label{fig:simdata_masses}}
+and the total mass in substructures.\label{fig:masses}}
 \end{center}
@@
 for the Cosmic Horseshoe is given in Figure~\ref{fig:masses2}. As with
-the simulated data (Figure~\ref{fig:simdata_masses}), we see an expected negative
+the simulated data (Figure~\ref{fig:masses}), we see an expected negative
 correlation between these two quantities. However, the points are not as
@@
 
+\bibitem[\protect\citeauthoryear{Millar}{2011}]{millar}
+Millar, R.~B., Maximum likelihood estimation and inference: with examples in R, SAS and ADMB. Vol. 111. John Wiley \& Sons, 2011.
+
 \bibitem[\protect\citeauthoryear{O'Hagan and Forster}{2004}]{ohagan}

### 2015-07-23 Papers/ms.tex
Masses

@@
 smoothly distributed in this case (we discuss this issue further
-in Section~\ref{sec:convergence}). The posterior distribution for
-$N_{\rm lens}$ also shows some evidence for more than zero substructures.
+in Section~\ref{sec:convergence}). An upper ``limit'' on the SIE mass, with
+95\% posterior probability, is $5.21 \pm 0.02\times 10^{12} M_\odot$
+The posterior distribution for
+$N_{\rm lens}$ (Figure~\ref{fig:N_lens2})
+also shows some evidence for more than zero substructures.
 In particular, the prior probability for $N_{\rm lens} > 0$ was 10/11
@@
 its critical ellipse, which is not the critical curve of the lens overall),
-and the total mass in substructures.\label{fig:masses2}}
+and the total mass in substructures. Assuming a flat cosmology with
+$\Omega_m=0.3$, $\Omega_\Lambda=0.7$, and
+$H_0=70$ km/s/Mpc, one mass unit corresponds to 2.07$\times 10^{11} M_\odot$.
+\label{fig:masses2}}
 \end{center}
@@
 masses. With 95\% probability the substructure mass is less than 88 units
-and with 75\% probability it is less than 54 units.
+and with 75\% probability it is less than 54 units. Clearly, it is not the
+substructure mass over the entire domain that is of interest.
 

### 2015-07-23 Papers/ms.tex
A few more words

@@
 in Section~\ref{sec:convergence}). An upper ``limit'' on the SIE mass, with
-95\% posterior probability, is $5.21 \pm 0.02\times 10^{12} M_\odot$
+95\% posterior probability, is $5.21 M_\odot$.
 The posterior distribution for
@@
 model would only be able to explain the data by adding substructures.
-Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within
-the SIE family. One way of further investigating this is to use a different family of
+Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within the SIE$+\gamma$ family.
+In fact, some of the posterior
+samples obtained contain massive substructures outside of the image, which
+could be modelling higher-order effects of the environment beyond what is
+captured by the simple external shear model.
+One way of further investigating this is to use a different family of
 smooth lens models and doing model selection based on the marginal likelihoods.

### 2015-07-23 Papers/ms.tex
Small clarification
Two more paragraphs in the conclusion

@@
 could be modelling higher-order effects of the environment beyond what is
-captured by the simple external shear model.
+captured by the simple external shear model. This is one way of violating
+the SIE$+\gamma$ assumption, and another is simply to have a different projected
+density profile.
 One way of further investigating this is to use a different family of
@@
 and found mild evidence in favour of the existence of a substructure, or at
-the very least, a departure from a simple SIE+$\gamma$ lens profile.
+the very least, a departure from a simple SIE+$\gamma$ lens profile. The
+main output of our method is a set of posterior samples, each representing
+a plausible scenario for the lens and the source given the data
+and the assumed prior information. These samples can be displayed as a movie,
+which is a very useful method for intuitively understanding the remaining
+uncertainty. Any posterior summaries of interest can be
+produced from the samples, but the interpretation of many of these summaries
+is not necessarily straightforward. We have suggested that the
+posterior expectation of the empirical measure of substructure positions is
+one of the most helpful summaries.
+
+The model assumptions used in this paper are fairly simple. In future work we
+intend to generalise the smooth lens model beyond the overly simplistic
+SIE+$\gamma$ model, and to generalize the model to multi-band data. Applications
+to other systems are also forthcoming, as well as variants on the model using
+different conditional priors for the substructure properties given the
+hyperparameters.
 

### 2015-07-23 Papers/ms.tex
Get rid of subcaption package
Why the posterior is less crazy for the simulated data

@@
 \usepackage[utf8]{inputenc}
-\usepackage{subcaption} % subfigures
 \usepackage{float}
@@
 to the SIE component and that attributed to substructures. However, the
-distribution also appears somewhat ``lumpy'' or multimodal. This is probably
-not a feature of the actual posterior distribution, but rather appears due to
+distribution also appears somewhat ``lumpy'' or multimodal. This may
+not be a feature of the actual posterior distribution, but could arise due to
 imperfect sampling. Whereas a standard Metropolis sampler would move around
@@
 still challenging in this problem.
+
+The results for the simulated data (Figure~\ref{fig:masses})
+were less complex because of the definite existence of one substructure.
+Its mass and position provide some information about the hyperparameters
+$\boldsymbol{\alpha}_{\rm lens}$, restricting the probability that
+high mass substructures exist far from the image.
 

### 2015-07-23 Papers/ms.tex
Substructures outside the image

@@
 in Section~\ref{sec:convergence}). An upper ``limit'' on the SIE mass, with
-95\% posterior probability, is $5.21 M_\odot$.
+95\% posterior probability, is $5.21 M_\odot$. The algorithm has also found
+some possibilities where the substructure mass is much greater than this. In
+these cases, the substructures are far from the image --- it is the environment
+that is being modelled.
+
 The posterior distribution for
@@
 its critical ellipse, which is not the critical curve of the lens overall),
-and the total mass in substructures. Assuming a flat cosmology with
+and the total mass in substructures. The units are square arcseconds (i.e.
+a unit mass would have an Einstein radius of one arcsecond).
+Assuming a flat cosmology with
 $\Omega_m=0.3$, $\Omega_\Lambda=0.7$, and
-$H_0=70$ km/s/Mpc, one mass unit corresponds to 2.07$\times 10^{11} M_\odot$.
+$H_0=70$ km/s/Mpc, one unit corresponds to 2.07$\times 10^{11} M_\odot$.
 \label{fig:masses2}}

### 2015-07-24 Lenses/BlobbyNIE.jl
Starting function to integrate blob mass within a region

@@ -89,3 +89,11 @@ function magnification(parameters::Array{Float64, 2}, x::Float64, y::Float64, h:
 	return -2.5*log10(abs(J11*J22 - J12*J21))
 end
 
+
+# Input: parameters of a blob (length four)
+function blob_mass_within(parameters::Array{Float64, 2},
+							x_min, x_max, y_min, y_max)
+	assert(size(parameters) == (1, 4))
+	xc, yc, mass, width = parameters
+end
+

### 2015-07-24 Lenses/BlobbyNIE.jl
Function to numerically integrate blob

@@ -92,8 +92,28 @@ end
 
 # Input: parameters of a blob (length four)
 function blob_mass_within(parameters::Array{Float64, 2},
-							x_min, x_max, y_min, y_max)
+							x_min, x_max, y_min, y_max; n=1001)
 	assert(size(parameters) == (1, 4))
 	xc, yc, mass, width = parameters
+	widthsq = width^2
+	C = mass*2.0/pi/widthsq
+
+	x = linspace(x_min, x_max, n)
+	y = linspace(y_max, y_min, n)
+	f = zeros(n, n)
+	for(j in 1:n)
+		for(i in 1:n)
+			rsq = (x[i] - xc)^2 + (y[j] - yc)^2
+			if(rsq <= widthsq)
+				f[i, j] += C*(1.0 - rsq/widthsq)
+			end
+		end
+	end
+
+	return (x[2] - x[1])*(y[1] - y[2])*sum(f)
 end
+
+params = zeros(1, 4)
+params[1], params[2], params[3], params[4] = 0.0, 0.0, 1.0, 0.5
+println(blob_mass_within(params, -0.5, 0.5, -0.5, 0.5))
 

### 2015-07-24 Papers/ms.tex
Fixed mass units: all in terms of critical density. No simple b^2

@@
 its critical ellipse, which is not the critical curve of the lens overall),
-and the total mass in substructures. The units are square arcseconds (i.e.
-a unit mass would have an Einstein radius of one arcsecond).
+and the total mass in substructures. The units are defined by the critical
+density, so that a mass of $\pi$ units would have an Einstein radius of one arcsecond.
 Assuming a flat cosmology with
 $\Omega_m=0.3$, $\Omega_\Lambda=0.7$, and
-$H_0=70$ km/s/Mpc, one unit corresponds to 2.07$\times 10^{11} M_\odot$.
+$H_0=70$ km/s/Mpc, one unit corresponds to 6.59$\times 10^{10} M_\odot$.
 \label{fig:masses2}}

### 2015-07-24 display.py

@@ -119,7 +119,7 @@ show()
 figure(3)
 rc("font", size=16, family="serif", serif="Computer Sans")
 rc("text", usetex=True)
-plot(output[:,2]**2, output[:,39:48].sum(axis=1), 'bo', markersize=5,\
+plot(output[:,2]**2*pi, output[:,39:48].sum(axis=1), 'bo', markersize=5,\
                        alpha=0.2)
 xlabel('SIE mass (within critical ellipse)')
 ylabel('Total substructure mass')

### 2015-07-25 display.py
mass units

@@ -5,6 +5,7 @@ and the residuals.
 from pylab import *
 import os
 
+mass_units = 1.
 saveFrames = False # For making movies
 if saveFrames:
 	os.system('rm Frames/*.png')
@@ -119,8 +120,8 @@ show()
 figure(3)
 rc("font", size=16, family="serif", serif="Computer Sans")
 rc("text", usetex=True)
-plot(output[:,2]**2*pi, output[:,39:48].sum(axis=1), 'bo', markersize=5,\
-                       alpha=0.2)
+plot(mass_units*pi*output[:,2]**2, mass_units*output[:,39:48].sum(axis=1),\
+					'bo', markersize=5, alpha=0.2)
 xlabel('SIE mass (within critical ellipse)')
 ylabel('Total substructure mass')
 savefig('masses.pdf', bbox_inches='tight')

### 2015-07-26 Papers/ms.tex
New mass figure

@@
 and the total mass in substructures. The units are defined by the critical
-density, so that a mass of $\pi$ units would have an Einstein radius of one arcsecond.
-Assuming a flat cosmology with
+density, so that a mass of $\pi$ units would have an Einstein radius of one arcsecond. To calculate the masses in solar masses, we assumed a flat cosmology with
 $\Omega_m=0.3$, $\Omega_\Lambda=0.7$, and
-$H_0=70$ km/s/Mpc, one unit corresponds to 6.59$\times 10^{10} M_\odot$.
+$H_0=70$ km/s/Mpc.
 \label{fig:masses2}}
@@
 compute posterior probabilities for any hypothesis about the substructure
-masses. With 95\% probability the substructure mass is less than 88 units
-and with 75\% probability it is less than 54 units. Clearly, it is not the
-substructure mass over the entire domain that is of interest.
+masses.
+With 95\% probability the substructure mass is less than 5.80$\times 10^{12}$ solar masses and with 75\% probability it is less than 3.56$\times 10^{12}$ solar masses.
+As the einstein ring implies a mass of about $5 \times 10^{12}$
+solar masses, it is not the substructure mass over the entire domain
+that is of interest.
 

### 2015-07-26 Papers/ms.tex
Two more references

@@
 ``blobs'' is unknown), we used a trans-dimensional MCMC sampler based on
-reversible jump MCMC \citep{green}. We implemented the MCMC using the
+reversible jump MCMC \citep{green}. This framework has been used successfully
+in many astronomical inference problems \citep[e.g.][]{jones, renate}.
+We implemented the MCMC using the
 {\tt RJObject} software \citep{rjobject}, a C++ library for implementing trans-dimensional MCMC with hierarchically-specified priors when the model is
@@
 
+\bibitem[\protect\citeauthoryear{Jones, Kashyap, 
+\& van Dyk}{2014}]{jones} Jones D.~E., Kashyap V.~L., van Dyk D.~A., 2014, arXiv, arXiv:1411.7447
+
 \bibitem[\protect\citeauthoryear{Koopmans}{2005}]{koopmans} 
@@
 
+\bibitem[\protect\citeauthoryear{Umst{\"a}tter et 
+al.}{2005}]{renate} Umst{\"a}tter R., Christensen N., Hendry 
+M., Meyer R., Simha V., Veitch J., Vigeland S., Woan G., 2005, PhRvD, 72, 
+022001
+
 \bibitem[\protect\citeauthoryear{Vegetti 

### 2015-07-27 Lenses/BlobbyNIE.jl
Split magnification into jacobian function

@@ -71,9 +71,9 @@ function fire_ray(parameters::Array{Float64, 2}, x::Float64, y::Float64)
 	return [xs, ys]
 end
 
-# Compute the magnification at position (x, y).
+# Compute the jacobian of the lens-->source plane mapping at position (x, y).
 # h is the spacing for numerical differentiation
-function magnification(parameters::Array{Float64, 2}, x::Float64, y::Float64, h::Float64=1E-6)
+function jacobian(parameters::Array{Float64, 2}, x::Float64, y::Float64, h::Float64=1E-6)
 	(xs1, ys1) = fire_ray(parameters, x + h, y)
 	(xs2, ys2) = fire_ray(parameters, x - h, y)
 
@@ -86,7 +86,14 @@ function magnification(parameters::Array{Float64, 2}, x::Float64, y::Float64, h:
 	J21 = (xs1 - xs2)/(2*h)
 	J22 = (ys1 - ys2)/(2*h)
 
-	return -2.5*log10(abs(J11*J22 - J12*J21))
+	return(J11*J22 - J12*J21)
+end
+
+
+# Compute the magnification (in magnitudes) at position (x, y).
+# h is the spacing for numerical differentiation
+function magnification(parameters::Array{Float64, 2}, x::Float64, y::Float64, h::Float64=1E-6)
+	return -2.5*log10(abs(jacobian(parameters, x, y, h)))
 end
 
 

### 2015-07-27 lens_plots.jl

@@ -48,7 +48,8 @@ mag = magnification_image(posterior_sample[which, :], x, y)
 #									contour[i, 1], contour[i, 2])
 #end
 
-plt.imshow(-(mag .> 5.5), interpolation="nearest", cmap="gray")
+plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
+					vmin=-7.0, vmax=7.0, cmap="coolwarm")
 plt.show()
 
 xx = zeros(size(y)[1], size(x)[1])

### 2015-07-27 lens_plots.jl
Calculate jacobian instead of log of its absolute value

@@ -25,9 +25,20 @@ function magnification_image(parameters::Array{Float64, 2}, x::Array{Float64, 1}
 	return mag
 end
 
+# Function to calculate jacobian on a grid
+function jacobian_image(parameters::Array{Float64, 2}, x::Array{Float64, 1}, y::Array{Float64, 1})
+	mag = zeros(length(y), length(x))
+	for(j in 1:length(y))
+		for(i in 1:length(x))
+			mag[i, j] = jacobian(parameters, x[i], y[j])
+		end
+	end
+	return mag
+end
+
 x = linspace(-10,  10, 3001)
 y = linspace( 10, -10, 3001)
-mag = magnification_image(posterior_sample[which, :], x, y)
+mag = jacobian_image(posterior_sample[which, :], x, y)
 
 ## Use matplotlib's contour function to get the critical curve
 ## http://stackoverflow.com/questions/5666056/matplotlib-extracting-data-from-contour-lines

### 2015-07-27 lens_plots.jl
Sign change method

@@ -36,9 +36,9 @@ function jacobian_image(parameters::Array{Float64, 2}, x::Array{Float64, 1}, y::
 	return mag
 end
 
-x = linspace(-10,  10, 3001)
-y = linspace( 10, -10, 3001)
-mag = jacobian_image(posterior_sample[which, :], x, y)
+x = linspace(-10,  10, 1001)
+y = linspace( 10, -10, 1001)
+mag = magnification_image(posterior_sample[which, :], x, y)
 
 ## Use matplotlib's contour function to get the critical curve
 ## http://stackoverflow.com/questions/5666056/matplotlib-extracting-data-from-contour-lines
@@ -60,38 +60,39 @@ mag = jacobian_image(posterior_sample[which, :], x, y)
 #end
 
 plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
-					vmin=-7.0, vmax=7.0, cmap="coolwarm")
+					vmin=-5.0, vmax=5.0, cmap="coolwarm")
 plt.show()
 
-xx = zeros(size(y)[1], size(x)[1])
-yy = zeros(size(y)[1], size(x)[1])
-for(j in 1:size(yy)[1])
-	for(i in 1:size(xx)[1])
-		xx[i, j] = x[j]
-		yy[i, j] = y[i]
+rays = zeros(100000, 4)
+n_rays = 0
+for(j in 1:size(y)[1])
+	f1 = jacobian(posterior_sample[which, :], x[1], y[j])
+	for(i in 2:size(x)[1])
+		f2 = jacobian(posterior_sample[which, :], x[i], y[j])
+		if(sign(f1) == -sign(f2))
+			rays[n_rays+1, :] = [[x[i], y[j], 0.0, 0.0]]
+			n_rays += 1
+		end
+		f1 = f2
+	end
+
+	if(mod(j, 10) == 0)
+		println(j, " ", n_rays)
 	end
 end
-
-xx = xx[mag .> 5.5]
-yy = yy[mag .> 5.5]
-xs = xx
-ys = yy
-for(i in 1:size(xs)[1])
-	(xs[i], ys[i]) = fire_ray(posterior_sample[which, :],
-									xx[i], yy[i])
-end
-
-
+rays = rays[1:n_rays, :]
 
 plt.figure(figsize=(8, 8))
[…]

### 2015-07-27 lens_plots.jl
Speedup. Need to fix alignment

@@ -36,9 +36,9 @@ function jacobian_image(parameters::Array{Float64, 2}, x::Array{Float64, 1}, y::
 	return mag
 end
 
-x = linspace(-10,  10, 1001)
-y = linspace( 10, -10, 1001)
-mag = magnification_image(posterior_sample[which, :], x, y)
+x = linspace(-10,  10, 2001)
+y = linspace( 10, -10, 2001)
+mag = sign(jacobian_image(posterior_sample[which, :], x, y))
 
 ## Use matplotlib's contour function to get the critical curve
 ## http://stackoverflow.com/questions/5666056/matplotlib-extracting-data-from-contour-lines
@@ -61,16 +61,18 @@ mag = magnification_image(posterior_sample[which, :], x, y)
 
 plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
 					vmin=-5.0, vmax=5.0, cmap="coolwarm")
-plt.show()
 
+
+params = posterior_sample[which, :]
 rays = zeros(100000, 4)
 n_rays = 0
-for(j in 1:size(y)[1])
-	f1 = jacobian(posterior_sample[which, :], x[1], y[j])
-	for(i in 2:size(x)[1])
-		f2 = jacobian(posterior_sample[which, :], x[i], y[j])
-		if(sign(f1) == -sign(f2))
-			rays[n_rays+1, :] = [[x[i], y[j], 0.0, 0.0]]
+for(j in 1:length(y))
+	f1 = jacobian(params, x[1], y[j])
+	for(i in 2:length(x))
+		f2 = jacobian(params, x[i], y[j])
+		if(sign(f1) != sign(f2))
+			(xs, ys) = fire_ray(params, x[i], y[j])
+			rays[n_rays+1, :] = [[x[i], y[j], xs, ys]]
 			n_rays += 1
 		end
 		f1 = f2
@@ -82,8 +84,9 @@ for(j in 1:size(y)[1])
 end
 rays = rays[1:n_rays, :]
 
-plt.figure(figsize=(8, 8))
-plt.plot(rays[:,1], rays[:,2], "k.", markersize=1)
+plt.hold(true)
+plt.plot(rays[:,1], rays[:,2], "w.", markersize=1)
+plt.plot(
 plt.show()
 
 #plt.xlabel("x_s")

### 2015-07-27 Lenses/BlobbyNIE.jl
Working (still need to investigate gaps)

@@ -73,7 +73,7 @@ end
 
 # Compute the jacobian of the lens-->source plane mapping at position (x, y).
 # h is the spacing for numerical differentiation
-function jacobian(parameters::Array{Float64, 2}, x::Float64, y::Float64, h::Float64=1E-6)
+function jacobian(parameters::Array{Float64, 2}, x::Float64, y::Float64, h::Float64=1E-7)
 	(xs1, ys1) = fire_ray(parameters, x + h, y)
 	(xs2, ys2) = fire_ray(parameters, x - h, y)
 

### 2015-07-27 lens_plots.jl

@@ -36,28 +36,9 @@ function jacobian_image(parameters::Array{Float64, 2}, x::Array{Float64, 1}, y::
 	return mag
 end
 
-x = linspace(-10,  10, 2001)
-y = linspace( 10, -10, 2001)
-mag = sign(jacobian_image(posterior_sample[which, :], x, y))
-
-## Use matplotlib's contour function to get the critical curve
-## http://stackoverflow.com/questions/5666056/matplotlib-extracting-data-from-contour-lines
-#contour = plt.contour(x, y, mag, [5.5, 5.51])
-#plt.clf()
-#plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
-#					vmin=-7.0, vmax=7.0, cmap="coolwarm")
-#contour = contour[:collections][:1]
-#contour = contour[:get_paths]()[1][:vertices]
-#plt.plot(contour[:,1], contour[:,2], "k", linewidth=2)
-#plt.show()
-
-## Fire the contour through to the source plane
-#xs = contour[:,1]
-#ys = contour[:,2]
-#for(i in 1:size(xs)[1])
-#	(xs[i], ys[i]) = fire_ray(posterior_sample[which, :],
-#									contour[i, 1], contour[i, 2])
-#end
+x = linspace(-10,  10, 3001)
+y = linspace( 10, -10, 3001)
+mag = magnification_image(posterior_sample[which, :], x, y)
 
 plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
 					vmin=-5.0, vmax=5.0, cmap="coolwarm")
@@ -66,36 +47,24 @@ plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
 params = posterior_sample[which, :]
 rays = zeros(100000, 4)
 n_rays = 0
-for(j in 1:length(y))
-	f1 = jacobian(params, x[1], y[j])
-	for(i in 2:length(x))
-		f2 = jacobian(params, x[i], y[j])
+for(j in 1:length(x))
+	for(i in 1:(length(y)-1))
+		f1 = jacobian(params, x[j], y[i])
+		f2 = jacobian(params, x[j], y[i+1])
 		if(sign(f1) != sign(f2))
[…]

### 2015-07-27 lens_plots.jl
Fixed more issues

@@ -19,7 +19,7 @@ function magnification_image(parameters::Array{Float64, 2}, x::Array{Float64, 1}
 	mag = zeros(length(y), length(x))
 	for(j in 1:length(y))
 		for(i in 1:length(x))
-			mag[i, j] = magnification(parameters, x[i], y[j])
+			mag[i, j] = magnification(parameters, x[j], y[i])
 		end
 	end
 	return mag
@@ -30,7 +30,7 @@ function jacobian_image(parameters::Array{Float64, 2}, x::Array{Float64, 1}, y::
 	mag = zeros(length(y), length(x))
 	for(j in 1:length(y))
 		for(i in 1:length(x))
-			mag[i, j] = jacobian(parameters, x[i], y[j])
+			mag[i, j] = jacobian(parameters, x[j], y[i])
 		end
 	end
 	return mag
@@ -52,11 +52,10 @@ for(j in 1:length(x))
 		f1 = jacobian(params, x[j], y[i])
 		f2 = jacobian(params, x[j], y[i+1])
 		if(sign(f1) != sign(f2))
-			(xs, ys) = fire_ray(params, x[i], 0.5*(y[j] + y[j+1]))
-			rays[n_rays+1, :] = [[x[i], 0.5*(y[j] + y[j+1]), xs, ys]]
+			(xs, ys) = fire_ray(params, x[j], y[i])
+			rays[n_rays+1, :] = [[x[j], y[i], xs, ys]]
 			n_rays += 1
 		end
-		f1 = f2
 	end
 end
 rays = rays[1:n_rays, :]
@@ -64,6 +63,7 @@ rays = rays[1:n_rays, :]
 plt.hold(true)
 plt.plot(rays[:,1], rays[:,2], "w.", markersize=1)
 plt.plot(rays[:,3], rays[:,4], "b.", markersize=1)
+plt.axis([-10.0, 10.0, -10.0, 10.0])
 plt.show()
 writedlm("rays.txt", rays)
 plt.show()

### 2015-07-27 lens_plots.jl
Plot a source and image

@@ -6,6 +6,7 @@ include("Lenses/BlobbyNIE.jl")
 
 # Load the posterior samples
 posterior_sample = readdlm("posterior_sample.txt")
+metadata = readdlm("Data/mock_metadata.txt")
 
 # Specify a row
 which = 1
@@ -64,7 +65,30 @@ plt.hold(true)
 plt.plot(rays[:,1], rays[:,2], "w.", markersize=1)
 plt.plot(rays[:,3], rays[:,4], "b.", markersize=1)
 plt.axis([-10.0, 10.0, -10.0, 10.0])
-plt.show()
 writedlm("rays.txt", rays)
+plt.show()
+
+src = vec(posterior_sample[which, 469:468 + metadata[1]*metadata[2]*metadata[8]^2])
+img = vec(posterior_sample[which, 469 + 2*metadata[1]*metadata[2]*metadata[8]^2:(size(posterior_sample)[2]-2)])
+src = transpose(reshape(src, int(metadata[2]*metadata[8]), int(metadata[1]*metadata[8])))
+img = transpose(reshape(img, int(metadata[2]), int(metadata[1])))
+
+plt.rc("font", size=20, family="serif", serif="Computer Sans")
+plt.rc("text", usetex=True)
+plt.subplot(1, 2, 1)
+plt.imshow(src, interpolation="nearest", cmap="Oranges", extent=[-10, 10, -10, 10])
+plt.hold(true)
+plt.plot(rays[:,3], rays[:,4], "k.", markersize=1)
+plt.title("Source")
+plt.gca().set_xticks([])
+plt.gca().set_yticks([])
+plt.subplot(1, 2, 2)
+plt.imshow(img, interpolation="nearest", cmap="Oranges", extent=[-10, 10, -10, 10])
+plt.hold(true)
+plt.plot(rays[:,1], rays[:,2], "k.", markersize=1)
+plt.title("Image")
+plt.axis(metadata[3:6])
+plt.gca().set_xticks([])
+plt.gca().set_yticks([])
 plt.show()
 

### 2015-07-27 lens_plots.jl
lower case t

@@ -74,7 +74,7 @@ src = transpose(reshape(src, int(metadata[2]*metadata[8]), int(metadata[1]*metad
 img = transpose(reshape(img, int(metadata[2]), int(metadata[1])))
 
 plt.rc("font", size=20, family="serif", serif="Computer Sans")
-plt.rc("text", usetex=True)
+plt.rc("text", usetex=true)
 plt.subplot(1, 2, 1)
 plt.imshow(src, interpolation="nearest", cmap="Oranges", extent=[-10, 10, -10, 10])
 plt.hold(true)

### 2015-07-27 lens_plots.jl
Set axis limits correctly

@@ -80,15 +80,16 @@ plt.imshow(src, interpolation="nearest", cmap="Oranges", extent=[-10, 10, -10, 1
 plt.hold(true)
 plt.plot(rays[:,3], rays[:,4], "k.", markersize=1)
 plt.title("Source")
-plt.gca().set_xticks([])
-plt.gca().set_yticks([])
+#plt.gca().set_xticks([])
+#plt.gca().set_yticks([])
+plt.axis(metadata[3:6])
 plt.subplot(1, 2, 2)
 plt.imshow(img, interpolation="nearest", cmap="Oranges", extent=[-10, 10, -10, 10])
 plt.hold(true)
 plt.plot(rays[:,1], rays[:,2], "k.", markersize=1)
 plt.title("Image")
 plt.axis(metadata[3:6])
-plt.gca().set_xticks([])
-plt.gca().set_yticks([])
+#plt.gca().set_xticks([])
+#plt.gca().set_yticks([])
 plt.show()
 

### 2015-07-28 Papers/ms.tex
Fixed minor error
Pictures of sources and images

@@
 is $\mathcal{H} \approx 129$ nats. 
+Three example models (lens and source) sampled from the posterior are shown
+in Figure~\ref{fig:sources}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.8]{sources.pdf}
+\caption{Three example sources (and the corresponding lensed, blurred images)
+representative of the posterior distribution. All three lens system scenarios
+have substructures, which cause subtle distortions from the usual shape of
+the caustics and critical curves (plotted as black curves).
+The angular scales are 3 arcseconds for the sources and 15
+arcseconds for the images.
+\label{fig:sources}}
+\end{center}
+\end{figure}
 

### 2015-07-28 lens_plots.jl
Code for source plots

@@ -8,88 +8,108 @@ include("Lenses/BlobbyNIE.jl")
 posterior_sample = readdlm("posterior_sample.txt")
 metadata = readdlm("Data/mock_metadata.txt")
 
-# Specify a row
-which = 1
 
-# Size of the 2D array
-M = size(posterior_sample)[1]
-N = size(posterior_sample)[2]
+plt.figure(figsize=(5, 6))
+for(which in 1:3)
+	# Size of the 2D array
+	M = size(posterior_sample)[1]
+	N = size(posterior_sample)[2]
 
-# Function to calculate magnification on a grid
-function magnification_image(parameters::Array{Float64, 2}, x::Array{Float64, 1}, y::Array{Float64, 1})
-	mag = zeros(length(y), length(x))
-	for(j in 1:length(y))
-		for(i in 1:length(x))
-			mag[i, j] = magnification(parameters, x[j], y[i])
+	# Function to calculate magnification on a grid
+	function magnification_image(parameters::Array{Float64, 2}, x::Array{Float64, 1}, y::Array{Float64, 1})
+		mag = zeros(length(y), length(x))
+		for(j in 1:length(y))
+			for(i in 1:length(x))
+				mag[i, j] = magnification(parameters, x[j], y[i])
+			end
+		end
+		return mag
+	end
+
+	# Function to calculate jacobian on a grid
+	function jacobian_image(parameters::Array{Float64, 2}, x::Array{Float64, 1}, y::Array{Float64, 1})
+		mag = zeros(length(y), length(x))
+		for(j in 1:length(y))
+			for(i in 1:length(x))
+				mag[i, j] = jacobian(parameters, x[j], y[i])
+			end
+		end
+		return mag
+	end
+
+	x = linspace(-10,  10, 3001)
+	y = linspace( 10, -10, 3001)
+	mag = magnification_image(posterior_sample[which, :], x, y)
+
+#	plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
+#						vmin=-5.0, vmax=5.0, cmap="coolwarm")
+
+
+	params = posterior_sample[which, :]
+	rays = zeros(100000, 4)
+	n_rays = 0
+	for(j in 1:length(x))
+		for(i in 1:(length(y)-1))
[…]

### 2015-07-28 Papers/ms.tex
Lumley
Final-ish editing

@@
 sample the posterior distribution and evaluate the marginal likelihood of the
-model parameters including the number of blobs in the source and the lens.
+model, including the summation over the unknown
+number of blobs in the source and the lens.
 We demonstrate the method on a simulated data set with a single
 substructure, which is recovered well with moderate uncertainties. We also
-apply the method to an image of the ``Cosmic Horseshoe'' system, and find some
+apply the method to the g-band
+image of the ``Cosmic Horseshoe'' system, and find some
 hints of potential substructures. However, we caution that such results could
@@
 \section{Introduction}
-Galaxy-galaxy lensing is a powerful astrophysical tool for studying
+Galaxy-galaxy gravitational lensing is a powerful astrophysical tool for studying
 the distribution of matter, including dark matter, in galaxies
-\citep{treu}. It holds substantial potential as a technique for discovering
-and measuring the properties of dark matter substructures \citep{koopmans}.
-In recent years, this potential has been realised in several lens systems
+\citep{treu}. One promising application of lensing is to study
+and measure the properties of dark matter substructures in the lens
+galaxy \citep{koopmans}.
+In recent years, this promise has been realised in several lens systems
 which are thought to contain at least one dark substructure
@@
 \item How to compute the results (e.g. optimization methods, Markov Chain
-Monte Carlo with source parameters marginalized out analytically, or
-with the source parameters included).
+Monte Carlo [MCMC] with source parameters marginalized out analytically, or
+MCMC with the source parameters included).
 \end{enumerate}
@@
 for mathematical reasons, so
-that the source can be analytically marginalized over
+that the source can be analytically marginalized out
 \citep{2003ApJ...590..673W}. Unfortunately, a multivariate gaussian prior
-over pixel intensities can correspond to a very poor model of our prior
+over pixel intensities usually corresponds to a poor model of our prior
 beliefs about the source. It assigns virtually zero prior probability
@@
 surface brightness or density values; in fact, the marginal prior probability
-that any pixel is negative is 0.5.
+that any pixel is negative is typically 0.5.
 
@@
 
-\section{Finding dark substructures}
 If possible, it is best
@@
 comparison between our choices here and any proposed alternatives should be
-straightforward, provided a mixture of our model and another is considered
-a reasonable model of prior beliefs.
+straightforward, if a union of our hypothesis space and another
+can be considered a reasonable model of prior uncertainty.
 
@@
 in real surface brightness profiles.
-
 For computational speed, we choose the following
@@
 in Section~\ref{sec:convergence}). An upper ``limit'' on the SIE mass, with
-95\% posterior probability, is $5.21 M_\odot$. The algorithm has also found
+95\% posterior probability, is $5.21 \times 10^{12}$ solar masses.
+The algorithm has also found
 some possibilities where the substructure mass is much greater than this. In
@@
 Ross Fadely (NYU), and Alan Heavens (Edinburgh)
-for valuable discussion.
+for valuable discussion. Thomas Lumley (Auckland) also deserves credit for
+ending BJB's usage of the jet colormap.
 This work was funded by a Marsden Fast Start grant from the Royal Society of

### 2015-07-28 Papers/ms.tex
More edits, found mistake in blob normalisation that now needs checking throughout

@@
 
-\date{To be submitted to MNRAS}
+\date{}
 
@@
 moderately flexible (e.g. a mixture model, \citet{2011MNRAS.412.2521B})
-or free-form (e.g. pixellated) model for the surface brightness profile of the source
+or free-form (e.g. pixellated) model for the surface brightness profile of the source;\\
 \item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid
-[SIE]) or flexible model (e.g. pixellated) for the mass profile of the lens
+[SIE]) or flexible model (e.g. pixellated) for the mass profile of the lens; and\\
 \item How to compute the results (e.g. optimization methods, Markov Chain
@@
 The main differences are:
-i) we use a simpler and faster set of basis functions,
+i) we use a simpler and faster set of basis functions;
 ii) we apply it to the lens as well as the source, allowing for the
-possibility of substructure, and
+possibility of substructure; and
 iii) the implementation is based on a C++ template library developed by
@@
 multi-band data; this will be reserved for a future contribution.
-
-If possible, it is best
+The source code for this project is available at
+{\tt http://www.github.com/eggplantbren/Lensing2}.
+
 If we are interested in detecting and measuring the properties of
@@
 \begin{array}{lr}
-\frac{A}{2\pi w^2}\left[1 - \left(\frac{r}{w}\right)^2\right], & r \leq w\\
+\frac{2A}{\pi w^2}\left[1 - \left(\frac{r}{w}\right)^2\right], & r \leq w\\
 0, & \textnormal{otherwise}
@@
 \begin{array}{lr}
-\frac{A_i}{2\pi w_i^2}\left[1 - \left(\frac{r_i}{w_i}\right)^2\right], & r_i \leq w_i\\
+\frac{2A_i}{\pi w_i^2}\left[1 - \left(\frac{r_i}{w_i}\right)^2\right], & r_i \leq w_i\\
 0, & \textnormal{otherwise}
@@
 where $r_i = \sqrt{(x - x_i^{\rm src})^2 + (y - y_i^{\rm src})^2}$.
-
 Under these assumptions, the source can be described in its entirety

### 2015-07-29 Papers/ms.tex
Correct formulas
Bracket style
Finished editing pass

@@
 \begin{array}{lr}
-\frac{2A}{\pi w^2}\left[1 - \left(\frac{r}{w}\right)^2\right], & r \leq w\\
+\frac{2A}{\pi w^2}\left(1 - \frac{r^2}{w^2}\right), & r \leq w\\
 0, & \textnormal{otherwise}
@@
 \begin{array}{lr}
-\frac{2A_i}{\pi w_i^2}\left[1 - \left(\frac{r_i}{w_i}\right)^2\right], & r_i \leq w_i\\
+\frac{2A_i}{\pi w_i^2}\left(1 - \frac{r_i^2}{w_i^2}\right), & r_i \leq w_i\\
 0, & \textnormal{otherwise}
@@
 \begin{array}{lr}
-\frac{M}{2\pi v^2}\left[1 - \left(\frac{r}{v}\right)^2\right], & r \leq v\\
+\frac{2M}{\pi v^2}\left(1 - \frac{r^2}{v^2}\right), & r \leq v\\
 0, & \textnormal{otherwise}
@@
 \end{eqnarray}
+which is the same as the surface brightness profile of a source blob.
 The deflection angles for a single blob are:
-
-%Menc = 4.*components[i][2]/widthsq*(0.5*rsq -
-%				rsq*rsq/(4*widthsq));
-
 \begin{eqnarray}
@@
 \begin{array}{lr}
--\frac{\left[2(r/v)^2 - (r/v)^4\right]Mx}{r^3}, & r \leq v\\
--\frac{Mx}{\pi r^3}, & \textnormal{otherwise}
+\left(2 - r^2/v^2\right)\frac{Mx}{\pi v^2}, & r \leq v\\
+\frac{Mx}{\pi r^2}, & \textnormal{otherwise}
 \end{array}
@@
 \begin{array}{lr}
--\frac{\left[2(r/v)^2 - (r/v)^4\right]My}{r^3}, & r \leq v\\
--\frac{My}{\pi r^3}, & \textnormal{otherwise}
+\left(2 - r^2/v^2\right)\frac{My}{\pi v^2}, & r \leq v\\
+\frac{My}{\pi r^2}, & \textnormal{otherwise}
 \end{array}
@@
 \end{eqnarray}
-where $r=\sqrt{x^2 + y^2}$. For $N$ such blobs the deflection angles are
+where $r=\sqrt{x^2 + y^2}$. These do not depend on any slow functions such
+as square roots or exponentials.
+For $N$ such blobs the deflection angles are
 summed over all blobs. Therefore the lens can be entirely described by
@@
 \end{eqnarray}
-and $\boldsymbol{\theta}_{\rm SIE}$ describes the parameters for the SIE
+and $\boldsymbol{\theta}_{\rm SIE}$ describes the parameters for the SIE+$\gamma$
 component:
@@
 \boldsymbol{\theta}_{\rm SIE} = \left\{
-b, q, (x_c^{\rm SIE}, y_c^{\rm SIE}), \theta, \gamma, \theta_\gamma
+b, q, x_c^{\rm SIE}, y_c^{\rm SIE}, \theta, \gamma, \theta_\gamma
 \right\}.
@@
 a Jeffreys prior) between $a$ and $b$. The notation $T(\alpha, \beta)$ after
-a distribution denotes truncation to the interval $[\alpha, \beta]$.
+a distribution denotes truncation to the interval $[\alpha, \beta]$. The
+constant {\tt imageWidth} is the geometric mean of the image dimensions in
+the $x$ and $y$ directions.
 \label{tab:priors}}
@@
 of possible sources and lenses.
-
 To compute the posterior distribution for the parameters
@@
 
-Evaluating likelihood function requires that we compute a ``mock'' image from
+Evaluating the likelihood function requires that we compute a ``mock'' image from
 the current setting of the parameters. This mock image is calculated using
@@
 substructure. The image is shown in Figure~\ref{fig:simulated_image}, and
-consists of 100 $\times$ 100 pixels. The PSF was compact and was
+consists of 100 $\times$ 100 pixels. The point spread function (PSF) was compact and was
 defined on a 5 $\times$ 5 grid. The data was created by firing only one ray
@@
 
+For the purposes of a paper, static summaries are more convenient than movies.
+One useful summary is based on the concept of empirical measure.
 The {\it empirical measure} of the substructure positions is a function that
-takes the substructure positions $(x_i^{\rm lens}, y_i^{\rm lens})$ and
+takes the actual substructure positions $(x_i^{\rm lens}, y_i^{\rm lens})$ and
 produces a ``density function'' over two dimensions, composed of delta
@@
 needs to be redefined, so we ask about the mass within some aperture of finite
-area. For an SIE, the mass (in dimensionless units) within the critical
-ellipse is simply $b^2$. However, the blobs have finite total masses
+area. For an SIE, the mass (in dimensionless units based on the critical density)
+within the critical
+ellipse is simply $\pi b^2$. However, the blobs have finite total masses
 $\{M_i\}$. To obtain the posterior distribution for the lens masses, one must
@@
 With 95\% probability the substructure mass is less than 5.80$\times 10^{12}$ solar masses and with 75\% probability it is less than 3.56$\times 10^{12}$ solar masses.
-As the einstein ring implies a mass of about $5 \times 10^{12}$
-solar masses, it is not the substructure mass over the entire domain
-that is of interest.
+As the einstein ring itself implies a mass of about $5 \times 10^{12}$
+solar masses, these summaries are affected by the possibility of blobs outside
+the main einstein ring.
 
@@
 the input modelling assumptions, and a slightly different (yet still
-``reasonable'') set of choices might yield different results. For example, if
+reasonable) set of choices might yield different results. For example, if
 the density profile of the lens was smooth but not of the SIE form, and the
@@
 Another option which we defer to future work is to implement a more flexible
-model (such as a concentric mixture of concentric elliptical lenses). This
+model (such as a mixture of concentric elliptical lenses). This
 result is consistent with that of \citet{2008MNRAS.388..384D}, who found a slight preference for an elliptical power law profile over the SIE
@@
 imperfect sampling. Whereas a standard Metropolis sampler would move around
-very slowly in the hypothesis space, the DNS algorithm naturally spends some
+very slowly in the hypothesis space, DNS naturally spends a non-negligible fraction
 of the time sampling the prior. Therefore, a particle exploring the parameter
@@
 is a natural feature of the algorithm (and is also present in related
-algorithms such as parallel tempering). Despite this feature, the patchy
+algorithms such as parallel tempering). Despite this, the patchy
 nature of Figure~\ref{fig:masses2} suggests that posterior exploration is

### 2015-07-29 Papers/ms.tex
Fixed awkward sentence

@@
 The model assumptions used in this paper are fairly simple. In future work we
-intend to generalise the smooth lens model beyond the overly simplistic
-SIE+$\gamma$ model, and to generalize the model to multi-band data. Applications
+intend to generalize the model to multi-band data, and extend the
+smooth lens model beyond the overly simplistic
+SIE+$\gamma$ assumption. Applications
 to other systems are also forthcoming, as well as variants on the model using

### 2015-07-30 Papers/ms.tex
GFL comments

@@
 \item Whether to use a simply parameterized (e.g. a Sérsic profile),
-moderately flexible (e.g. a mixture model, \citet{2011MNRAS.412.2521B})
+moderately flexible \citep[e.g. a mixture model,][]{2011MNRAS.412.2521B}
 or free-form (e.g. pixellated) model for the surface brightness profile of the source;\\
@@
 The SIE+$\gamma$ has nine free parameters:
-the (circularized) einstein radius $b$, axis ratio $q$, central position
+the (circularized) Einstein radius $b$, axis ratio $q$, central position
 $(x_c, y_c)$, orientation angle $\theta$, the external shear $\gamma$, and the
@@
 \caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
-lens plus a single dark substructure. The image was blurred by a PSF and had
-some noise added.\label{fig:simulated_image}}
+lens in the center of the image (which does not contribute any flux), plus a
+single substructure close to the top left image.
+The image was blurred by a PSF and had some noise added.\label{fig:simulated_image}}
 \end{center}
@@
 With 95\% probability the substructure mass is less than 5.80$\times 10^{12}$ solar masses and with 75\% probability it is less than 3.56$\times 10^{12}$ solar masses.
-As the einstein ring itself implies a mass of about $5 \times 10^{12}$
+As the Einstein ring itself implies a mass of about $5 \times 10^{12}$
 solar masses, these summaries are affected by the possibility of blobs outside
-the main einstein ring.
+the main Einstein ring.
 

### 2015-09-01 display.py
Auto histogram (bins thing was wrong)

@@ -127,7 +127,7 @@ ylabel('Total substructure mass')
 savefig('masses.pdf', bbox_inches='tight')
 show()
 
-hist(output[:,18], bins=arange(0, 11) - 0.5*0.3, width=0.3, alpha=0.3)
+hist(output[:,18], 100, alpha=0.8)
 xlim([-0.2, 10.2])
 gca().set_xticks(arange(0, 11))
 xlabel('$N_{\\rm lens}$')

### 2015-09-01 Papers/ms.tex
Updated keywords
Color coding of revisions

@@
 \usepackage{float}
+\usepackage{color}
 
 \usepackage{epstopdf}
+
+% For revisions
+\newcommand{\revisions}{\color{blue}}
 
@@
 \begin{keywords}
-gravitational lensing --- methods: data analysis --- methods: statistical
+gravitational lensing: strong --- methods: data analysis --- methods: statistical
 \end{keywords}
@@
 
-\section{Simulated Data}
+\section{{\revisions``Easy''} Simulated Data}
 To demonstrate the method, we generated a simulated dataset with a single
@@
 \end{figure}
+
+{\revisions
+\section{``Harder'' Simulated Data}
+}
 

### 2015-09-01 Papers/ms.tex
A little more revision

@@
 number of blobs in the source and the lens.
-We demonstrate the method on a simulated data set with a single
-substructure, which is recovered well with moderate uncertainties. We also
+We demonstrate the method on {\revisions two
+simulated data sets: one with a single
+substructure, and one with ten}. We also
 apply the method to the g-band
@@
 \section{{\revisions``Easy''} Simulated Data}
-To demonstrate the method, we generated a simulated dataset with a single
-substructure. The image is shown in Figure~\ref{fig:simulated_image}, and
+To demonstrate the method, we generated a simulated dataset {\revisions where
+the lens was an SIE$+\gamma$ profile with a single additional substructure}.
+The image is shown in Figure~\ref{fig:simulated_image}, and
 consists of 100 $\times$ 100 pixels. The point spread function (PSF) was compact and was
@@
 \section{``Harder'' Simulated Data}
+To further test the algorithm, we created a ``harder'' simulated image, where
+the lens consisted of an SIE+$\gamma$ profile plus 10 additional substructures.
+
 }

### 2015-09-01 Papers/ms.tex
More sensible image names

@@
 the lens was an SIE$+\gamma$ profile with a single additional substructure}.
-The image is shown in Figure~\ref{fig:simulated_image}, and
+The image is shown in Figure~\ref{fig:image1}, and
 consists of 100 $\times$ 100 pixels. The point spread function (PSF) was compact and was
@@
 \begin{center}
-\includegraphics[scale=0.5]{simulated_image.pdf}
+\includegraphics[scale=0.5]{image1.pdf}
 \caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
@@
 single substructure close to the top left image.
-The image was blurred by a PSF and had some noise added.\label{fig:simulated_image}}
+The image was blurred by a PSF and had some noise added.\label{fig:image1}}
 \end{center}
@@
 As a further demonstration the method, we apply it to the g-band data
-of the Cosmic Horseshoe J1004+4112 \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
+of the Cosmic Horseshoe J1004+4112 \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:image3}.
 For this system,
@@
 \begin{center}
-\includegraphics[scale=0.5]{horseshoe_image.pdf}
+\includegraphics[scale=0.5]{image3.pdf}
 \caption{The g-band INT image of the Cosmic Horseshoe, with the lens galaxy
 subtracted.
-\label{fig:horseshoe_image}}
+\label{fig:image3}}
 \end{center}

### 2015-09-01 Papers/images.py

@@ -7,7 +7,15 @@ imshow(img, interpolation="nearest", cmap="Oranges")
 gca().set_xticklabels("")
 gca().set_yticklabels("")
 title("Simulated Dataset")
-savefig("simulated_image.pdf", bbox_inches="tight")
+savefig("image1.pdf", bbox_inches="tight")
+show()
+
+img = loadtxt("../Data/harder_image.txt")
+imshow(img, interpolation="nearest", cmap="Oranges")
+gca().set_xticklabels("")
+gca().set_yticklabels("")
+title("Simulated Dataset")
+savefig("image2.pdf", bbox_inches="tight")
 show()
 
 img = loadtxt("../Data/horseshoe_image.txt")
@@ -19,6 +27,6 @@ gca().set_yticklabels([-7.66, 0, 7.66])
 xlabel("$x$ (arcseconds)")
 ylabel("$y$ (arcseconds)")
 title("Cosmic Horseshoe")
-savefig("horseshoe_image.pdf", bbox_inches="tight")
+savefig("image3.pdf", bbox_inches="tight")
 show()
 

### 2015-09-01 lens_plots.jl
Plot the lens positions

@@ -46,6 +46,20 @@ for(which in 1:3)
 
 
 	params = posterior_sample[which, :]
+	x_substructures = params[20:29]
+	y_substructures = params[30:39]
+	m_substructures = params[40:49]
+	x_substructures = x_substructures[m_substructures .!= 0.]
+	y_substructures = y_substructures[m_substructures .!= 0.]
+
+	# Convert x and y to pixel coordinates for overplotting
+	dx = (metadata[4] - metadata[3])/metadata[2]
+	dy = (metadata[6] - metadata[5])/metadata[1]
+	x_substructures = (x_substructures - metadata[3])/dx - 0.5
+	y_substructures = (metadata[6] - y_substructures)/dy - 0.5
+	x_nie = (params[6] - metadata[3])/dx - 0.5
+	y_nie = (metadata[6] - params[6])/dy - 0.5
+
 	rays = zeros(100000, 4)
 	n_rays = 0
 	for(j in 1:length(x))
@@ -102,6 +116,12 @@ for(which in 1:3)
 	plt.imshow(img, interpolation="nearest", cmap="Oranges", extent=metadata[3:6])
 	plt.hold(true)
 	plt.plot(rays[:,1], rays[:,2], "k.", markersize=1)
+
+	# Plot center of NIE
+	plot(x_nie, y_nie, 'yo', markersize=10)
+	# Substructures
+	plot(x_substructures, y_substructures, 'wo', alpha=0.5)
+
 	if(which == 1)
 		plt.title("Image")
 	end

### 2015-09-02 Papers/ms.tex
Image of the harder data

@@
 \includegraphics[scale=0.4]{substructures.pdf}
-\caption{The simulated data, with substructure positions overlaid (a
+\caption{The {\revisions `easy'} simulated data, with substructure positions overlaid (a
 Monte Carlo approximation to the posterior expectation of the empirical
@@
 the lens consisted of an SIE+$\gamma$ profile plus 10 additional substructures.
-
-}
+The image is shown in Figure~\ref{fig:image2}. With the easy dataset, there
+was little hope of measuring the substructure mass function parameter
+$\mu_{\rm lens}$ since there was only a single substructure which would provide
+little information about $\mu_{\rm lens}$ (only constraining its general
+order of magnitude), even if its mass were measured perfectly.}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{image2.pdf}
+\caption{{\revisions The `harder' simulated data, consisting of a more
+complex source profile, and a lens with 10 substructures.}
+\label{fig:image2}}
+\end{center}
+\end{figure}
 

### 2015-09-03 MyModel.cpp
Remove deprecated 'update' methods

@@ -19,6 +19,7 @@ MyModel::MyModel()
 ,surface_brightness(Data::get_instance().get_x_rays())
 ,model_image(Data::get_instance().get_ni(),
 		vector<long double>(Data::get_instance().get_nj()))
+,staleness1(0), staleness2(0)
 {
 
 }
@@ -145,8 +146,6 @@ void MyModel::shoot_rays()
 			ys[i][j] = y[i][j] - ay;
 		}
 	}
-
-	staleness2 = 0;
 }
 
 void MyModel::calculate_surface_brightness()
@@ -169,62 +168,6 @@ void MyModel::calculate_surface_brightness()
 			psf.blur_image2(surface_brightness);
 		else
 			psf.blur_image(surface_brightness);
-	}
-
-	staleness1 = 0;
-}
-
-void MyModel::update_surface_brightness()
-{
-	staleness1++;
-
-	vector< vector<long double> >
-		delta_surface_brightness(surface_brightness.size(),
-			vector<long double>(surface_brightness[0].size(), 0.));
-
-	for(size_t i=0; i<xs.size(); i++)
-	{
-		for(size_t j=0; j<xs[i].size(); j++)
-		{
-			delta_surface_brightness[i][j] = source.evaluate_diff
-							(xs[i][j], ys[i][j]);
-		}
-	}
-
-	if(Data::get_instance().psf_is_highres())
-	{
-		// Blur using the PSF
-		const PSF& psf = Data::get_instance().get_psf();
-
-		if(Data::get_instance().use_fft())
-			psf.blur_image2(delta_surface_brightness);
-		else
-			psf.blur_image(delta_surface_brightness);
-	}
-
-	// Add the delta to the surface brightness
-	for(size_t i=0; i<surface_brightness.size(); i++)
-		for(size_t j=0; j<surface_brightness[i].size(); j++)
-			surface_brightness[i][j] += delta_surface_brightness[i][j];
-}
-
-
-void MyModel::update_rays()
-{
-	staleness2++;
-
-	const vector< vector<long double> >& x = Data::get_instance().get_x_rays();
-	const vector< vector<long double> >& y = Data::get_instance().get_y_rays();
-
-	double ax, ay;
-	for(size_t i=0; i<xs.size(); i++)
-	{
-		for(size_t j=0; j<xs[i].size(); j++)
-		{
-			lens.alpha_diff(x[i][j], y[i][j], ax, ay);
-			xs[i][j] -= ax;
-			ys[i][j] -= ay;
-		}
 	}
 }
 

### 2015-09-03 MyModel.h

@@ -33,9 +33,7 @@ class MyModel:public DNest3::Model
 		unsigned int staleness1, staleness2;
 
 		void shoot_rays();
-		void update_rays();
 		void calculate_surface_brightness();
-		void update_surface_brightness();
 		void calculate_model_image();
 
 	public:

### 2015-09-03 MyModel.cpp
Masking

@@ -135,27 +135,35 @@ void MyModel::shoot_rays()
 {
 	const vector< vector<long double> >& x = Data::get_instance().get_x_rays();
 	const vector< vector<long double> >& y = Data::get_instance().get_y_rays();
+	const vector< vector<double> >& sigma = Data::get_instance().get_sigma();
 
 	double ax, ay;
 	for(size_t i=0; i<xs.size(); i++)
 	{
 		for(size_t j=0; j<xs[i].size(); j++)
 		{
-			lens.alpha(x[i][j], y[i][j], ax, ay);
-			xs[i][j] = x[i][j] - ax;
-			ys[i][j] = y[i][j] - ay;
+			// Extremely high sigma values are "masked"
+			if(sigma[i][j] < 1E100)
+			{
+				lens.alpha(x[i][j], y[i][j], ax, ay);
+				xs[i][j] = x[i][j] - ax;
+				ys[i][j] = y[i][j] - ay;
+			}
 		}
 	}
 }
 
 void MyModel::calculate_surface_brightness()
 {
+	const vector< vector<double> >& sigma = Data::get_instance().get_sigma();
+
 	for(size_t i=0; i<xs.size(); i++)
 	{
 		for(size_t j=0; j<xs[i].size(); j++)
 		{
-			surface_brightness[i][j] = source.evaluate(xs[i][j],
-								ys[i][j]);
+			// Extremely high sigma values are "masked"
+			if(sigma[i][j] < 1E100)
+				surface_brightness[i][j] = source.evaluate(xs[i][j], ys[i][j]);
 		}
 	}
 

### 2015-09-03 MyModel.cpp
Don't include masked pixels in log likelihood

@@ -91,10 +91,13 @@ double MyModel::logLikelihood() const
 	{
 		for(size_t j=0; j<image[i].size(); j++)
 		{
-			var = sigma[i][j]*sigma[i][j] + sigma0*sigma0
-					+ sigma1*model_image[i][j];
-			logL += -0.5*log(2.*M_PI*var) -
-			0.5*pow(image[i][j] - model_image[i][j], 2)/var;
+			if(sigma[i][j] < 1E100)
+			{
+				var = sigma[i][j]*sigma[i][j] + sigma0*sigma0
+						+ sigma1*model_image[i][j];
+				logL += -0.5*log(2.*M_PI*var) -
+				0.5*pow(image[i][j] - model_image[i][j], 2)/var;
+			}
 		}
 	}
 

### 2015-09-03 Papers/ms.tex
Truth values for easy data

@@
 the problem, and the kind of outputs the method can produce.
+{\revisions
+The SIE$+\gamma$ parameters were
+$\{b, q, x_c^{\rm SIE}, y_c^{\rm SIE}, \theta, \gamma, \theta_\gamma\}
+= \{5.25, 0.323, 0.191, -0.341, 0.833, 0.0322, 0.497\}$, where the length
+units in the image plane are arbitrary, and rotation angles are measured in
+radians. The single substructure is located at $(-2.57, 2.20)$, close to the
+upper left image. Its mass is 2.50 units, using the convention where the
+critical density is 1. For comparison, the SIE mass within its critical
+ellipse is $\pi b^2 = 86.6$ units.
+}
 
@@
 \caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
-lens in the center of the image (which does not contribute any flux), plus a
+lens close to the center of the image (which does not contribute any flux), plus a
 single substructure close to the top left image.
-The image was blurred by a PSF and had some noise added.\label{fig:image1}}
+The image was blurred by a PSF and had some noise added.
+In an arbitrary system of units, this image extends from -8 to 8 in the
+$x$ and $y$ directions.\label{fig:image1}}
 \end{center}

### 2015-09-03 Papers/ms.tex
slight wording change
Fixed empirical measure equations
Forgot revisions

@@
 units in the image plane are arbitrary, and rotation angles are measured in
-radians. The single substructure is located at $(-2.57, 2.20)$, close to the
-upper left image. Its mass is 2.50 units, using the convention where the
+radians. The single substructure is located at $(-2.57, 2.20)$, about halfway
+between the center and the upper left image.
+Its mass is 2.50 units, using the convention where the
 critical density is 1. For comparison, the SIE mass within its critical
@@
 The posterior expected value of the empirical measure is:
+{\revisions
 \begin{eqnarray}
@@
 \sum_{i=1}^{N_{\rm lens}}
-\delta^2\left(x - x_i^{\rm lens}, y_i^{\rm lens} - y_i^{\rm lens}\right)
+\delta^2\left(x - x_i^{\rm lens}, y - y_i^{\rm lens}\right)
 \, d\boldsymbol{\theta}
 \end{eqnarray}
+}
 where $\boldsymbol{\theta}$ denotes all parameters and hyperparameters
@@
 obtain the expected value of the empirical measure using:
+{\revisions
 \begin{eqnarray}
@@
 \sum_{k=1}^n
-\sum_{i=1}^{N_{\rm lens}}
-\delta^2\left(x - x_i^{\rm lens}, y_i^{\rm lens} - y_i^{\rm lens}\right)
-\end{eqnarray}
+\sum_{i=1}^{N_{\rm lens}^k}
+\delta^2\left(x - x_{ik}^{\rm lens}, y - y_{ik}^{\rm lens}\right)
+\end{eqnarray}
+}
 where $n$ is the number of posterior samples. The resulting function is

### 2015-09-04 Papers/images.py
Show the substructures

@@ -3,7 +3,30 @@ rc("font", size=16, family="serif", serif="Computer Sans")
 rc("text", usetex=True)
 
 img = loadtxt("../Data/mock_image.txt")
+truth = loadtxt("../Data/mock_truth.txt")
+metadata = loadtxt("../Data/mock_metadata.txt")
+
+# Convert x and y to pixel coordinates for overplotting
+dx = (metadata[3] - metadata[2])/metadata[1]
+dy = (metadata[5] - metadata[4])/metadata[0]
+x_substructures = truth[19:29]
+y_substructures = truth[29:39]
+x_substructures = x_substructures[x_substructures != 0.]
+y_substructures = y_substructures[y_substructures != 0.]
+x_substructures = (x_substructures - metadata[2])/dx - 0.5
+y_substructures = (metadata[5] - y_substructures)/dy - 0.5
+x_nie = (truth[5] - metadata[2])/dx - 0.5
+y_nie = (metadata[5] - truth[6])/dy - 0.5
+
 imshow(img, interpolation="nearest", cmap="Oranges")
+hold(True)
+# Plot center of NIE
+plot(x_nie, y_nie, 'wo', markersize=15)
+# Substructures
+plot(x_substructures, y_substructures, 'g*', markersize=15)
+xlim([-0.5, metadata[1] - 0.5])
+ylim([metadata[0] - 0.5, -0.5])
+
 gca().set_xticklabels("")
 gca().set_yticklabels("")
 title("Simulated Dataset")

### 2015-09-04 Papers/images.py
Show the substructures

@@ -34,7 +34,29 @@ savefig("image1.pdf", bbox_inches="tight")
 show()
 
 img = loadtxt("../Data/harder_image.txt")
+truth = loadtxt("../Data/harder_truth.txt")
+metadata = loadtxt("../Data/mock_metadata.txt")
+
+# Convert x and y to pixel coordinates for overplotting
+dx = (metadata[3] - metadata[2])/metadata[1]
+dy = (metadata[5] - metadata[4])/metadata[0]
+x_substructures = truth[19:29]
+y_substructures = truth[29:39]
+x_substructures = x_substructures[x_substructures != 0.]
+y_substructures = y_substructures[y_substructures != 0.]
+x_substructures = (x_substructures - metadata[2])/dx - 0.5
+y_substructures = (metadata[5] - y_substructures)/dy - 0.5
+x_nie = (truth[5] - metadata[2])/dx - 0.5
+y_nie = (metadata[5] - truth[6])/dy - 0.5
+
 imshow(img, interpolation="nearest", cmap="Oranges")
+hold(True)
+# Plot center of NIE
+plot(x_nie, y_nie, 'wo', markersize=15)
+# Substructures
+plot(x_substructures, y_substructures, 'g*', markersize=15)
+xlim([-0.5, metadata[1] - 0.5])
+ylim([metadata[0] - 0.5, -0.5])
 gca().set_xticklabels("")
 gca().set_yticklabels("")
 title("Simulated Dataset")

### 2015-09-04 Papers/ms.tex
Captions mention the symbols

@@
 \caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
-lens close to the center of the image (which does not contribute any flux), plus a
-single substructure close to the top left image.
+lens close to the center of the image, indicated by the white circle, plus a
+single substructure close to the top left image (indicated by a star symbol).
 The image was blurred by a PSF and had some noise added.
@@
 \caption{{\revisions The `harder' simulated data, consisting of a more
-complex source profile, and a lens with 10 substructures.}
+complex source profile, and a lens with an SIE+$\gamma$ (whose centre is
+indicated by a white circle) and ten substructures. Only five of the
+substructures (star symbols) occured within the square image boundary, but the other five still have an effect on the image.}
 \label{fig:image2}}

### 2015-09-04 display.py
consistency with what's in the paper

@@ -74,9 +74,9 @@ for i in xrange(0, output.shape[0]):
 	imshow(img2, interpolation='nearest', cmap='Oranges')
 	hold(True)
 	# Plot center of NIE
-	plot(x_nie, y_nie, 'yo', markersize=10)
+	plot(x_nie, y_nie, 'wo', markersize=15, alpha=0.5)
 	# Substructures
-	plot(x_substructures, y_substructures, 'wo', alpha=0.5)
+	plot(x_substructures, y_substructures, 'g*', markersize=15, alpha=0.5)
 	xlim([-0.5, metadata[1] - 0.5])
 	ylim([metadata[0] - 0.5, -0.5])
 	title('Model Image ' + str(i+1))

### 2015-09-05 display.py
Code to overplot the true mass

@@ -124,6 +124,10 @@ plot(mass_units*pi*output[:,2]**2, mass_units*output[:,39:48].sum(axis=1),\
 					'bo', markersize=5, alpha=0.2)
 xlabel('SIE mass (within critical ellipse)')
 ylabel('Total substructure mass')
+
+# Plot the true masses
+#truth = loadtxt('Data/mock_truth.txt')
+#plot(pi*truth[2], truth[39:49].sum(), 'ro')
 savefig('masses.pdf', bbox_inches='tight')
 show()
 

### 2015-09-05 lens_plots.jl
Consistency with new symbols

@@ -118,9 +118,9 @@ for(which in 1:3)
 	plt.plot(rays[:,1], rays[:,2], "k.", markersize=1)
 
 	# Plot center of NIE
-	plot(x_nie, y_nie, 'yo', markersize=10)
+	plot(x_nie, y_nie, 'wo', markersize=15)
 	# Substructures
-	plot(x_substructures, y_substructures, 'wo', alpha=0.5)
+	plot(x_substructures, y_substructures, "g*", markersize=15, alpha=0.5)
 
 	if(which == 1)
 		plt.title("Image")

### 2015-09-05 lens_plots.jl
Plots not quite working

@@ -118,9 +118,9 @@ for(which in 1:3)
 	plt.plot(rays[:,1], rays[:,2], "k.", markersize=1)
 
 	# Plot center of NIE
-	plot(x_nie, y_nie, 'wo', markersize=15)
+	plt.plot(x_nie, y_nie, "wo", markersize=15)
 	# Substructures
-	plot(x_substructures, y_substructures, "g*", markersize=15, alpha=0.5)
+	plt.plot(x_substructures, y_substructures, "g*", markersize=15, alpha=0.5)
 
 	if(which == 1)
 		plt.title("Image")

### 2015-09-05 lens_plots.jl
Plot the substructure positions

@@ -52,13 +52,13 @@ for(which in 1:3)
 	x_substructures = x_substructures[m_substructures .!= 0.]
 	y_substructures = y_substructures[m_substructures .!= 0.]
 
-	# Convert x and y to pixel coordinates for overplotting
+#	# Convert x and y to pixel coordinates for overplotting
 	dx = (metadata[4] - metadata[3])/metadata[2]
 	dy = (metadata[6] - metadata[5])/metadata[1]
 	x_substructures = (x_substructures - metadata[3])/dx - 0.5
 	y_substructures = (metadata[6] - y_substructures)/dy - 0.5
-	x_nie = (params[6] - metadata[3])/dx - 0.5
-	y_nie = (metadata[6] - params[6])/dy - 0.5
+	x_nie = params[6]#(params[6] - metadata[3])/dx - 0.5
+	y_nie = params[7]#(metadata[6] - params[7])/dy - 0.5
 
 	rays = zeros(100000, 4)
 	n_rays = 0
@@ -118,16 +118,16 @@ for(which in 1:3)
 	plt.plot(rays[:,1], rays[:,2], "k.", markersize=1)
 
 	# Plot center of NIE
-	plt.plot(x_nie, y_nie, "wo", markersize=15)
+	plt.plot(x_nie, y_nie, "wo")
 	# Substructures
-	plt.plot(x_substructures, y_substructures, "g*", markersize=15, alpha=0.5)
+	plt.plot(x_substructures, y_substructures, "g*", alpha=0.5)
 
 	if(which == 1)
 		plt.title("Image")
 	end
 	plt.axis(metadata[3:6])
-	#plt.gca().set_xticks([])
-	#plt.gca().set_yticks([])
+	plt.gca().set_xticks([])
+	plt.gca().set_yticks([])
 end
 
 plt.savefig("sources.pdf", bbox_inches="tight")

### 2015-09-06 display.py
Use proper coordinates (not pixels)

@@ -41,14 +41,7 @@ for i in xrange(0, output.shape[0]):
 	x_substructures = x_substructures[good]
 	y_substructures = y_substructures[good]
 	m_substructures = m_substructures[good]
-
-	# Convert x and y to pixel coordinates for overplotting
-	dx = (metadata[3] - metadata[2])/metadata[1]
-	dy = (metadata[5] - metadata[4])/metadata[0]
-	x_substructures = (x_substructures - metadata[2])/dx - 0.5
-	y_substructures = (metadata[5] - y_substructures)/dy - 0.5
-	x_nie = (x[5] - metadata[2])/dx - 0.5
-	y_nie = (metadata[5] - x[6])/dy - 0.5
+	x_nie, y_nie = x[5], x[6]
 
 	# Extract images
 	# For MyModel2 (sersic source only), replace 468 with 66
@@ -63,22 +56,20 @@ for i in xrange(0, output.shape[0]):
 	img2 = img2.reshape((metadata[0], metadata[1]))
 
 	subplot(2,3,1)
-	imshow(src, interpolation='nearest', cmap='Oranges')
+	imshow(src, extent=metadata[2:6], interpolation='nearest', cmap='Oranges')
 	title('Model Source ' + str(i+1))
 
 	subplot(2,3,2)
-	imshow(img1, interpolation='nearest', cmap='Oranges')
+	imshow(img1, extent=metadata[2:6], interpolation='nearest', cmap='Oranges')
 	title('Unblurred Image ' + str(i+1))
 
 	subplot(2,3,3)
-	imshow(img2, interpolation='nearest', cmap='Oranges')
+	imshow(img2, extent=metadata[2:6], interpolation='nearest', cmap='Oranges')
 	hold(True)
 	# Plot center of NIE
 	plot(x_nie, y_nie, 'wo', markersize=15, alpha=0.5)
 	# Substructures
 	plot(x_substructures, y_substructures, 'g*', markersize=15, alpha=0.5)
-	xlim([-0.5, metadata[1] - 0.5])
-	ylim([metadata[0] - 0.5, -0.5])
 	title('Model Image ' + str(i+1))
 	hold(False)
 

### 2015-09-06 Papers/ms.tex
Mention residuals
residual sentence

@@
 {\revisions
+For the sampled parameter values representing the posterior distribution, there
+was no structure in the residuals (not shown), when normalised by the noise
+standard deviation in each pixel. This is unsurprising since the model
+assumptions are entirely correct for this dataset.
+}
+
+{\revisions
 \section{``Harder'' Simulated Data}
@@
 \end{figure}
+
+{\revisions
+As with the easy dataset, the standardised residuals of the sampled models
+resembled noise.
+}
 

### 2015-09-07 display.py
Fixed bugs

@@ -118,7 +118,8 @@ ylabel('Total substructure mass')
 
 # Plot the true masses
 #truth = loadtxt('Data/mock_truth.txt')
-#plot(pi*truth[2], truth[39:49].sum(), 'ro')
+#hold(True)
+#plot(pi*truth[2]**2, truth[39:49].sum(), 'r*', markersize=20)
 savefig('masses.pdf', bbox_inches='tight')
 show()
 

### 2015-09-07 Papers/ms.tex
Mention residuals
Filenames etc changed to make way for dataset 2

@@
 we can verify that the results of the inference do behave in understandable
-ways. For example, in Figure~\ref{fig:masses},
+ways. For example, in Figure~\ref{fig:masses1},
 we plot the joint posterior distribution
@@
 \begin{center}
-\includegraphics[scale=0.4]{masses.pdf}
+\includegraphics[scale=0.4]{masses1.pdf}
 \caption{The joint posterior distribution for the SIE mass (integrated within
 its critical ellipse, which is not the critical curve of the lens overall),
-and the total mass in substructures.\label{fig:masses}}
+and the total mass in substructures.\label{fig:masses1}}
 \end{center}
@@
 The posterior distribution for $N_{\rm lens}$ is also clearly of interest, and
-is displayed in Figure~\ref{fig:N_lens}. The prior for this parameter was
+is displayed in Figure~\ref{fig:N_lens1}. The prior for this parameter was
 uniform from 0 to 10 (inclusive), and the possibility $N=0$ has been
@@
 \begin{center}
-\includegraphics[scale=0.4]{N_lens.pdf}
+\includegraphics[scale=0.4]{N_lens1.pdf}
 \caption{The marginal posterior distribution for $N_{\rm lens}$, the
@@
 and other such possibilities.
-\label{fig:N_lens}}
+\label{fig:N_lens1}}
 \end{center}
@@
 \begin{center}
-\includegraphics[scale=0.4]{substructures.pdf}
+\includegraphics[scale=0.4]{substructures1.pdf}
 \caption{The {\revisions `easy'} simulated data, with substructure positions overlaid (a
@@
 (where one was actually placed).
-\label{fig:substructures}}
+\label{fig:substructures1}}
 \end{center}
@@
 The joint posterior distribution for the SIE mass total substructure mass
-for the Cosmic Horseshoe is given in Figure~\ref{fig:masses2}. As with
-the simulated data (Figure~\ref{fig:masses}), we see an expected negative
+for the Cosmic Horseshoe is given in Figure~\ref{fig:masses3}. As with
+the simulated data (Figure~\ref{fig:masses1}), we see an expected negative
 correlation between these two quantities. However, the points are not as
@@
 The posterior distribution for
-$N_{\rm lens}$ (Figure~\ref{fig:N_lens2})
+$N_{\rm lens}$ (Figure~\ref{fig:N_lens3})
 also shows some evidence for more than zero substructures.
@@
 \begin{center}
-\includegraphics[scale=0.4]{masses2.pdf}
+\includegraphics[scale=0.4]{masses3.pdf}
 \caption{The joint posterior distribution for the SIE mass (integrated within
@@
 $H_0=70$ km/s/Mpc.
-\label{fig:masses2}}
+\label{fig:masses3}}
 \end{center}
@@
 \begin{center}
-\includegraphics[scale=0.4]{N_lens2.pdf}
+\includegraphics[scale=0.4]{N_lens3.pdf}
 \caption{The posterior distribution for the number of lens substructures
 in the Cosmic Horseshoe system. There is mild evidence in favour of the
-hypothesis that $N_{\rm lens} \neq 0$.\label{fig:N_lens2}}
+hypothesis that $N_{\rm lens} \neq 0$.\label{fig:N_lens3}}
 \end{center}
@@
 expected value of the empirical measure of substructure positions
-(Figure~\ref{fig:substructures2}) we find no consistency in their positions,
-unlike for the simulated data (Figure~\ref{fig:substructures}). This situation
+(Figure~\ref{fig:substructures3}) we find no consistency in their positions,
+unlike for the simulated data (Figure~\ref{fig:substructures1}). This situation
 is not uncommon. For example, \citet{exoplanet} found evidence for a large
@@
 \begin{center}
-\includegraphics[scale=0.4]{substructures2.pdf}
+\includegraphics[scale=0.4]{substructures3.pdf}
 \caption{The positions of substructures encountered in the MCMC sampling
@@
 posterior expected value of the empirical measure of substructure
-positions. Unlike Figure~\ref{fig:substructures}, for the Cosmic Horseshoe
+positions. Unlike Figure~\ref{fig:substructures1}, for the Cosmic Horseshoe
 there is little consistency in the positions of the substructures.
-\label{fig:substructures2}}
+\label{fig:substructures3}}
 \end{center}
@@
 Three example models (lens and source) sampled from the posterior are shown
-in Figure~\ref{fig:sources}.
+in Figure~\ref{fig:sources}. {\revisions
+The model was able to fit the data down to the noise level.
+}
 
@@
 results, the MCMC output should be treated with caution. For example, in
-Figure~\ref{fig:masses2}, there is a correlation between the mass attributed
+Figure~\ref{fig:masses3}, there is a correlation between the mass attributed
 to the SIE component and that attributed to substructures. However, the
@@
 algorithms such as parallel tempering). Despite this, the patchy
-nature of Figure~\ref{fig:masses2} suggests that posterior exploration is
+nature of Figure~\ref{fig:masses3} suggests that posterior exploration is
 still challenging in this problem.
 
-The results for the simulated data (Figure~\ref{fig:masses})
+The results for the simulated data (Figure~\ref{fig:masses1})
 were less complex because of the definite existence of one substructure.

### 2015-09-07 Papers/ms.tex
Results figures for the harder simulated data
caption work

@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{masses2.pdf}
+\caption{{\revisions
+Same as Figure~\ref{fig:masses1}, but for the `harder' simulated dataset.
+}
+\label{fig:masses2}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{N_lens2.pdf}
+\caption{{\revisions
+Same as Figure~\ref{fig:N_lens1}, but for the `harder' simulated dataset.
+}
+\label{fig:N_lens2}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{substructures2.pdf}
+\caption{{\revisions
+Same as Figure~\ref{fig:substructures1}, but for the `harder' simulated dataset.
+The true number of substructures was 10, which also happens to be the posterior
+mode. Only five substructures were located within the domain of the image, but
+$N_{\rm lens} = 10$ is probable because the spread-out positions of the
+m
+}
+\label{fig:substructures2}}
+\end{center}
+\end{figure}
+
 {\revisions
@@
 \includegraphics[scale=0.4]{masses3.pdf}
-\caption{The joint posterior distribution for the SIE mass (integrated within
+\caption{{\revisions Same as Figure~\ref{fig:masses1}, but for the Cosmic Horseshoe.} The joint posterior distribution for the SIE mass (integrated within
 its critical ellipse, which is not the critical curve of the lens overall),
@@
 \includegraphics[scale=0.4]{N_lens3.pdf}
-\caption{The posterior distribution for the number of lens substructures
+\caption{{\revisions Same as Figure~\ref{fig:N_lens1}, but for the Cosmic Horseshoe.} The posterior distribution for the number of lens substructures
 in the Cosmic Horseshoe system. There is mild evidence in favour of the
@@
 \includegraphics[scale=0.4]{substructures3.pdf}
-\caption{The positions of substructures encountered in the MCMC sampling
+\caption{{\revisions Same as Figure~\ref{fig:substructures1}, but for the Cosmic Horseshoe.} The positions of substructures encountered in the MCMC sampling
 for the Cosmic Horseshoe; technically a Monte Carlo approximation to the

### 2015-09-07 Papers/ms.tex
marginal likelihood and information

@@
 {\revisions
+The estimated marginal likelihood of our model, for the `harder' simulated data,
+is
+$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -5671.9$, and
+the information (Kullback-Leibler divergence from the prior to the posterior)
+is $\mathcal{H} \approx 155.7$ nats. 
 As with the easy dataset, the standardised residuals of the sampled models

### 2015-09-07 Papers/ms.tex
Run details

@@
 
+{\revisions As with the `easy' dataset,
+we generated 5,000 samples from the DNS target distribution and thinned
+by a factor of $10^5$, so $5 \times 10^8$ MCMC iterations were actually
+performed, taking approximately 60 hours. The slower runtime in this case
+was because $N_{\rm lens} = 10$, more CPU time was spent exploring parts of
+the hypothesis space where $N_{\rm lens}$ is high. The run resulted in 557
+equally-weighted posterior samples.
+}
+
 \begin{figure}

### 2015-09-07 Papers/ms.tex
More caption work

@@
 Same as Figure~\ref{fig:N_lens1}, but for the `harder' simulated dataset.
+The true number of substructures was 10, which also happens to be the posterior
+mode. Only five substructures were located within the domain of the image, but
+$N_{\rm lens} = 10$ is probable because the spread-out positions of the
+substructures imply that $R_{\rm lens}$ is probably large.
 }
@@
 Same as Figure~\ref{fig:substructures1}, but for the `harder' simulated dataset.
-The true number of substructures was 10, which also happens to be the posterior
-mode. Only five substructures were located within the domain of the image, but
-$N_{\rm lens} = 10$ is probable because the spread-out positions of the
-m
+For all of the substructures located close to the ring, the positions were well
+constrained. There was weak evidence for some substructures that did not in
+fact exist.
 }

### 2015-09-08 Papers/ms.tex
referee

@@
 It is a pleasure to thank Phil Marshall (Stanford), Tommaso Treu (UCLA),
-Ross Fadely (NYU), and Alan Heavens (Edinburgh)
+Ross Fadely (NYU), Alan Heavens (Edinburgh), {\revisions and the referee}
 for valuable discussion. Thomas Lumley (Auckland) also deserves credit for

### 2015-09-08 Papers/ms.tex
Huppenkothen reference updated
A bit more talking

@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{image2.pdf}
+\caption{{\revisions The `harder' simulated data, consisting of a more
+complex source profile, and a lens with an SIE+$\gamma$ (whose centre is
+indicated by a white circle) and ten substructures. Only five of the
+substructures (star symbols) occured within the square image boundary, but the other five still have an effect on the image.}
+\label{fig:image2}}
+\end{center}
+\end{figure}
+
 {\revisions As with the `easy' dataset,
@@
 the hypothesis space where $N_{\rm lens}$ is high. The run resulted in 557
-equally-weighted posterior samples.
+equally-weighted posterior samples. The posterior distribution for the SIE
+mass and the total substructure mass is given in Figure~\ref{fig:masses2}.
 }
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.5]{image2.pdf}
-\caption{{\revisions The `harder' simulated data, consisting of a more
-complex source profile, and a lens with an SIE+$\gamma$ (whose centre is
-indicated by a white circle) and ten substructures. Only five of the
-substructures (star symbols) occured within the square image boundary, but the other five still have an effect on the image.}
-\label{fig:image2}}
-\end{center}
-\end{figure}
 
@@
 \end{figure}
+
+{\revisions
+To demonstrate the claim that we can infer something about the mass function
+of substructures directly, we have plotted the posterior
+distribution for $\mu_{\rm lens}$, the hyperparameter for the substructure
+masses, in Figure~\ref{fig:mu_lens}.
+}
 
@@
 \bibitem[\protect\citeauthoryear{Huppenkothen et 
-al.}{2015}]{magnetron} Huppenkothen D., et al., 2015,
-accepted for publication in ApJ. arXiv:1501.05251
+al.}{2015}]{magnetron} Huppenkothen D., et al., 2015, ApJ, 810, 
+66
 

### 2015-09-09 display.py
Correct extent

@@ -132,13 +132,11 @@ savefig('N_lens.pdf', bbox_inches='tight')
 show()
 
 figure(4, figsize=(8, 8))
-imshow(data, interpolation="nearest", cmap="Oranges")
+imshow(data, extent=metadata[2:6], interpolation="nearest", cmap="Oranges")
 hold(True)
 plot(all_substructures_x, all_substructures_y, 'k.', markersize=3)
 gca().set_xticks([])
 gca().set_yticks([])
-xlim([-0.5, metadata[1] - 0.5])
-ylim([metadata[0] - 0.5, -0.5])
 title('Substructure Positions')
 savefig('substructures.pdf', bbox_inches='tight')
 show()

### 2015-09-09 lens_plots.jl
fixes

@@ -8,7 +8,6 @@ include("Lenses/BlobbyNIE.jl")
 posterior_sample = readdlm("posterior_sample.txt")
 metadata = readdlm("Data/mock_metadata.txt")
 
-
 plt.figure(figsize=(5, 6))
 for(which in 1:3)
 	# Size of the 2D array
@@ -37,13 +36,11 @@ for(which in 1:3)
 		return mag
 	end
 
-	x = linspace(-10,  10, 3001)
-	y = linspace( 10, -10, 3001)
-	mag = magnification_image(posterior_sample[which, :], x, y)
-
+	x = linspace(-10,  10, 1001)
+	y = linspace( 10, -10, 1001)
+#	mag = magnification_image(posterior_sample[which, :], x, y)
 #	plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
 #						vmin=-5.0, vmax=5.0, cmap="coolwarm")
-
 
 	params = posterior_sample[which, :]
 	x_substructures = params[20:29]
@@ -51,14 +48,7 @@ for(which in 1:3)
 	m_substructures = params[40:49]
 	x_substructures = x_substructures[m_substructures .!= 0.]
 	y_substructures = y_substructures[m_substructures .!= 0.]
-
-#	# Convert x and y to pixel coordinates for overplotting
-	dx = (metadata[4] - metadata[3])/metadata[2]
-	dy = (metadata[6] - metadata[5])/metadata[1]
-	x_substructures = (x_substructures - metadata[3])/dx - 0.5
-	y_substructures = (metadata[6] - y_substructures)/dy - 0.5
-	x_nie = params[6]#(params[6] - metadata[3])/dx - 0.5
-	y_nie = params[7]#(metadata[6] - params[7])/dy - 0.5
+	x_nie, y_nie = params[6], params[7]
 
 	rays = zeros(100000, 4)
 	n_rays = 0
@@ -87,31 +77,31 @@ for(which in 1:3)
 
 	rays = rays[1:n_rays, :]
 
-#	plt.hold(true)
-#	plt.plot(rays[:,1], rays[:,2], "w.", markersize=1)
-#	plt.plot(rays[:,3], rays[:,4], "b.", markersize=1)
-#	plt.axis([-10.0, 10.0, -10.0, 10.0])
-#	writedlm("rays.txt", rays)
-#	plt.show()
+##	plt.hold(true)
[…]

### 2015-09-09 Papers/ms.tex
Include the mu_lens figure
new numbers

@@
 \begin{figure}
+\centering
+\includegraphics[scale=0.45]{mu_lens.pdf}
+\caption{{\revisions The posterior distribution for $\mu_{\rm lens}$, the
+hyperparameter which determines the prior expected value of substructure
+masses, given the `harder' simulated data. The true value (in arbitrary units)
+was 1, which is indicated by the vertical line.
+}
+\label{fig:mu_lens}}
+\end{figure}
+
+\begin{figure}
 \begin{center}
@@
 by a factor of $10^5$, so $5 \times 10^8$ MCMC iterations were actually
-performed, taking approximately 40 hours. The first 1/3 of the run was
-excluded as burn-in. After resampling, this resulted in 632
+performed, taking approximately 40 hours. After resampling, this resulted in
+{\revisions 718}
 equally weighted posterior samples. Although this image is smaller than the
@@
 The estimated marginal likelihood of our model
-is
-$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -6967$, and
+is {\revisions
+$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -6948.5$}, and
 the information (Kullback-Leibler divergence from the prior to the posterior)
-is $\mathcal{H} \approx 129$ nats. 
+is {\revisions $\mathcal{H} \approx 123.1$} nats. 
 Three example models (lens and source) sampled from the posterior are shown
@@
 of the time sampling the prior. Therefore, a particle exploring the parameter
-space can ``forget'' its good fitting position, move somewhere completely
-different, and find another good fitting model in a different location. This
+space can ``forget'' its good-fitting position, move somewhere completely
+different, and find another good-fitting model in a different location. This
 is a natural feature of the algorithm (and is also present in related

### 2015-09-09 Papers/ms.tex
More updated numbers

@@
 8 threads.}. After resampling these samples to
-reflect the posterior distribution, we were left with 537
+reflect the posterior distribution, we were left with {\revisions 500}
 (equally weighted) posterior samples.
@@
 (averaged over all parameters including $N_{\rm lens}$ and $N_{\rm src}$)
-is
-$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -14248$, and
+is {\revisions
+$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -14141.4$, and
 the information (Kullback-Leibler divergence from the prior to the posterior)
-is $\mathcal{H} \approx 99$ nats. The information represents the degree of
+is $\mathcal{H} \approx 99.4$ nats}. The information represents the degree of
 compression of the posterior distribution with respect to the prior, and can

### 2015-09-09 Lenses/BlobbyNIE.jl
Function to make a map of the density

@@ -96,6 +96,31 @@ function magnification(parameters::Array{Float64, 2}, x::Float64, y::Float64, h:
 	return -2.5*log10(abs(jacobian(parameters, x, y, h)))
 end
 
+function density(parameters::Array{Float64, 2},
+					x_min, x_max, y_min, y_max; n=1001)
+	assert(size(parameters)[1] == 1)
+
+	x = linspace(x_min, x_max, n)
+	y = linspace(y_max, y_min, n)
+	f = zeros(n, n)
+
+	for(k in 1:parameters[19])
+		xc, yc, mass, width = parameters[19+k], parameters[29+k], parameters[39+k], parameters[49+k]
+		widthsq = width^2
+		C = mass*2.0/pi/widthsq
+
+		for(j in 1:n)
+			for(i in 1:n)
+				rsq = (x[i] - xc)^2 + (y[j] - yc)^2
+				if(rsq <= widthsq)
+					f[i, j] += C*(1.0 - rsq/widthsq)
+				end
+			end
+		end
+	end
+
+	return f
+end
 
 # Input: parameters of a blob (length four)
 function blob_mass_within(parameters::Array{Float64, 2},
@@ -123,4 +148,5 @@ end
 params = zeros(1, 4)
 params[1], params[2], params[3], params[4] = 0.0, 0.0, 1.0, 0.5
 println(blob_mass_within(params, -0.5, 0.5, -0.5, 0.5))
+
 

### 2015-09-09 lens_plots.jl
Density in second column

@@ -8,7 +8,7 @@ include("Lenses/BlobbyNIE.jl")
 posterior_sample = readdlm("posterior_sample.txt")
 metadata = readdlm("Data/mock_metadata.txt")
 
-plt.figure(figsize=(5, 6))
+plt.figure(figsize=(8, 10))
 for(which in 1:3)
 	# Size of the 2D array
 	M = size(posterior_sample)[1]
@@ -36,8 +36,8 @@ for(which in 1:3)
 		return mag
 	end
 
-	x = linspace(-10,  10, 1001)
-	y = linspace( 10, -10, 1001)
+	x = linspace(metadata[3], metadata[4], 1001)
+	y = linspace(metadata[5], metadata[6], 1001)
 #	mag = magnification_image(posterior_sample[which, :], x, y)
 #	plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
 #						vmin=-5.0, vmax=5.0, cmap="coolwarm")
@@ -50,32 +50,32 @@ for(which in 1:3)
 	y_substructures = y_substructures[m_substructures .!= 0.]
 	x_nie, y_nie = params[6], params[7]
 
-	rays = zeros(100000, 4)
-	n_rays = 0
-	for(j in 1:length(x))
-		for(i in 1:(length(y)-1))
-			f1 = jacobian(params, x[j], y[i])
-			f2 = jacobian(params, x[j], y[i+1])
-			if(sign(f1) != sign(f2))
-				(xs, ys) = fire_ray(params, x[j], y[i])
-				rays[n_rays+1, :] = [[x[j], y[i], xs, ys]]
-				n_rays += 1
-			end
-		end
-	end
-	for(i in 1:length(y))
-		for(j in 1:(length(x)-1))
-			f1 = jacobian(params, x[j], y[i])
-			f2 = jacobian(params, x[j+1], y[i])
-			if(sign(f1) != sign(f2))
-				(xs, ys) = fire_ray(params, x[j], y[i])
-				rays[n_rays+1, :] = [[x[j], y[i], xs, ys]]
-				n_rays += 1
-			end
-		end
-	end
+#	rays = zeros(100000, 4)
+#	n_rays = 0
+#	for(j in 1:length(x))
+#		for(i in 1:(length(y)-1))
+#			f1 = jacobian(params, x[j], y[i])
+#			f2 = jacobian(params, x[j], y[i+1])
[…]

### 2015-09-09 lens_plots.jl
comment out liens

@@ -36,8 +36,8 @@ for(which in 1:3)
 		return mag
 	end
 
-	x = linspace(metadata[3], metadata[4], 1001)
-	y = linspace(metadata[5], metadata[6], 1001)
+#	x = linspace(metadata[3], metadata[4], 1001)
+#	y = linspace(metadata[5], metadata[6], 1001)
 #	mag = magnification_image(posterior_sample[which, :], x, y)
 #	plt.imshow(mag, interpolation="nearest", extent=[-10, 10, -10, 10],
 #						vmin=-5.0, vmax=5.0, cmap="coolwarm")

### 2015-09-09 Lenses/BlobbyNIE.jl
Fixed minor bugs

@@ -111,7 +111,7 @@ function density(parameters::Array{Float64, 2},
 
 		for(j in 1:n)
 			for(i in 1:n)
-				rsq = (x[i] - xc)^2 + (y[j] - yc)^2
+				rsq = (x[j] - xc)^2 + (y[i] - yc)^2
 				if(rsq <= widthsq)
 					f[i, j] += C*(1.0 - rsq/widthsq)
 				end
@@ -135,7 +135,7 @@ function blob_mass_within(parameters::Array{Float64, 2},
 	f = zeros(n, n)
 	for(j in 1:n)
 		for(i in 1:n)
-			rsq = (x[i] - xc)^2 + (y[j] - yc)^2
+			rsq = (x[j] - xc)^2 + (y[i] - yc)^2
 			if(rsq <= widthsq)
 				f[i, j] += C*(1.0 - rsq/widthsq)
 			end

### 2015-09-09 Papers/ms.tex

@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
 \includegraphics[scale=0.8]{sources.pdf}
-\caption{Three example sources (and the corresponding lensed, blurred images)
-representative of the posterior distribution. All three lens system scenarios
-have substructures, which cause subtle distortions from the usual shape of
-the caustics and critical curves (plotted as black curves).
-The angular scales are 3 arcseconds for the sources and 15
+\caption{Three example sources, the density profile in substructures,
+and the corresponding lensed, blurred images,
+representative of the posterior distribution.
+The angular scales are 7.5 arcseconds for the sources and 15
 arcseconds for the images.
@@
 \end{center}
-\end{figure}
+\end{figure*}
 

### 2015-09-09 lens_plots.jl
Less vertical space

@@ -8,7 +8,7 @@ include("Lenses/BlobbyNIE.jl")
 posterior_sample = readdlm("posterior_sample.txt")
 metadata = readdlm("Data/mock_metadata.txt")
 
-plt.figure(figsize=(8, 10))
+plt.figure(figsize=(8, 8))
 for(which in 1:3)
 	# Size of the 2D array
 	M = size(posterior_sample)[1]

### 2015-09-10 Papers/ms.tex
Updated some numbers and fixed marginal likelihood notation

@@
 is {\revisions
-$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -14141.4$, and
+$\ln\left[p(\boldsymbol{D})\right] \approx -14141.4$, and
 the information (Kullback-Leibler divergence from the prior to the posterior)
@@
 is
-$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -5671.9$, and
+$\ln\left[p(\boldsymbol{D})\right] \approx -5671.9$, and
 the information (Kullback-Leibler divergence from the prior to the posterior)
@@
 in Section~\ref{sec:convergence}). An upper ``limit'' on the SIE mass, with
-95\% posterior probability, is $5.21 \times 10^{12}$ solar masses.
+95\% posterior probability, is $5.20 \times 10^{12}$ solar masses.
 The algorithm has also found
@@
 In particular, the prior probability for $N_{\rm lens} > 0$ was 10/11
-$\approx$ 0.91, whereas the posterior probability is approximately 0.97.
-This corresponds to a Bayes Factor of approximately 3 in favour of
+$\approx$ 0.91, whereas the posterior probability is approximately {\revisions 0.997}.
+This corresponds to a Bayes Factor of {\revisions about 300} in favour of
 $N_{\rm lens} > 0$ versus the alternative $N_{\rm lens} = 0$.
@@
 \caption{{\revisions Same as Figure~\ref{fig:N_lens1}, but for the Cosmic Horseshoe.} The posterior distribution for the number of lens substructures
-in the Cosmic Horseshoe system. There is mild evidence in favour of the
-hypothesis that $N_{\rm lens} \neq 0$.\label{fig:N_lens3}}
+in the Cosmic Horseshoe system. There is {\revisions moderate} evidence in favour of the hypothesis that $N_{\rm lens} \neq 0$.\label{fig:N_lens3}}
 \end{center}
@@
 is {\revisions
-$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -6948.5$}, and
+$\ln\left[p(\boldsymbol{D})\right] \approx -6948.5$}, and
 the information (Kullback-Leibler divergence from the prior to the posterior)
@@
 true. We then applied the method to an image of the Cosmic Horseshoe system
-and found mild evidence in favour of the existence of a substructure, or at
+and found {\revisions moderate} evidence in favour of the existence of a substructure, or at
 the very least, a departure from a simple SIE+$\gamma$ lens profile. The

### 2015-09-10 Papers/ms.tex
More number updates

@@
 masses.
-With 95\% probability the substructure mass is less than 5.80$\times 10^{12}$ solar masses and with 75\% probability it is less than 3.56$\times 10^{12}$ solar masses.
+With 95\% probability the substructure mass is less than {\revisions 1.53$\times 10^{13}$} solar masses and with 75\% probability it is less than {\revisions 5.10$\times 10^{12}$} solar masses.
 As the Einstein ring itself implies a mass of about $5 \times 10^{12}$

### 2015-09-10 MyModel2.cpp
ALways reshoot rays if lens changed

@@ -68,13 +68,7 @@ double MyModel2::perturb()
 	{
 		logH += lens.perturb();
 
-		if(lens.get_blobs_flag() &&
-			(lens.get_size_of_diff() < lens.get_num_components())
-			&& staleness2 < 10)
-			update_rays();
-		else
-			shoot_rays();
-
+		shoot_rays();
 		calculate_surface_brightness();
 		calculate_model_image();
 	}

### 2015-09-10 MyModel2.cpp
Output the unblurred image inMyModel2

@@ -114,6 +114,10 @@ void MyModel2::print(std::ostream& out) const
 		for(size_t j=0; j<xs[i].size(); j++)
 			out<<source.evaluate(x[i][j], y[i][j])<<' ';
 
+	for(size_t i=0; i<xs.size(); i++)
+		for(size_t j=0; j<xs[i].size(); j++)
+			out<<surface_brightness[i][j]<<' ';
+
 	for(size_t i=0; i<model_image.size(); i++)
 		for(size_t j=0; j<model_image[i].size(); j++)
 			out<<model_image[i][j]<<' ';

### 2015-09-11 display.py
Extent fixes

@@ -58,10 +58,12 @@ for i in xrange(0, output.shape[0]):
 	subplot(2,3,1)
 	imshow(src, extent=metadata[2:6], interpolation='nearest', cmap='Oranges')
 	title('Model Source ' + str(i+1))
+	axis(metadata[2:6])
 
 	subplot(2,3,2)
 	imshow(img1, extent=metadata[2:6], interpolation='nearest', cmap='Oranges')
 	title('Unblurred Image ' + str(i+1))
+	axis(metadata[2:6])
 
 	subplot(2,3,3)
 	imshow(img2, extent=metadata[2:6], interpolation='nearest', cmap='Oranges')
@@ -72,15 +74,18 @@ for i in xrange(0, output.shape[0]):
 	plot(x_substructures, y_substructures, 'g*', markersize=15, alpha=0.5)
 	title('Model Image ' + str(i+1))
 	hold(False)
+	axis(metadata[2:6])
 
 	subplot(2,2,3)
-	imshow(data, interpolation='nearest', cmap='Oranges')
+	imshow(data, extent=metadata[2:6], interpolation='nearest', cmap='Oranges')
 	title('Data')
+	axis(metadata[2:6])
 
 	subplot(2,2,4)
 	sigma = sqrt(sig**2 + x[0]**2 + x[1]*img2)
-	imshow((img2 - data)/sigma, interpolation='nearest', cmap='Oranges')
+	imshow((img2 - data)/sigma, extent=metadata[2:6], interpolation='nearest', cmap='Oranges')
 	title('Standardised Residuals')
+	axis(metadata[2:6])
 	draw()
 
 	if saveFrames:

### 2015-09-11 Papers/ms.tex
SPH
More honest abstract

@@
 apply the method to the g-band
-image of the ``Cosmic Horseshoe'' system, and find some
-hints of potential substructures. However, we caution that such results could
-also be caused by misspecifications in the model (such as the shape of
+image of the ``Cosmic Horseshoe'' system, and find {\revisions evidence for more
+than zero substructures}. However, {\revisions these have large spatial
+extent and probably only point to misspecifications in the model}
+(such as the shape of
 the smooth lens component or the point spread function),
@@
 each blob will evaluate to zero over a large fraction of the domain which
-confers an additional speed advantage.
+confers an additional speed advantage. {\revisions More conventional choices such as
+gaussians are possible, as are alternative compact basis functions, perhaps
+inspired by the smoothed particle hydrodynamics literature
+\citep{2012MNRAS.425.1068D}.}
 
@@
 
+{\revisions
+\bibitem[\protect\citeauthoryear{Dehnen 
+\& Aly}{2012}]{2012MNRAS.425.1068D} Dehnen W., Aly H., 2012, MNRAS, 425, 1068
+}
+
 \bibitem[\protect\citeauthoryear{Dye et al.}{2008}]{2008MNRAS.388..384D} 

### 2015-09-11 Papers/ms.tex
Editing in the introduction

@@
 
-We have developed an approach for solving this same problem (inferring the
+{\revisions In this paper, we introduce} an approach for solving this same problem (inferring the
 number and properties of dark substructures given an image) in a more direct
-fashion. However, with appropriate modifications, it may also prove useful in other
+fashion, {\revisions by fitting a model with an unknown number of substructures directly to the image data.}
+However, with appropriate modifications, it may also prove useful in other
 galaxy-galaxy lens modelling areas. One example is time-delay cosmography, which
@@
 moderately flexible \citep[e.g. a mixture model,][]{2011MNRAS.412.2521B}
-or free-form (e.g. pixellated) model for the surface brightness profile of the source;\\
+or free-form (e.g. pixellated) model for the surface brightness profile of the source;
 \item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid
-[SIE]) or flexible model (e.g. pixellated) for the mass profile of the lens; and\\
+[SIE]) or flexible model (e.g. pixellated) for the mass profile of the lens; and
 \item How to compute the results (e.g. optimization methods, Markov Chain

### 2015-09-11 Papers/ms.tex
Comment about another level of hierarchy
More words about the posterior for mu_lens

@@
 \citep{2015arXiv150507840A, 2015ApJ...807...87S, pancoast}.
+{\revisions Here, we are referring to
+the mass function of the substructures within a single lens galaxy. An
+additional level of hierarchy would be needed to answer questions about a
+sample of lens galaxies}.
 
@@
 To demonstrate the claim that we can infer something about the mass function
-of substructures directly, we have plotted the posterior
+of substructures directly from the image data, we have plotted the posterior
 distribution for $\mu_{\rm lens}$, the hyperparameter for the substructure
-masses, in Figure~\ref{fig:mu_lens}.
+masses, in Figure~\ref{fig:mu_lens}. The true value was 1, and the
+posterior distribution indicates a fairly wide uncertainty range that is
+at least consistent with the true value in some sense. Given that the image
+only contained a few substructures whose masses could be measured with any
+accuracy, the large uncertainty is not surprising.
 }

### 2015-09-12 Papers/ms.tex
Youtube
First half of GFL's comments

@@
 locations suggested by the correction term. This kind of inference has also
-been done with point-like multiple images of QSOs \citep{2012MNRAS.419..936F}.
+been done with point-like multiple images of {\revisions quasars} \citep{2012MNRAS.419..936F}.
 
@@
 pixellated models, which is also a motivation behind
-\citet{2015arXiv150500198T}'s investigation of shapelets.
+{\revisions the investigation of
+shapelets by \citet{2015arXiv150500198T}}.
 One way of achieving this is with mixture models.
@@
 \end{eqnarray}
-
 The dimensionality of the parameter space for the source depends on the
@@
 \end{eqnarray}
-where $r=\sqrt{x^2 + y^2}$. These do not depend on any slow functions such
+where $r=\sqrt{x^2 + y^2}$. These do not depend on any
+{\revisions computationally expensive} functions such
 as square roots or exponentials.
@@
 The {\tt RJObject} library uses the
-Diffusive Nested Sampling algorithm \citep[DNS][]{dnest} for its sampling, but the
+Diffusive Nested Sampling algorithm \citep[DNS;][]{dnest} for its sampling, but the
 trans-dimensionality is handled by the MCMC moves. Therefore, the marginal
@@
 mass and the total substructure mass is given in Figure~\ref{fig:masses2}.
+The samples can be viewed as a movie at
+{\tt www.youtube.com/watch?v=o3ppfKSk248}.
 }

### 2015-09-12 Papers/ms.tex
Last GFL comment

@@
 {\revisions
-The SIE$+\gamma$ parameters were
+The SIE$+\gamma$ parameters were, {\revisions to three significant figures},
 $\{b, q, x_c^{\rm SIE}, y_c^{\rm SIE}, \theta, \gamma, \theta_\gamma\}

### 2015-10-09 Papers/ms.tex
Paragraph about sersic profiles etc

@@
 % For revisions
-\newcommand{\revisions}{\color{blue}}
+\newcommand{\revisions}{}
+\newcommand{\revisionstwo}{\color{blue}}
 
@@
 inspired by the smoothed particle hydrodynamics literature
-\citep{2012MNRAS.425.1068D}.}
+\citep{2012MNRAS.425.1068D}.} {\revisionstwo Alternative choices, such as Sérsic
+profiles, may be more realistic despite their computational cost. This is
+especially likely in the case of an early-type source galaxy
+\citep[e.g.][]{eels}. Such modifications are possible without great effort
+using the {\tt RJObject} library, and once implemented, the marginal likelihood
+can be compared across different choices for the source model.}
 
@@
 
+\bibitem[\protect\citeauthoryear{Auger et al.}{2011}]{eels} 
+Auger M.~W., Treu T., Brewer B.~J., Marshall P.~J., 2011, MNRAS, 411, L6
+
 \bibitem[\protect\citeauthoryear{Belokurov et 

### 2015-10-09 Papers/ms.tex
mention fastell
Turn off revisionstwo and remove revisions stuff from abstract in preparation for arxiv submission

@@
 \newcommand{\revisions}{}
-\newcommand{\revisionstwo}{\color{blue}}
+\newcommand{\revisionstwo}{}
 
@@
 number of blobs in the source and the lens.
-We demonstrate the method on {\revisions two
+We demonstrate the method on two
 simulated data sets: one with a single
-substructure, and one with ten}. We also
+substructure, and one with ten. We also
 apply the method to the g-band
-image of the ``Cosmic Horseshoe'' system, and find {\revisions evidence for more
-than zero substructures}. However, {\revisions these have large spatial
-extent and probably only point to misspecifications in the model}
+image of the ``Cosmic Horseshoe'' system, and find evidence for more
+than zero substructures. However, these have large spatial
+extent and probably only point to misspecifications in the model
 (such as the shape of
@@
 simplicity comes a lack of realism, and generalising the smooth lens model
-is an important future step. Ultimately, concentric
+is an important future step. {\revisionstwo The softened power law elliptical
+mass density or SPEMD model is a popular generalization of the SIE where the
+deflection angles can still be computed quickly using the approximations given
+by \citet{fastell}.}
+
+Ultimately, concentric
 mixtures of smooth components may be the most useful for realistic inference
@@
 
+\bibitem[\protect\citeauthoryear{Barkana}{1998}]{fastell} 
+Barkana R., 1998, ApJ, 502, 531
+
 \bibitem[\protect\citeauthoryear{Auger et al.}{2011}]{eels} 

### 2015-11-29 Papers/Paper2/ms.tex
Placeholder paper 2

--- 2015-09-12 Papers/ms.tex
@@
 % For revisions
-\newcommand{\revisions}{\color{blue}}
+\newcommand{\revisions}{}
+\newcommand{\revisionstwo}{}
 
 \title[]
-{Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures}
+{The mass of the substructure in the ``Jackpot'' Gravitational Lens}
 
@@
 \begin{abstract}
-We introduce a Bayesian solution to the problem of inferring the density
-profile of strong gravitational lenses when the lens galaxy may contain
-multiple dark or faint substructures. The source and lens models are based on
-a superposition of an unknown number of non-negative basis functions
-(or ``blobs'') whose form was chosen with speed as a primary criterion.
-The prior distribution for the blobs' properties is specified hierarchically,
-so the mass function of substructures is a natural output of the method.
-We use reversible
-jump Markov Chain Monte Carlo (MCMC) within Diffusive Nested Sampling (DNS) to
-sample the posterior distribution and evaluate the marginal likelihood of the
-model, including the summation over the unknown
-number of blobs in the source and the lens.
-We demonstrate the method on {\revisions two
-simulated data sets: one with a single
-substructure, and one with ten}. We also
-apply the method to the g-band
-image of the ``Cosmic Horseshoe'' system, and find {\revisions evidence for more
-than zero substructures}. However, {\revisions these have large spatial
-extent and probably only point to misspecifications in the model}
-(such as the shape of
-the smooth lens component or the point spread function),
-which are difficult to guard against in full generality.
+
 \end{abstract}
@@
 \section{Introduction}
-Galaxy-galaxy gravitational lensing is a powerful astrophysical tool for studying
-the distribution of matter, including dark matter, in galaxies
-\citep{treu}. One promising application of lensing is to study
-and measure the properties of dark matter substructures in the lens
-galaxy \citep{koopmans}.
-In recent years, this promise has been realised in several lens systems
-which are thought to contain at least one dark substructure
-\citep{vegetti1, vegetti2, vegetti3}. In these studies, the lens was modelled
-as a superposition of a smooth component (such as an elliptical power-law
-matter distribution) plus a pixellized ``non-parametric'' correction term.
-The estimated spatial structure of the correction term provides clues about
-the locations of possible substructures. In a second modelling step, the lens
-is assumed to be a smooth overall component plus a compact ``blob'' near any
-locations suggested by the correction term. This kind of inference has also
-been done with point-like multiple images of {\revisions quasars} \citep{2012MNRAS.419..936F}.
-
-{\revisions In this paper, we introduce} an approach for solving this same problem (inferring the
-number and properties of dark substructures given an image) in a more direct
-fashion, {\revisions by fitting a model with an unknown number of substructures directly to the image data.}
-However, with appropriate modifications, it may also prove useful in other
-galaxy-galaxy lens modelling areas. One example is time-delay cosmography, which
-requires realistically flexible lens models, and reliable quantification
-of the uncertainties
-\citep{2013ApJ...766...70S, 2014ApJ...788L..35S, grillo}.
-
-Lens modelling has been a topic of much interest over the last two decades.
-Most approaches are based on Bayesian inference \citep{sivia, ohagan}, maximum
-likelihood \citep{millar} or
-variations thereof. These approaches may be categorized according to the
-following criteria:
-\begin{enumerate}
-\item Whether to use a simply parameterized (e.g. a Sérsic profile),
-moderately flexible \citep[e.g. a mixture model,][]{2011MNRAS.412.2521B}
-or free-form (e.g. pixellated) model for the surface brightness profile of the source;
-\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid
-[SIE]) or flexible model (e.g. pixellated) for the mass profile of the lens; and
-\item How to compute the results (e.g. optimization methods, Markov Chain
-Monte Carlo [MCMC] with source parameters marginalized out analytically, or
-MCMC with the source parameters included).
-\end{enumerate}
-Recent sophisicated approaches investigating different prior assumptions
-and computational approaches include \citet{2014MNRAS.445.2181C},
-\citet{2015arXiv150500198T}, and
-\citet{2015arXiv150407629B}.
-
-Each approach involves tradeoffs between convenience and realism.
-Simply parameterized models, such as Sérsic surface
-brightness profiles for the source,
-and singular isothermal ellipsoid plus
-external shear (SIE+$\gamma$) models for the lens \citep{1994A&A...284..285K},
-are very
-convenient. They only have a few adjustable parameters, and they capture
-(to ``first order'') relevant prior information that we have about the
-source and lens profiles. Of course, they are clearly simplifications,
-and can produce misleading results if the actual profile is very different
-from any member of the assumed family.
-
-On the
-other hand, pixellated models for the source \citep[e.g.][]{suyu} or the lens
-\citep[e.g.][]{2014MNRAS.445.2181C} can in principle represent ``any''
-source surface brightness profile or lens projected density profile. However, the prior
-distribution over pixel values is often chosen to be a multivariate gaussian
-for mathematical reasons, so
-that the source can be analytically marginalized out
-\citep{2003ApJ...590..673W}. Unfortunately, a multivariate gaussian prior
-over pixel intensities usually corresponds to a poor model of our prior
-beliefs about the source. It assigns virtually zero prior probability
-to the hypothesis that the source actually looks like a galaxy, and very high
-prior probability to the hypothesis that the source looks like noise (or
-blurred noise). These priors also assign nonzero probability to negative
-surface brightness or density values; in fact, the marginal prior probability
-that any pixel is negative is typically 0.5.
-
-\citet{2011MNRAS.412.2521B} argued that an ideal
-modelling approach lies somewhere between simply-parameterised and
-pixellated models, which is also a motivation behind
-{\revisions the investigation of
-shapelets by \citet{2015arXiv150500198T}}.
-One way of achieving this is with mixture models.
-The source and the lens can be built up from a mixture of a moderate
-number (from a few to a few hundred) of
-simply parameterised components. For the source, this allows
-us to incorporate prior knowledge about the local correlations (the surface
-brightness at any particular point is likely to be similar to that at a
-nearby point) and the fact that most of the sky is
-dark \citep{2006ApJ...637..608B}. The \citet{2011MNRAS.412.2521B} model also
-allowed for multi-band data, and allowed for our expectation that the image
-may or may not be similar in different bands.
-
-The present paper is similar in approach to \citet{2011MNRAS.412.2521B}.
-The main differences are:
-i) we use a simpler and faster set of basis functions;
-ii) we apply it to the lens as well as the source, allowing for the
-possibility of substructure; and
-iii) the implementation is based on a C++ template library developed by
-\citet{rjobject} which allows for hierarchical priors and trans-dimensional
-MCMC to be implemented in a relatively straightforward manner.
-However, in the present paper we do not account for
-multi-band data; this will be reserved for a future contribution.
-The source code for this project is available at
-{\tt http://www.github.com/eggplantbren/Lensing2}.
-
-If we are interested in detecting and measuring the properties of
-possible dark substructures in a lens galaxy,
-a superposition of an unknown number of ``blobs'' is the
-most natural model. In addition, if we want to constrain the mass function of
-these blobs \citep[e.g.][]{2009MNRAS.400.1583V, 2014MNRAS.442.2017V},
-we will need a hierarchical model which specifies the prior probability
-distribution for the masses conditional on some hyperparameters. Inferring the
-mass function of the blobs then reduces to calculating the posterior
-distribution for the hyperparameters. This is related to the general principle
-that we should (ideally) construct our inference methods so that the
-quantities we infer directly answer our scientific questions
-\citep{2015arXiv150507840A, 2015ApJ...807...87S, pancoast}.
-{\revisions Here, we are referring to
-the mass function of the substructures within a single lens galaxy. An
-additional level of hierarchy would be needed to answer questions about a
-sample of lens galaxies}.
-
-\section{The Model}
-We now describe the details of our model and its parameterization. The
-motivation for most of our modelling choices is a compromise between
-computational efficiency, realism, and ease of implementation. None of the
-choices we have made are final in any sense; rather, this model should be
-considered a proof of concept. We encourage exploration of
-other choices. Since we can compute marginal likelihoods, Bayesian model
-comparison between our choices here and any proposed alternatives should be
-straightforward, if a union of our hypothesis space and another
-can be considered a reasonable model of prior uncertainty.
-
-\subsection{The Source}
-The surface brightness profile of the source is assumed to be composed of
-a sum of a finite number of ``blobs'', or basis functions, in order to
-allow some flexibility while incorporating prior information about the
-non-negativity of surface brightness, and the spatial correlation expected
-in real surface brightness profiles.
-For computational speed, we choose the following
-functional form for the surface brightness profile
-of a single blob centered at the origin:
-\begin{eqnarray}
-f(x, y) &=& \left\{
-\begin{array}{lr}
-\frac{2A}{\pi w^2}\left(1 - \frac{r^2}{w^2}\right), & r \leq w\\
-0, & \textnormal{otherwise}
-\end{array}
-\right.
-\end{eqnarray}
-where $r = \sqrt{x^2 + y^2}$, $w$ is the width of the blob, and $A$ is the
-total flux of the blob (i.e. the integral of the surface brightness over the
-entire domain).
-These basis functions are inverted paraboloids, which are faster to evaluate
-than gaussians, since they do not
-contain an exponential function. In addition, the finite support means that
-each blob will evaluate to zero over a large fraction of the domain which
-confers an additional speed advantage. {\revisions More conventional choices such as
-gaussians are possible, as are alternative compact basis functions, perhaps
-inspired by the smoothed particle hydrodynamics literature
-\citep{2012MNRAS.425.1068D}.}
-
-If our model contains $N_{\rm src}$ such blobs, positioned at
-$\left\{(x_i^{\rm src}, y_i^{\rm src})\right\}$ with widths $\{w_i\}$ and total fluxes
-$\{A_i\}$, the overall surface brightness profile is:
-\begin{eqnarray}
-f(x, y) &=& \sum_{i=1}^{N_{\rm src}}\left\{
-\begin{array}{lr}
-\frac{2A_i}{\pi w_i^2}\left(1 - \frac{r_i^2}{w_i^2}\right), & r_i \leq w_i\\
-0, & \textnormal{otherwise}
-\end{array}
-\right.
-\end{eqnarray}
-where $r_i = \sqrt{(x - x_i^{\rm src})^2 + (y - y_i^{\rm src})^2}$.
-Under these assumptions, the source can be described in its entirety
-by the following parameters:
-\begin{eqnarray}
-\left\{
-N_{\rm src}, \left\{\boldsymbol{\theta}^{\rm src}_i\right\}_{i=1}^N
-\right\}
-\end{eqnarray}
-where $\boldsymbol{\theta}^{\rm src}_i$ denotes the parameters for source blob $i$:
-\begin{eqnarray}
-\boldsymbol{\theta}^{\rm src}_i &=& \left\{x_i, y_i, A_i, w_i
-\right\}.
-\end{eqnarray}
-The dimensionality of the parameter space for the source depends on the
-minimum and maximum values of $N_{\rm src}$, which we set to 0 and 100
-respectively (more detail about priors is given in Section~\ref{sec:priors}).
-Therefore the source is described by 1 -- 401 parameters.
-
-\subsection{The Lens}
-The surface mass density profile of the lens is modelled as a superposition
-of a singular isothermal ellipsoid plus external shear (SIE+$\gamma$) and
-$N$ circular lens ``blobs''. The SIE+$\gamma$ is a simple and widely used lens
-model with analytically available deflection angles, and is intended to account
-for the bulk of the lensing effect due to the smooth spatial distribution
-of (visible and dark) matter in the lens galaxy. Unfortunately, along with
-simplicity comes a lack of realism, and generalising the smooth lens model
-is an important future step. Ultimately, concentric
-mixtures of smooth components may be the most useful for realistic inference
-of the density profile of the halo. A common approach in the lensing
-community, that is similar in spirit, is a superposition of an elliptical
-power law, external shear, and a pixellated potential correction. However, the
-direct use of blobs is closer to the scientific question at hand
-when investigating postential dark substructures.
-
-The SIE+$\gamma$ has nine free parameters:
-the (circularized) Einstein radius $b$, axis ratio $q$, central position
-$(x_c, y_c)$, orientation angle $\theta$, the external shear $\gamma$, and the
-orientation angle of the external shear, $\theta_{\gamma}$.
-
-The $N$ lens blobs are intended to model possible dark or faint substructures
-in the projected mass profile of the lens.
-A lensing blob with mass $M$ and width $v$
-centered at the origin has the following surface mass density profile:
-\begin{eqnarray}
-\rho(x, y) &=& \left\{
-\begin{array}{lr}
-\frac{2M}{\pi v^2}\left(1 - \frac{r^2}{v^2}\right), & r \leq v\\
-0, & \textnormal{otherwise}
-\end{array}
-\right.
-\end{eqnarray}
-which is the same as the surface brightness profile of a source blob.
-The deflection angles for a single blob are:
-\begin{eqnarray}
-\alpha_x(x, y) &=&
-\left\{
-\begin{array}{lr}
-\left(2 - r^2/v^2\right)\frac{Mx}{\pi v^2}, & r \leq v\\
-\frac{Mx}{\pi r^2}, & \textnormal{otherwise}
-\end{array}
-\right.\\
-\alpha_y(x, y) &=&
-\left\{
-\begin{array}{lr}
-\left(2 - r^2/v^2\right)\frac{My}{\pi v^2}, & r \leq v\\
-\frac{My}{\pi r^2}, & \textnormal{otherwise}
-\end{array}
-\right.
-\end{eqnarray}
-where $r=\sqrt{x^2 + y^2}$. These do not depend on any
-{\revisions computationally expensive} functions such
-as square roots or exponentials.
-For $N$ such blobs the deflection angles are
-summed over all blobs. Therefore the lens can be entirely described by
-the following parameters:
-
-\begin{eqnarray}
-\left\{
-\boldsymbol{\theta}_{\rm SIE},
-N_{\rm lens}, \left\{\boldsymbol{\theta}^{\rm lens}_i\right\}_{i=1}^N
-\right\}
-\end{eqnarray}
-where $\boldsymbol{\theta}^{\rm lens}_i$ denotes the parameters for lens blob $i$:
-\begin{eqnarray}
-\boldsymbol{\theta}^{\rm lens}_i &=& \left\{x_i^{\rm lens}, y_i^{\rm lens}, M_i, v_i
-\right\},
-\end{eqnarray}
-and $\boldsymbol{\theta}_{\rm SIE}$ describes the parameters for the SIE+$\gamma$
-component:
-\begin{eqnarray}
-\boldsymbol{\theta}_{\rm SIE} = \left\{
-b, q, x_c^{\rm SIE}, y_c^{\rm SIE}, \theta, \gamma, \theta_\gamma
-\right\}.
-\end{eqnarray}
-
-Since the model is not of fixed dimension (the number of source and lens
-``blobs'' is unknown), we used a trans-dimensional MCMC sampler based on
-reversible jump MCMC \citep{green}. This framework has been used successfully
-in many astronomical inference problems \citep[e.g.][]{jones, renate}.
-We implemented the MCMC using the
-{\tt RJObject} software \citep{rjobject}, a C++ library for implementing trans-dimensional MCMC with hierarchically-specified priors when the model is
-a ``mixture model'' or similar, as is the case here.
-The {\tt RJObject} library uses the
-Diffusive Nested Sampling algorithm \citep[DNS;][]{dnest} for its sampling, but the
-trans-dimensionality is handled by the MCMC moves. Therefore, the marginal
-likelihood we obtain is one that involves a sum over the hypothesis space
-for $N_{\rm src}$ and $N_{\rm lens}$. In other words, we do not need
-separate runs with different trial values of $N_{\rm src}$ and $N_{\rm lens}$.
-Previous astronomical
-applications of {\tt RJObject} include \citet{magnetron}
-and~\citet{exoplanet}. Proposal moves for the parameters (positions and masses
-of the source and lens blobs), and birth/death moves to add or remove blobs
-to the source or lens, are handled internally by {\tt RJObject} and
-fit into the general framework described in \citet{rjobject}.
-
-\section{Prior Probability Distributions}\label{sec:priors}
-The prior probability distributions for all hyperparameters, parameters, and
-the data, are given in Table~\ref{tab:priors}, and a factorization of the
-joint distribution is displayed in Figure~\ref{fig:pgm}. With these priors,
-we aim to express a large degree of prior uncertainty (hence the liberal use
-of uniform, log-uniform, and Cauchy distributions). However, we also specify
-some priors hierarchically to allow (for example)
-blobs to cluster around a typical central
-position, rather than implying a high probability for substructure positions
-being spread uniformly (in a frequency sense) over the sky. We also applied
-hierarchical priors to the substructure masses (and source fluxes) so that, while
-the typical order of magnitude of the masses is unknown, the masses
-themselves are likely to be roughly the same order of magnitude. The
-hyperparameters of these distributions can also be interpreted as
-straightforward answers to questions about the substructure mass function.
-
-\begin{table*}
-\begin{tabular}{|l|l|l|}
-\hline
-Quantity	&	Meaning		& Prior\\
-\hline
-{\bf Numbers of Blobs}\\
-\hline
-$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
-$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
-\hline
-{\bf Source hyperparameters} ($\boldsymbol{\alpha}_{\rm src}$)\\
-\hline
-$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times${\tt imageWidth})\\
-$R_{\rm src}$   &	Typical distance of blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & LogUniform(0.01$\times${\tt imageWidth}, 10$\times${\tt imageWidth})\\
-$\mu_{\rm src}$ &	Typical flux of source blobs	& $\ln(\mu_{\rm src}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
-$W_{\rm max}^{\rm src}$ &		Maximum width of source blobs	& LogUniform(0.001$\times${\tt imageWidth}, {\tt imageWidth})\\
-$W_{\rm min}^{\rm src}$ &		Minimum width of source blobs	& Uniform(0, $W_{\rm max}^{\rm src}$)\\
-\hline
-{\bf Lens hyperparameters} ($\boldsymbol{\alpha}_{\rm lens}$)\\
-\hline
-$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times${\tt imageWidth})\\
-$R_{\rm lens}$  &	Typical distance of blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& LogUniform(0.01$\times${\tt imageWidth}, 10$\times${\tt imageWidth})\\
-$\mu_{\rm lens}$&	Typical mass of lens blobs	& $\ln(\mu_{\rm lens}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
-$W_{\rm max}^{\rm lens}$ &		Maximum width of lens blobs	& LogUniform(0.001$\times${\tt imageWidth}, {\tt imageWidth})\\
-$W_{\rm min}^{\rm lens}$ &		Minimum width of lens blobs	& Uniform(0, $W_{\rm max}^{\rm lens}$)\\
-\hline
-{\bf Source Blob Parameters} ($\boldsymbol{\theta}_i^{\rm src}$)\\
-\hline
-$(x_i^{\rm src}, y_i^{\rm src})$ & Blob position & Circular(location=$(x_c^{\rm src}, y_c^{\rm src})$, scale=$R_{\rm src}$)\\
-$A_i$  & Blob flux & Exponential(mean=$\mu_{\rm src}$)\\
-$w_i$  & Blob width & Uniform($W_{\rm min}^{\rm src}$, $W_{\rm max}^{\rm src}$)\\
-\hline
-{\bf Lens Blob Parameters} ($\boldsymbol{\theta}_i^{\rm lens}$)\\
-\hline
-$(x_i^{\rm lens}, y_i^{\rm lens})$ & Blob position & Circular(location=$(x_c^{\rm lens}, y_c^{\rm lens})$, scale=$R_{\rm lens}$) \\
-$M_i$  & Blob mass & Exponential(mean=$\mu_{\rm lens}$)\\
-$v_i$  & Blob width & Uniform($W_{\rm min}^{\rm lens}$, $W_{\rm max}^{\rm lens}$)\\
-\hline
-{\bf Smooth Lens Parameters} ($\boldsymbol{\theta}_{\rm SIE}$)\\
-\hline
-$b$ & SIE Einstein Radius & LogUniform(0.001$\times${\tt imageWidth}, {\tt imageWidth})\\
-$q$ & Axis ratio & Uniform(0, 0.95)\\
-$(x_c^{\rm SIE}, y_c^{\rm SIE})$ & Central position & iid Cauchy(location=$(0,0)$, scale=0.1$\times${\tt imageWidth})\\
-$\theta$ & Orientation angle & Uniform$(0, \pi)$\\
-$\gamma$ & External shear & Cauchy$(0, 0.05)T(0, \infty)$\\
-$\theta_\gamma$ & External shear angle & Uniform$(0, \pi)$\\
-\hline
-{\bf Noise Parameters} ($\boldsymbol{\sigma}$)\\
-\hline
-$\sigma_0$ & Constant component of noise variance & $\ln(\sigma_0) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
-$\sigma_1$ & Coefficient for variance increasing with flux &
-$\ln(\sigma_1) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
-\hline
-{\bf Data} ($\boldsymbol{D}$)\\
-\hline
-$D_{ij}$ & Pixel intensities & Normal$(m_{ij}, s_{ij}^2 + \sigma_0^2 + \sigma_1m_{ij})$
-\end{tabular}
-\caption{The prior distribution for all hyperparameters, parameters, and the
-data, in our model. Uniform$(a, b)$ is a uniform
-distribution between $a$ and $b$. LogUniform$(a, b)$ is a log-uniform
-distribution (with density $f(x) \propto 1/x$, sometimes erroneously called
-a Jeffreys prior) between $a$ and $b$. The notation $T(\alpha, \beta)$ after
-a distribution denotes truncation to the interval $[\alpha, \beta]$. The
-constant {\tt imageWidth} is the geometric mean of the image dimensions in
-the $x$ and $y$ directions.
-\label{tab:priors}}
-\end{table*}
-
-We assign somewhat informative (but heavy-tailed)
-Cauchy priors to the central positions of the source and the lens.
-One might object to the Cauchy priors
-for the central positions (and argue instead for gaussians) on the
-basis that they do not have rotational symmetry. However, the priors we
-are assigning are prior only to the values of the data pixel intensities only,
-and not other facts about the data, such as its dimensions in arc seconds, or its
-rectangular shape. Given these, there is no reason to insist on rotational
-symmetry. The Cauchy priors are intended to enhance the plausibility
-(relative to what a uniform prior would imply) that the
-lens and source are somewhere near the centre of the image, but in a cautious
-way.
-
-The ``circular'' conditional prior for the blob positions has the following
-density:
-\begin{eqnarray}
-\rho(x, y)\, dx \, dy &=&
-\frac{1}{2\pi W} \frac{1}{r}\exp\left(-\frac{r}{W}\right) \, dx \, dy
-\end{eqnarray}
-where $r = \sqrt{(x-x_c)^2 + (y-y_c)^2}$. This results from an exponential
-distribution (with expectation $W$) for the radial coordinate and a uniform distribution for the angular coordinate in plane polar coordinates. This was
-chosen (as opposed to a more ``obvious'' choice such as a normal distribution)
-for computational reasons: the {\tt RJObject} code requires a function to
-transform from Uniform(0, 1) distributions to this distribution and back
-(making use of cumulative distribution functions and their inverses), and
-the normal would have required the use of special functions for this.
-
-\begin{figure*}
-\includegraphics{pgm.pdf}
-\caption{A probabilistic graphical model (PGM) of the dependence structure
-of the prior information, produced using DAFT ({\tt www.daft-pgm.org}).
-The prior for the source and lens blob parameters are specified conditional
-on hyperparameters. The purpose of this is to induce dependence in the prior
-distribution for the blob parameters, implying (for example) that the mass of
-one blob is slightly informative about the mass of another, and that the
-locations might be clustered around a certain typical location.
-\label{fig:pgm}}
-\end{figure*}
-
-\subsection{Conditional prior for the data}
-The conditional prior for the data given the parameters
-is a product of independent gaussian distributions, one for each pixel.
-The mean of the gaussian is given by the ``mock'' noise-free image we would
-expect based on the parameters. The standard deviation of the gaussian is
-a combination of three terms; the first (denoted $s_{ij}$) is a ``noise map''
-which is loaded from a file, the second is an unknown constant $\sigma_0$
-which applies to the whole image, and the third is proportional to the
-square root of the mock image, with proportionality constant $\sigma_1$.
-
-This is usually called the ``sampling distribution'', or sometimes just the
-``likelihood''. However, sampling distribution is misleading since no
-physical frequency distribution exists which is being sampled from. The term
-likelihood is also usually used to refer to the scalar function of the parameters
-obtained when the data are known. For a discussion of the view that this
-object is really a prior distribution, see \citet[][pp. 33--35]{caticha}.
-
-It is common to provide a ``variance image'' to lens modelling software,
-which specifies the standard deviations used in the likelihood function.
-However, telescopes do not provide variance images. It also does not make
-sense to specify vague priors prior to the image pixel values but posterior to
-the variance image (which usually resembles the image itself, and therefore
-would be highly informative). Allowing the standard deviation of the gaussian in the
-likelihood to depend on the mock image brightness is a more principled way
-of modelling our actual inferential situation. Nevertheless, we allow for an
-input variance image as well, which can be used for ad-hoc masking of
-troublesome regions (such as unmodelled flux from other sources).
-
-\section{Computation}
-Computing the posterior distribution over the parameters of such a model
-requires that we can implement Markov Chain Monte Carlo (MCMC) over the space
-of possible sources and lenses.
-To compute the posterior distribution for the parameters
-(of which there are 24--464, depending on the values of $N_{\rm src}$ and
-$N_{\rm lens}$), we use Diffusive Nested Sampling \citep{dnest}, a form
-of Nested Sampling \citep{skilling} that uses the Metropolis algorithm
-to move around the parameter space.
-
-The proposal distributions for the blob parameters (both source and lens) are
-handled by the {\tt RJObject} library \citep{rjobject}. This includes
-birth and death proposals that increase or decrease either $N_{\rm src}$,
-or $N_{\rm lens}$, as well as proposals that move the blobs (in their parameter
-space) while keeping the number of blobs fixed. {\tt RJObject} also
-facilitates proposals that change the hyperparameters (either for the lens
-or the source) while keeping the actual blobs in place, as well as proposals
-that change the hyperparameters and shift all of the relevant blobs in
-so they are appropriate for the new values of the hyperparameters.
-
-Evaluating the likelihood function requires that we compute a ``mock'' image from
-the current setting of the parameters. This mock image is calculated using
-standard ray-tracing methods with a uniform grid of $n \times n$ rays
-fired per image pixel. However, certain kinds of proposals do not affect the
-image in any way, such as those which change the noise parameters. For efficiency
-we do not recompute the mock image in these cases.
-
-\section{{\revisions``Easy''} Simulated Data}
-To demonstrate the method, we generated a simulated dataset {\revisions where
-the lens was an SIE$+\gamma$ profile with a single additional substructure}.
-The image is shown in Figure~\ref{fig:image1}, and
-consists of 100 $\times$ 100 pixels. The point spread function (PSF) was compact and was
-defined on a 5 $\times$ 5 grid. The data was created by firing only one ray
-per pixel, and the inference was also carried out under the same level of
-approximation. Since the model assumptions are all correct for this image, the
-demonstration here is purely to illustrate the computational tractability of
-the problem, and the kind of outputs the method can produce.
-{\revisions
-The SIE$+\gamma$ parameters were, {\revisions to three significant figures},
-$\{b, q, x_c^{\rm SIE}, y_c^{\rm SIE}, \theta, \gamma, \theta_\gamma\}
-= \{5.25, 0.323, 0.191, -0.341, 0.833, 0.0322, 0.497\}$, where the length
-units in the image plane are arbitrary, and rotation angles are measured in
-radians. The single substructure is located at $(-2.57, 2.20)$, about halfway
-between the center and the upper left image.
-Its mass is 2.50 units, using the convention where the
-critical density is 1. For comparison, the SIE mass within its critical
-ellipse is $\pi b^2 = 86.6$ units.
-}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.5]{image1.pdf}
-\caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
-lens close to the center of the image, indicated by the white circle, plus a
-single substructure close to the top left image (indicated by a star symbol).
-The image was blurred by a PSF and had some noise added.
-In an arbitrary system of units, this image extends from -8 to 8 in the
-$x$ and $y$ directions.\label{fig:image1}}
-\end{center}
-\end{figure}
-
-We executed the code to generate 5,000 samples from the ``mixture of
-constrained priors'' distribution of DNS. Our thinning factor was $10^5$,
-so $5 \times 10^8$ MCMC iterations were actually performed, taking approximately
-48 hours on a modest desktop PC\footnote{The computer was purchased in 2012
-and has a second-generation intel i7 processor, and the process was run on
-8 threads.}. After resampling these samples to
-reflect the posterior distribution, we were left with {\revisions 500}
-(equally weighted) posterior samples.
-
-The posterior distributions for complex models, such as the mixture models used here, are often challenging and unintuitive to summarise. One effective way
-to visualise the uncertainty in the inferences is to play a movie where each
-frame is a sample from the posterior distribution. The degree to which the
-frames differ from each other conveys the uncertainty remaining after taking
-the data into account.
-
-For the purposes of a paper, static summaries are more convenient than movies.
-One useful summary is based on the concept of empirical measure.
-The {\it empirical measure} of the substructure positions is a function that
-takes the actual substructure positions $(x_i^{\rm lens}, y_i^{\rm lens})$ and
-produces a ``density function'' over two dimensions, composed of delta
-functions at the positions themselves:
-\begin{eqnarray}
-\left\{
-(x_i^{\rm lens}, y_i^{\rm lens})
-\right\}_{i=1}^{N_{\rm lens}}
-\Longrightarrow
-\sum_{i=1}^{N_{\rm lens}}
-\delta^2\left(x - x_i^{\rm lens}, y - y_i^{\rm lens}\right).
-\end{eqnarray}
-
-Intuitively, the empirical measure is a mathematical object that is like
-an ``infinite resolution histogram'', in this case a two dimensional histogram,
-of the substructure positions.
-Being a function of the actual substructure positions, the empirical measure
-is not available to us since we do not know those positions with certainty.
-However, we have samples from the posterior distribution for those positions,
-and can use these (trivially) to create samples from the posterior distribution
-for the empirical measure. We can also summarise this posterior, for example,
-by taking its expected value.
-
-The posterior expected value of the empirical measure is:
-{\revisions
-\begin{eqnarray}
-\int p(\boldsymbol{\theta} | \boldsymbol{D})
-\sum_{i=1}^{N_{\rm lens}}
-\delta^2\left(x - x_i^{\rm lens}, y - y_i^{\rm lens}\right)
-\, d\boldsymbol{\theta}
-\end{eqnarray}
-}
-where $\boldsymbol{\theta}$ denotes all parameters and hyperparameters
-(including the $N$s) and ``$\int \,d\boldsymbol{\theta}$'' is an integral and summation over the entire parameter space.
-
-Since we can approximate posterior expectations using Monte Carlo, we can
-obtain the expected value of the empirical measure using:
-{\revisions
-\begin{eqnarray}
-\frac{1}{n}
-\sum_{k=1}^n
-\sum_{i=1}^{N_{\rm lens}^k}
-\delta^2\left(x - x_{ik}^{\rm lens}, y - y_{ik}^{\rm lens}\right)
-\end{eqnarray}
-}
-where $n$ is the number of posterior samples. The resulting function is
-an ``image'' with a point mass wherever a substructure occurred. For
-visualisation purposes the image can be blurred, or calculated at a lower
-resolution by replacing the Dirac-delta function with a discrete version
-which returns a nonzero constant
-if a substructure appears in a pixel or zero otherwise.
-
-The masses of the smooth and substructure components of the lens are usually
-of interest. Since the total mass of an SIE lens is infinite, the question
-needs to be redefined, so we ask about the mass within some aperture of finite
-area. For an SIE, the mass (in dimensionless units based on the critical density)
-within the critical
-ellipse is simply $\pi b^2$. However, the blobs have finite total masses
-$\{M_i\}$. To obtain the posterior distribution for the lens masses, one must
-be clear about exactly which mass they are talking about, and many definitions
-are possible, although some might be more meaningful or well constrained than
-others.
-
-In the present paper we do not address the question of exactly which quantities
-related to the
-density profile of the lens are most scientifically interesting. Nevertheless,
-we can verify that the results of the inference do behave in understandable
-ways. For example, in Figure~\ref{fig:masses1},
-we plot the joint posterior distribution
-for the SIE mass within its critical ellipse and the total substructure mass
-over the entire domain. As one would expect, there is a strong dependence
-between these two quantities in the posterior distribution, as mass in the
-SIE can be traded off with mass in substructures to some extent, while
-the model remains (loosely speaking) ``consistent with the data''.
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.4]{masses1.pdf}
-\caption{The joint posterior distribution for the SIE mass (integrated within
-its critical ellipse, which is not the critical curve of the lens overall),
-and the total mass in substructures.\label{fig:masses1}}
-\end{center}
-\end{figure}
-
-The posterior distribution for $N_{\rm lens}$ is also clearly of interest, and
-is displayed in Figure~\ref{fig:N_lens1}. The prior for this parameter was
-uniform from 0 to 10 (inclusive), and the possibility $N=0$ has been
-(loosely speaking) ``ruled out'' by the image data. The true solution ($N=1$)
-has the highest probability. However, the possibilities with $N > 1$ are
-still fairly plausible, since it's possible that a very small substructure
-exists, and it's also possible that two substructures near each other could
-mimic the effect of one. The degree to which these possibilities are plausible
-is related to the choice of prior for the blob amplitudes and positions.
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.4]{N_lens1.pdf}
-\caption{The marginal posterior distribution for $N_{\rm lens}$, the
-number of substructures in the lens. The prior was uniform and the true
-value used to generate the data was 1. However, the data is only informative
-enough to suppress the probability of values above 1 slightly, since it
-is possible (given this data) that low mass substructures might exist somewhere,
-or that what we think is one substructure might actually be two close together,
-and other such possibilities.
-\label{fig:N_lens1}}
-\end{center}
-\end{figure}
-
-The estimated marginal likelihood of our model
-(averaged over all parameters including $N_{\rm lens}$ and $N_{\rm src}$)
-is {\revisions
-$\ln\left[p(\boldsymbol{D})\right] \approx -14141.4$, and
-the information (Kullback-Leibler divergence from the prior to the posterior)
-is $\mathcal{H} \approx 99.4$ nats}. The information represents the degree of
-compression of the posterior distribution with respect to the prior, and can
-be interpreted quite literally as how much was learned about the parameters from
-the data. It is also straightforward to estimate from Nested Sampling
-\citep{skilling}. Its definition is:
-\begin{eqnarray}
-\mathcal{H} = \int p(\boldsymbol{\theta} | \boldsymbol{D})
-\ln\left[\frac{p(\boldsymbol{\theta} | \boldsymbol{D})}{p(\boldsymbol{\theta})}\right]
-\, d\boldsymbol{\theta}
-\end{eqnarray}
-and we can build intuition about its meaning based on some simple examples. One
-such example is a uniform prior over a volume $V_0$ and a posterior which is
-uniform over a smaller volume $V_1$ contained within $V_0$. In this case
-$\mathcal{H} = \ln(V_0/V_1)$ nats. Therefore, a value of $\mathcal{H}=100$ nats
-implies the posterior distribution occupies roughly $e^{-100}$ of the prior
-volume.
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.4]{substructures1.pdf}
-\caption{The {\revisions `easy'} simulated data, with substructure positions overlaid (a
-Monte Carlo approximation to the posterior expectation of the empirical
-measure). The density of black points in any region is proportional to the
-expected number of substructures whose centers lie within that region. In this
-case, there is strong evidence for a substructure close to the top-left image
-(where one was actually placed).
-\label{fig:substructures1}}
-\end{center}
-\end{figure}
-
-{\revisions
-For the sampled parameter values representing the posterior distribution, there
-was no structure in the residuals (not shown), when normalised by the noise
-standard deviation in each pixel. This is unsurprising since the model
-assumptions are entirely correct for this dataset.
-}
-
-{\revisions
-\section{``Harder'' Simulated Data}
-To further test the algorithm, we created a ``harder'' simulated image, where
-the lens consisted of an SIE+$\gamma$ profile plus 10 additional substructures.
-The image is shown in Figure~\ref{fig:image2}. With the easy dataset, there
-was little hope of measuring the substructure mass function parameter
-$\mu_{\rm lens}$ since there was only a single substructure which would provide
-little information about $\mu_{\rm lens}$ (only constraining its general
-order of magnitude), even if its mass were measured perfectly.}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.5]{image2.pdf}
-\caption{{\revisions The `harder' simulated data, consisting of a more
-complex source profile, and a lens with an SIE+$\gamma$ (whose centre is
-indicated by a white circle) and ten substructures. Only five of the
-substructures (star symbols) occured within the square image boundary, but the other five still have an effect on the image.}
-\label{fig:image2}}
-\end{center}
-\end{figure}
-
-{\revisions As with the `easy' dataset,
-we generated 5,000 samples from the DNS target distribution and thinned
-by a factor of $10^5$, so $5 \times 10^8$ MCMC iterations were actually
-performed, taking approximately 60 hours. The slower runtime in this case
-was because $N_{\rm lens} = 10$, more CPU time was spent exploring parts of
-the hypothesis space where $N_{\rm lens}$ is high. The run resulted in 557
-equally-weighted posterior samples. The posterior distribution for the SIE
-mass and the total substructure mass is given in Figure~\ref{fig:masses2}.
-The samples can be viewed as a movie at
-{\tt www.youtube.com/watch?v=o3ppfKSk248}.
-}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.4]{masses2.pdf}
-\caption{{\revisions
-Same as Figure~\ref{fig:masses1}, but for the `harder' simulated dataset.
-}
-\label{fig:masses2}}
-\end{center}
-\end{figure}
-
-{\revisions
-To demonstrate the claim that we can infer something about the mass function
-of substructures directly from the image data, we have plotted the posterior
-distribution for $\mu_{\rm lens}$, the hyperparameter for the substructure
-masses, in Figure~\ref{fig:mu_lens}. The true value was 1, and the
-posterior distribution indicates a fairly wide uncertainty range that is
-at least consistent with the true value in some sense. Given that the image
-only contained a few substructures whose masses could be measured with any
-accuracy, the large uncertainty is not surprising.
-}
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.45]{mu_lens.pdf}
-\caption{{\revisions The posterior distribution for $\mu_{\rm lens}$, the
-hyperparameter which determines the prior expected value of substructure
-masses, given the `harder' simulated data. The true value (in arbitrary units)
-was 1, which is indicated by the vertical line.
-}
-\label{fig:mu_lens}}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.4]{N_lens2.pdf}
-\caption{{\revisions
-Same as Figure~\ref{fig:N_lens1}, but for the `harder' simulated dataset.
-The true number of substructures was 10, which also happens to be the posterior
-mode. Only five substructures were located within the domain of the image, but
-$N_{\rm lens} = 10$ is probable because the spread-out positions of the
-substructures imply that $R_{\rm lens}$ is probably large.
-}
-\label{fig:N_lens2}}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.4]{substructures2.pdf}
-\caption{{\revisions
-Same as Figure~\ref{fig:substructures1}, but for the `harder' simulated dataset.
-For all of the substructures located close to the ring, the positions were well
-constrained. There was weak evidence for some substructures that did not in
-fact exist.
-}
-\label{fig:substructures2}}
-\end{center}
-\end{figure}
-
-{\revisions
-The estimated marginal likelihood of our model, for the `harder' simulated data,
-is
-$\ln\left[p(\boldsymbol{D})\right] \approx -5671.9$, and
-the information (Kullback-Leibler divergence from the prior to the posterior)
-is $\mathcal{H} \approx 155.7$ nats. 
-As with the easy dataset, the standardised residuals of the sampled models
-resembled noise.
-}
-
-\section{The Cosmic Horseshoe}
-As a further demonstration the method, we apply it to the g-band data
-of the Cosmic Horseshoe J1004+4112 \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:image3}.
-For this system,
-more data is available (i and U band data, as well as more recent
-Hubble Space Telescope (HST) imaging), although the g-band image is the highest
-signal-to-noise of the INT images. The source redshift is $z_s=2.379$, and the
-lens is a massive luminous red galaxy at $z_l=0.4457$.
-Unfortunately our current implementation
-doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
-is quite slow when running on the larger HST image. Therefore this section
-should be considered a further demonstration of the technique, and not a
-thorough study of this system.
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.5]{image3.pdf}
-\caption{The g-band INT image of the Cosmic Horseshoe, with the lens galaxy
-subtracted.
-\label{fig:image3}}
-\end{center}
-\end{figure}
-
-We generated 5,000 samples from the DNS target distribution and thinned
-by a factor of $10^5$, so $5 \times 10^8$ MCMC iterations were actually
-performed, taking approximately 40 hours. After resampling, this resulted in
-{\revisions 718}
-equally weighted posterior samples. Although this image is smaller than the
-simulated data ($46 \times 46$ pixels), we fired $2 \times 2$ rays per pixel
-for greater accuracy.
-
-The joint posterior distribution for the SIE mass total substructure mass
-for the Cosmic Horseshoe is given in Figure~\ref{fig:masses3}. As with
-the simulated data (Figure~\ref{fig:masses1}), we see an expected negative
-correlation between these two quantities. However, the points are not as
-smoothly distributed in this case (we discuss this issue further
-in Section~\ref{sec:convergence}). An upper ``limit'' on the SIE mass, with
-95\% posterior probability, is $5.20 \times 10^{12}$ solar masses.
-The algorithm has also found
-some possibilities where the substructure mass is much greater than this. In
-these cases, the substructures are far from the image --- it is the environment
-that is being modelled.
-
-The posterior distribution for
-$N_{\rm lens}$ (Figure~\ref{fig:N_lens3})
-also shows some evidence for more than zero substructures.
-In particular, the prior probability for $N_{\rm lens} > 0$ was 10/11
-$\approx$ 0.91, whereas the posterior probability is approximately {\revisions 0.997}.
-This corresponds to a Bayes Factor of {\revisions about 300} in favour of
-$N_{\rm lens} > 0$ versus the alternative $N_{\rm lens} = 0$.
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.4]{masses3.pdf}
-\caption{{\revisions Same as Figure~\ref{fig:masses1}, but for the Cosmic Horseshoe.} The joint posterior distribution for the SIE mass (integrated within
-its critical ellipse, which is not the critical curve of the lens overall),
-and the total mass in substructures. The units are defined by the critical
-density, so that a mass of $\pi$ units would have an Einstein radius of one arcsecond. To calculate the masses in solar masses, we assumed a flat cosmology with
-$\Omega_m=0.3$, $\Omega_\Lambda=0.7$, and
-$H_0=70$ km/s/Mpc.
-\label{fig:masses3}}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.4]{N_lens3.pdf}
-\caption{{\revisions Same as Figure~\ref{fig:N_lens1}, but for the Cosmic Horseshoe.} The posterior distribution for the number of lens substructures
-in the Cosmic Horseshoe system. There is {\revisions moderate} evidence in favour of the hypothesis that $N_{\rm lens} \neq 0$.\label{fig:N_lens3}}
-\end{center}
-\end{figure}
-
-Despite weak evidence for the existence of substructure, when we examine the
-expected value of the empirical measure of substructure positions
-(Figure~\ref{fig:substructures3}) we find no consistency in their positions,
-unlike for the simulated data (Figure~\ref{fig:substructures1}). This situation
-is not uncommon. For example, \citet{exoplanet} found evidence for a large
-number of Keplerian signals in a time series, but the number of such signals
-with well constrained properties was much lower. Related to this, we can
-compute posterior probabilities for any hypothesis about the substructure
-masses.
-With 95\% probability the substructure mass is less than {\revisions 1.53$\times 10^{13}$} solar masses and with 75\% probability it is less than {\revisions 5.10$\times 10^{12}$} solar masses.
-As the Einstein ring itself implies a mass of about $5 \times 10^{12}$
-solar masses, these summaries are affected by the possibility of blobs outside
-the main Einstein ring.
-
-As with any inference, the results presented here may be sensitive to many of
-the input modelling assumptions, and a slightly different (yet still
-reasonable) set of choices might yield different results. For example, if
-the density profile of the lens was smooth but not of the SIE form, and the
-data were informative enough to show this, the current
-model would only be able to explain the data by adding substructures.
-Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within the SIE$+\gamma$ family.
-In fact, some of the posterior
-samples obtained contain massive substructures outside of the image, which
-could be modelling higher-order effects of the environment beyond what is
-captured by the simple external shear model. This is one way of violating
-the SIE$+\gamma$ assumption, and another is simply to have a different projected
-density profile.
-One way of further investigating this is to use a different family of
-smooth lens models and doing model selection based on the marginal likelihoods.
-Another option which we defer to future work is to implement a more flexible
-model (such as a mixture of concentric elliptical lenses). This
-result is consistent with that of \citet{2008MNRAS.388..384D}, who found a slight preference for an elliptical power law profile over the SIE
-(which is a specific case of an elliptical power law).
-
-Another potential inadequacy of our model is the assumption that the PSF is
-known. In practice, the PSF is often estimated from the image of nearby star(s),
-or from theoretical knowledge of the telescope (especially in the case of
-space based imaging). However, if the PSF is misspecified, or in fact varies
-across the image, this could induce subtle effects in the imaging which our
-current model could only explain using substructure.
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.4]{substructures3.pdf}
-\caption{{\revisions Same as Figure~\ref{fig:substructures1}, but for the Cosmic Horseshoe.} The positions of substructures encountered in the MCMC sampling
-for the Cosmic Horseshoe; technically a Monte Carlo approximation to the
-posterior expected value of the empirical measure of substructure
-positions. Unlike Figure~\ref{fig:substructures1}, for the Cosmic Horseshoe
-there is little consistency in the positions of the substructures.
-\label{fig:substructures3}}
-\end{center}
-\end{figure}
-
-The estimated marginal likelihood of our model
-is {\revisions
-$\ln\left[p(\boldsymbol{D})\right] \approx -6948.5$}, and
-the information (Kullback-Leibler divergence from the prior to the posterior)
-is {\revisions $\mathcal{H} \approx 123.1$} nats. 
-Three example models (lens and source) sampled from the posterior are shown
-in Figure~\ref{fig:sources}. {\revisions
-The model was able to fit the data down to the noise level.
-}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.8]{sources.pdf}
-\caption{Three example sources, the density profile in substructures,
-and the corresponding lensed, blurred images,
-representative of the posterior distribution.
-The angular scales are 7.5 arcseconds for the sources and 15
-arcseconds for the images.
-\label{fig:sources}}
-\end{center}
-\end{figure*}
-
-\subsection{Reproducibility of the results}\label{sec:convergence}
-The ``effective sample size'' returned by DNS, which we have described as the
-number of posterior samples, takes into account the fact DNS's target
-distribution is not the posterior. However, it does not take autocorrelation
-into account, and thus can present an optimistic picture of the accuracy of
-any Monte Carlo approximations to posterior quantities. Most standard diagnostic
-techniques used in MCMC can be applied here. The simplest of these is a
-check of reproducibility. If different runs yield substantially different
-results, the MCMC output should be treated with caution. For example, in
-Figure~\ref{fig:masses3}, there is a correlation between the mass attributed
-to the SIE component and that attributed to substructures. However, the
-distribution also appears somewhat ``lumpy'' or multimodal. This may
-not be a feature of the actual posterior distribution, but could arise due to
-imperfect sampling. Whereas a standard Metropolis sampler would move around
-very slowly in the hypothesis space, DNS naturally spends a non-negligible fraction
-of the time sampling the prior. Therefore, a particle exploring the parameter
-space can ``forget'' its good-fitting position, move somewhere completely
-different, and find another good-fitting model in a different location. This
-is a natural feature of the algorithm (and is also present in related
-algorithms such as parallel tempering). Despite this, the patchy
-nature of Figure~\ref{fig:masses3} suggests that posterior exploration is
-still challenging in this problem.
-
-The results for the simulated data (Figure~\ref{fig:masses1})
-were less complex because of the definite existence of one substructure.
-Its mass and position provide some information about the hyperparameters
-$\boldsymbol{\alpha}_{\rm lens}$, restricting the probability that
-high mass substructures exist far from the image.
-
-\section{Conclusions}
-We have developed a trans-dimensional Bayesian approach motivated directly by
-the question of whether dark substructures exist in a lens galaxy, given image
-data. By making use of the Diffusive Nested Sampling algorithm \citep{dnest}
-and the {\tt RJObject} library \citep{rjobject}, we outsource the difficulties
-associated with choosing Metropolis proposals for a hierarchical model of
-non-fixed dimension. The model allows for source and lens ``blobs'' to appear
-as needed to explain the data. The prior for the blobs' properties is
-specified hierarchically, to more realistically model sensible prior beliefs,
-and to tie the model parameters directly to questions of scientific interest
-such as the mass function of substructures.
-
-As a proof of concept, we demonstrated the successful recovery of a single
-substructure from simulated data for which all of the model assumptions were
-true. We then applied the method to an image of the Cosmic Horseshoe system
-and found {\revisions moderate} evidence in favour of the existence of a substructure, or at
-the very least, a departure from a simple SIE+$\gamma$ lens profile. The
-main output of our method is a set of posterior samples, each representing
-a plausible scenario for the lens and the source given the data
-and the assumed prior information. These samples can be displayed as a movie,
-which is a very useful method for intuitively understanding the remaining
-uncertainty. Any posterior summaries of interest can be
-produced from the samples, but the interpretation of many of these summaries
-is not necessarily straightforward. We have suggested that the
-posterior expectation of the empirical measure of substructure positions is
-one of the most helpful summaries.
-
-The model assumptions used in this paper are fairly simple. In future work we
-intend to generalize the model to multi-band data, and extend the
-smooth lens model beyond the overly simplistic
-SIE+$\gamma$ assumption. Applications
-to other systems are also forthcoming, as well as variants on the model using
-different conditional priors for the substructure properties given the
-hyperparameters.
 
 \section*{Acknowledgements}
-It is a pleasure to thank Phil Marshall (Stanford), Tommaso Treu (UCLA),
-Ross Fadely (NYU), Alan Heavens (Edinburgh), {\revisions and the referee}
-for valuable discussion. Thomas Lumley (Auckland) also deserves credit for
-ending BJB's usage of the jet colormap.
+It is a pleasure to thank Matt Auger (Cambridge) for valuable discussion and
+providing the data. Barkana
+
 This work was funded by a Marsden Fast Start grant from the Royal Society of
@@
 \begin{thebibliography}{99}
-\bibitem[\protect\citeauthoryear{Alsing et al.}{2015}]{2015arXiv150507840A} 
-Alsing J., Heavens A., Jaffe A.~H., Kiessling A., Wandelt B., Hoffmann T., 
-2015, arXiv, arXiv:1505.07840
-
-\bibitem[\protect\citeauthoryear{Belokurov et 
-al.}{2007}]{belokurov} Belokurov V., et al., 2007, ApJ, 671, L9
-
-\bibitem[\protect\citeauthoryear{Birrer, Amara, 
-\& Refregier}{2015}]{2015arXiv150407629B} Birrer S., Amara A., Refregier A., 2015, arXiv, arXiv:1504.07629
-
-\bibitem[\protect\citeauthoryear{Brewer 
-\& Lewis}{2006}]{2006ApJ...637..608B} Brewer B.~J., Lewis G.~F., 2006, ApJ, 637, 608
-
-\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
-\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011,
-Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380
-
-\bibitem[\protect\citeauthoryear{Brewer et al.}{2011}]{2011MNRAS.412.2521B} 
-Brewer B.~J., Lewis G.~F., Belokurov V., Irwin M.~J., Bridges T.~J., Evans 
-N.~W., 2011, MNRAS, 412, 2521
-
-\bibitem[\protect\citeauthoryear{Brewer}{2014}]{rjobject} Brewer, B. J., 2014,
-preprint. ArXiv: 1411.3921
-
-\bibitem[\protect\citeauthoryear{Brewer 
-\& Donovan}{2015}]{exoplanet} Brewer B.~J., Donovan C.~P., 2015, MNRAS, 448, 3206
-
-\bibitem[Caticha(2008)]{caticha} Caticha, A.\ 2008.\ Lectures 
-on Probability, Entropy, and Statistical Physics.\ ArXiv e-prints 
-arXiv:0808.0012.
-
-\bibitem[\protect\citeauthoryear{Coles, Read, 
-\& Saha}{2014}]{2014MNRAS.445.2181C} Coles J.~P., Read J.~I., Saha P., 2014, MNRAS, 445, 2181
-
-{\revisions
-\bibitem[\protect\citeauthoryear{Dehnen 
-\& Aly}{2012}]{2012MNRAS.425.1068D} Dehnen W., Aly H., 2012, MNRAS, 425, 1068
-}
-
-\bibitem[\protect\citeauthoryear{Dye et al.}{2008}]{2008MNRAS.388..384D} 
-Dye S., Evans N.~W., Belokurov V., Warren S.~J., Hewett P., 2008, MNRAS, 
-388, 384
-
-\bibitem[\protect\citeauthoryear{Fadely 
-\& Keeton}{2012}]{2012MNRAS.419..936F} Fadely R., Keeton C.~R., 2012, MNRAS, 419, 936
-
-\bibitem[\protect\citeauthoryear{Green}{1995}]{green}
-Green, P.~J., 1995, Reversible Jump Markov Chain Monte Carlo Computation and Bayesian Model Determination, Biometrika 82 (4): 711–732.
-
-\bibitem[\protect\citeauthoryear{Grillo et al.}{2015}]{grillo} 
-Grillo C., et al., 2015, ApJ, 800, 38
-
-\bibitem[\protect\citeauthoryear{Huppenkothen et 
-al.}{2015}]{magnetron} Huppenkothen D., et al., 2015, ApJ, 810, 
-66
-
-\bibitem[\protect\citeauthoryear{Jones, Kashyap, 
-\& van Dyk}{2014}]{jones} Jones D.~E., Kashyap V.~L., van Dyk D.~A., 2014, arXiv, arXiv:1411.7447
-
-\bibitem[\protect\citeauthoryear{Koopmans}{2005}]{koopmans} 
-Koopmans L.~V.~E., 2005, MNRAS, 363, 1136
-
-\bibitem[\protect\citeauthoryear{Kormann, Schneider, 
-\& Bartelmann}{1994}]{1994A&A...284..285K} Kormann R., Schneider P., Bartelmann M., 1994, A\&A, 284, 285
-
-\bibitem[\protect\citeauthoryear{Millar}{2011}]{millar}
-Millar, R.~B., Maximum likelihood estimation and inference: with examples in R, SAS and ADMB. Vol. 111. John Wiley \& Sons, 2011.
-
-\bibitem[\protect\citeauthoryear{O'Hagan and Forster}{2004}]{ohagan}
-O'Hagan, A., Forster,~J., 2004, Bayesian inference. London: Arnold.
-
-\bibitem[\protect\citeauthoryear{Pancoast, Brewer, 
-\& Treu}{2011}]{pancoast} Pancoast A., Brewer B.~J., Treu T., 2011, ApJ, 730, 139
-
-\bibitem[\protect\citeauthoryear{Schneider et 
-al.}{2015}]{2015ApJ...807...87S} Schneider M.~D., Hogg D.~W., Marshall 
-P.~J., Dawson W.~A., Meyers J., Bard D.~J., Lang D., 2015, ApJ, 807, 87
-
-\bibitem[\protect\citeauthoryear{Sivia \& Skilling}{2006}]{sivia} Sivia, 
-D.~ S., Skilling, J., 2006, Data Analysis: A Bayesian Tutorial, 2nd 
-Edition, Oxford University Press
-
-\bibitem[\protect\citeauthoryear{Skilling}{2006}]{skilling} Skilling, 
-J., 2006, ``Nested Sampling for General Bayesian Computation'', Bayesian 
-Analysis 4, pp. 833-860
-
-\bibitem[\protect\citeauthoryear{Suyu et al.}{2006}]{suyu} 
-Suyu S.~H., Marshall P.~J., Hobson M.~P., Blandford R.~D., 2006, MNRAS, 
-371, 983
-
-\bibitem[\protect\citeauthoryear{Suyu et al.}{2014}]{2014ApJ...788L..35S} 
-Suyu S.~H., et al., 2014, ApJ, 788, L35
-
-\bibitem[\protect\citeauthoryear{Suyu et al.}{2013}]{2013ApJ...766...70S} 
-Suyu S.~H., et al., 2013, ApJ, 766, 70
-
-\bibitem[\protect\citeauthoryear{Tagore 
-\& Jackson}{2015}]{2015arXiv150500198T} Tagore A.~S., Jackson N., 2015, arXiv, arXiv:1505.00198
-
-\bibitem[\protect\citeauthoryear{Treu}{2010}]{treu} Treu T., 2010, ARA\&A, 48, 87
-
-\bibitem[\protect\citeauthoryear{Umst{\"a}tter et 
-al.}{2005}]{renate} Umst{\"a}tter R., Christensen N., Hendry 
-M., Meyer R., Simha V., Veitch J., Vigeland S., Woan G., 2005, PhRvD, 72, 
-022001
-
-\bibitem[\protect\citeauthoryear{Vegetti 
-\& Koopmans}{2009}]{2009MNRAS.400.1583V} Vegetti S., Koopmans L.~V.~E., 2009, MNRAS, 400, 1583
-
-\bibitem[\protect\citeauthoryear{Vegetti et 
-al.}{2012}]{vegetti1} Vegetti S., Lagattuta D.~J., McKean J.~P., 
-Auger M.~W., Fassnacht C.~D., Koopmans L.~V.~E., 2012, Natur, 481, 341
-
-\bibitem[\protect\citeauthoryear{Vegetti, Czoske, 
-\& Koopmans}{2010}]{vegetti3} Vegetti S., Czoske O., Koopmans L.~V.~E., 2010, MNRAS, 407, 225
-
-\bibitem[\protect\citeauthoryear{Vegetti et 
-al.}{2010}]{vegetti2} Vegetti S., Koopmans L.~V.~E., Bolton A., 
-Treu T., Gavazzi R., 2010, MNRAS, 408, 1969
-
-\bibitem[\protect\citeauthoryear{Vegetti et 
-al.}{2014}]{2014MNRAS.442.2017V} Vegetti S., Koopmans L.~V.~E., Auger 
-M.~W., Treu T., Bolton A.~S., 2014, MNRAS, 442, 2017
-
-\bibitem[\protect\citeauthoryear{Warren 
-\& Dye}{2003}]{2003ApJ...590..673W} Warren S.~J., Dye S., 2003, ApJ, 590, 673
 \end{thebibliography}

### 2016-10-24 src/distances.py
Moved stuff around

@@ -1,0 +1,134 @@
+"""
+A module to compute cosmological distances, including:
+    comoving_distance (Dc)
+    angular_diameter_distance (Da)
+    luminosity_distance (Dl)
+    comoving_volume (volume)
+
+"""
+c = 299792458.
+G = 4.3e-6
+from math import pi
+import warnings
+warnings.warn("Default cosmology is Om=0.3,Ol=0.7,h=0.7,w=-1 and distance units are Mpc!",ImportWarning)
+
+class Distance:
+    def __init__(self,cosmo=[0.3,0.7,0.7]):
+        self.OMEGA_M = cosmo[0]
+        self.OMEGA_L = cosmo[1]
+        self.h = cosmo[2]
+        self.w = -1.
+        self.wpars = None
+        self.w_analytic = False
+        self.Dc = self.comoving_distance
+        self.Dt = self.comoving_transverse_distance
+        self.Dm = self.comoving_transverse_distance
+        self.Da = self.angular_diameter_distance
+        self.Dl = self.luminosity_distance
+        self.dm = self.distance_modulus
+        self.volume = self.comoving_volume
+
+    def set(self,cosmo):
+        self.OMEGA_M = cosmo[0]
+        self.OMEGA_L = cosmo[1]
+        self.h = cosmo[2]
+
+    def reset(self):
+        self.OMEGA_M = 0.3
+        self.OMEGA_L = 0.7
+        self.h = 0.7
+        self.w = -1.
+
+    def age(self,z):
+        from scipy import integrate
+        f = lambda zp,m,l,k : (m/zp+k+l*zp**2)**-0.5
+        om = self.OMEGA_M
+        ol = self.OMEGA_L
+        ok = 1.-om-ol
+        return (9.778/self.h)*integrate.romberg(f,1e-300,1/(1.+z),(om,ol,ok))
+
+    def comoving_distance(self,z1,z2=0.):
+        from scipy import integrate
+        if z2<z1:
+            z1,z2 = z2,z1
+        def fa(z):
+            if self.w_analytic==True:
+                return self.w(z,self.wpars)
+            from math import exp
+            wa = lambda z : (1.+self.w(z,self.wpars))/(1.+z)
[…]

### 2016-10-24 src/Lenses/BlobbySPEMD.cpp
Starting to write some stuff that will let you read in a lens from a file

@@ -222,3 +222,8 @@ void BlobbySPEMD::print(ostream& out) const
 	blobs.print(out); out<<' ';
 }
 
+void BlobbySPEMD::read(std::istream& in)
+{
+    in>>b>>q>>rc>>slope>>xc>>yc>>theta>>shear>>theta_shear;
+}
+

### 2016-10-24 src/Lenses/BlobbySPEMD.h

@@ -3,6 +3,7 @@
 
 #include <ostream>
 #include <exception>
+#include <istream>
 #include "../BasicUniform.h"
 #include "../Lens.h"
 #include "DNest4/code/RJObject/RJObject.h"
@@ -59,6 +60,9 @@ class BlobbySPEMD:public Lens
 
 		// If true, the most recent perturb only involved the blobs
 		bool get_blobs_flag() const { return blobs_flag; }
+
+        // Read from an input stream
+        void read(std::istream& in);
 };
 
 }

### 2016-10-24 src/MyModel.cpp

@@ -277,5 +277,32 @@ void MyModel::calculate_model_image()
 	}
 }
 
+void MyModel::read(std::istream& in)
+{
+    in>>sigma0>>sigma1>>psf_power;
+
+
+//	out<<' '<<sigma0<<' '<<sigma1<<' '<<psf_power<<' ';
+//	lens.print(out);
+//	source.print(out);
+
+//	// Make an image of the source (uses the ray resolution)
+//	const vector< vector<double> >& x = Data::get_instance().get_x_rays();
+//	const vector< vector<double> >& y = Data::get_instance().get_y_rays();
+//	for(size_t i=0; i<xs.size(); i++)
+//		for(size_t j=0; j<xs[i].size(); j++)
+//			out<<source.evaluate(x[i][j], y[i][j], false)<<' ';
+
+//	for(size_t i=0; i<xs.size(); i++)
+//		for(size_t j=0; j<xs[i].size(); j++)
+//			out<<surface_brightness[i][j]<<' ';
+
+//	for(size_t i=0; i<model_image.size(); i++)
+//		for(size_t j=0; j<model_image[i].size(); j++)
+//			out<<model_image[i][j]<<' ';
+
+
+}
+
 } // namespace Lensing2
 

### 2016-10-24 src/MyModel.h

@@ -4,6 +4,7 @@
 #include "Sources/Blobby.h"
 #include "Lenses/BlobbySPEMD.h"
 #include <vector>
+#include <istream>
 
 namespace Lensing2
 {
@@ -52,6 +53,9 @@ class MyModel
 		std::string description() const;
 
 		static void test();
+
+        // Read from an input stream
+        void read(std::istream& in);
 };
 
 } // namespace Lensing2

### 2016-10-24 src/BasicCircular.cpp
read functions

@@ -133,3 +133,10 @@ void BasicCircular::print(std::ostream& out) const
 	out<<xc<<' '<<yc<<' '<<width<<' '<<mu<<' '<<a<<' '<<b<<' ';
 }
 
+void BasicCircular::read(std::istream& in)
+{
+    in>>xc>>yc>>width>>mu>>a>>b;
+    k = a/b;
+}
+
+

### 2016-10-24 src/BasicCircular.h

@@ -2,6 +2,7 @@
 #define Lensing2_BasicCircular
 
 #include "DNest4/code/RJObject/ConditionalPriors/ConditionalPrior.h"
+#include <istream>
 
 class BasicCircular:public DNest4::ConditionalPrior
 {
@@ -32,6 +33,7 @@ class BasicCircular:public DNest4::ConditionalPrior
 		void to_uniform(std::vector<double>& vec) const;
 
 		void print(std::ostream& out) const;
+        void read(std::istream& in);
 };
 
 #endif

### 2016-10-24 src/BasicUniform.cpp

@@ -96,3 +96,9 @@ void BasicUniform::print(std::ostream& out) const
 	out<<mu<<' '<<a<<' '<<b<<' ';
 }
 
+void BasicUniform::read(std::istream& in)
+{
+    in>>mu>>a>>b;
+    k = a/b;
+}
+

### 2016-10-24 src/BasicUniform.h

@@ -2,6 +2,7 @@
 #define Lensing2_BasicUniform
 
 #include "DNest4/code/RJObject/ConditionalPriors/ConditionalPrior.h"
+#include <istream>
 
 class BasicUniform:public DNest4::ConditionalPrior
 {
@@ -28,6 +29,7 @@ class BasicUniform:public DNest4::ConditionalPrior
 		void to_uniform(std::vector<double>& vec) const;
 
 		void print(std::ostream& out) const;
+        void read(std::istream& in);
 };
 
 #endif

### 2016-10-24 src/Lenses/BlobbySPEMD.cpp

@@ -225,5 +225,6 @@ void BlobbySPEMD::print(ostream& out) const
 void BlobbySPEMD::read(std::istream& in)
 {
     in>>b>>q>>rc>>slope>>xc>>yc>>theta>>shear>>theta_shear;
+    blobs.read(in);
 }
 

### 2016-10-24 src/MyModel.cpp

@@ -280,28 +280,12 @@ void MyModel::calculate_model_image()
 void MyModel::read(std::istream& in)
 {
     in>>sigma0>>sigma1>>psf_power;
+    lens.read(in);
+    source.read(in);
 
-
-//	out<<' '<<sigma0<<' '<<sigma1<<' '<<psf_power<<' ';
-//	lens.print(out);
-//	source.print(out);
-
-//	// Make an image of the source (uses the ray resolution)
-//	const vector< vector<double> >& x = Data::get_instance().get_x_rays();
-//	const vector< vector<double> >& y = Data::get_instance().get_y_rays();
-//	for(size_t i=0; i<xs.size(); i++)
-//		for(size_t j=0; j<xs[i].size(); j++)
-//			out<<source.evaluate(x[i][j], y[i][j], false)<<' ';
-
-//	for(size_t i=0; i<xs.size(); i++)
-//		for(size_t j=0; j<xs[i].size(); j++)
-//			out<<surface_brightness[i][j]<<' ';
-
-//	for(size_t i=0; i<model_image.size(); i++)
-//		for(size_t j=0; j<model_image[i].size(); j++)
-//			out<<model_image[i][j]<<' ';
-
-
+	shoot_rays();
+	calculate_surface_brightness();
+	calculate_model_image();
 }
 
 } // namespace Lensing2

### 2016-10-24 src/Sources/Blobby.cpp

@@ -57,5 +57,10 @@ void Blobby::print(ostream& out) const
 	blobs.print(out);
 }
 
+void Blobby::read(istream& in)
+{
+    blobs.read(in);
+}
+
 } // namespace Lensing2
 

### 2016-10-24 src/Sources/Blobby.h

@@ -23,6 +23,7 @@ class Blobby:public Source
 		void from_prior(DNest4::RNG& rng);
 		double perturb(DNest4::RNG& rng);
 		void print(std::ostream& out) const;
+        void read(std::istream& in);
 
         // Getter
 		const DNest4::RJObject<BasicCircular>& get_blobs() const

### 2016-10-24 src/Lenses/BlobbySPEMD.cpp
More informative prior such that the SPEMD takes the bulk of the mass

@@ -89,7 +89,12 @@ void BlobbySPEMD::alpha(double x, double y, double& ax, double& ay, bool update)
 
 void BlobbySPEMD::from_prior(RNG& rng)
 {
-	b = exp(log(1E-3) + log(1E3)*rng.rand())*scale;
+    while(true)
+    {
+	    b = rng.rand();
+        if(rng.rand() <= (b/scale))
+            break;
+    }
 	q = 0.05 + 0.95*rng.rand();
 
 	// Stuff derived from b and q
@@ -144,10 +149,10 @@ double BlobbySPEMD::perturb(RNG& rng)
 
 	if(which == 0)
 	{
-		b = log(b/scale);
-		b += log(1E3)*rng.randh();
-		b = mod(b - log(1E-3), log(1E3)) + log(1E-3);
-		b = scale*exp(b);
+        logH -= log(b/scale);
+		b += rng.randh();
+        DNest4::wrap(b, 0.0, scale);
+        logH += log(b/scale);
 
 		// Stuff derived from b and q
 		qq = q;

### 2016-10-24 src/BasicUniform.cpp
More informative prior for mu of lens blobs

@@ -18,10 +18,13 @@ BasicUniform::BasicUniform(double x_min, double x_max,
 
 void BasicUniform::from_prior(RNG& rng)
 {
-	mu = tan(M_PI*(0.97*rng.rand() - 0.485));
-	mu = exp(mu);
+    // mass \propto (einstein radius)^2
+    // Don't want ER > size
+    // =>
+    // Don't want mass > size^2
+	mu = exp(log(1E-6*size*size) + log(1E6)*rng.rand());
 
-	b = exp(log(1E-3*size) + log(1E3)*rng.rand());
+	b = exp(log(0.001*size) + log(300.0)*rng.rand());
 	k = rng.rand();
 	a = k*b;
 }
@@ -34,17 +37,15 @@ double BasicUniform::perturb_hyperparameters(RNG& rng)
 	if(which == 0)
 	{
 		mu = log(mu);
-		mu = (atan(mu)/M_PI + 0.485)/0.97;
-		mu += rng.randh();
-		wrap(mu, 0., 1.);
-		mu = tan(M_PI*(0.97*mu - 0.485));
+		mu += log(1E6)*rng.randh();
+        DNest4::wrap(mu, log(1E-6*size*size), log(size*size));
 		mu = exp(mu);
 	}
 	else if(which == 1)
 	{
 		b = log(b);
-		b += log(1E3)*pow(10., 1.5 - 6.*rng.rand())*rng.randn();
-		b = mod(b - log(1E-3*size), log(1E3)) + log(1E-3*size);
+		b += log(300.0)*rng.randh();
+        wrap(b, log(0.001*size), log(0.3*size));
 		b = exp(b);
 		a = k*b;
 	}

### 2016-10-25 src/display.py
bugfix

@@ -135,7 +135,7 @@ show()
 figure(3)
 rc("font", size=16, family="serif", serif="Computer Sans")
 rc("text", usetex=True)
-plot(output[:,3], mass_units*output[:,121:171].sum(axis=1),\
+plot(output[:,3], mass_units*output[:,118:168].sum(axis=1),\
 					'ko', markersize=5, alpha=0.2)
 xlabel('SPEMD Einstein Radius')
 ylabel('Total substructure mass')

### 2016-10-25 src/loadrow.cpp
loadrow program

@@ -1,0 +1,43 @@
+#include <iostream>
+#include <fstream>
+#include "MyModel.h"
+#include "Data.h"
+
+/*
+* Loads a model from posterior_sample.txt and prints it to screen again.
+*/
+
+int main(int argc, char** argv)
+{
+    if(argc <= 1)
+    {
+        std::cerr<<"Usage: loadrow <row_number>"<<std::endl;
+        return 0;
+    }
+
+	// Load some "data" --- this is needed!
+    Lensing2::Data::get_instance().load("Data/mock_metadata.txt",
+                            "Data/harder_image.txt",
+                            "Data/mock_sigma.txt",
+                            "Data/mock_psf.txt");
+
+    // Model object to read into
+    Lensing2::MyModel m;
+
+    std::fstream fin("posterior_sample.txt", std::ios::in);
+    // Read past comment lines at the top of the file
+    while(fin.peek() == '#')
+        fin.ignore(10000000, '\n');
+
+    // Skip through to requested row
+    for(int i=0; i<atoi(argv[1]); ++i)
+        fin.ignore(10000000, '\n');
+
+    m.read(fin);
+    fin.close();
+
+    m.print(std::cout); std::cout<<std::endl;
+
+    return 0;
+}
+

### 2016-11-07 doc/Paper2/ms.tex
Moved stuff around
newer mnras template

--- 2015-11-29 Papers/Paper2/ms.tex
@@
-\documentclass[useAMS,usenatbib]{mn2e}
+% mnras_template.tex
+%
+% LaTeX template for creating an MNRAS paper
+%
+% v3.0 released 14 May 2015
+% (version numbers match those of mnras.cls)
+%
+% Copyright (C) Royal Astronomical Society 2015
+% Authors:
+% Keith T. Smith (Royal Astronomical Society)
 
-\voffset=-0.8in
+% Change log
+%
+% v3.0 May 2015
+%    Renamed to match the new package name
+%    Version number matches mnras.cls
+%    A few minor tweaks to wording
+% v1.0 September 2013
+%    Beta testing only - never publicly released
+%    First version: a simple (ish) template for creating an MNRAS paper
 
-% Packages:
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{xspace}
-%\usepackage{dsfont}
-\usepackage[utf8]{inputenc}
-\usepackage{float}
-\usepackage{color}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Basic setup. Most papers should leave these options alone.
+\documentclass[a4paper,fleqn,usenatbib]{mnras}
 
-\usepackage{epstopdf}
+% MNRAS is set in Times font. If you don't have this installed (most LaTeX
+% installations will be fine) or prefer the old Computer Modern fonts, comment
+% out the following line
+\usepackage{newtxtext,newtxmath}
+% Depending on your LaTeX fonts installation, you might get better results with one of these:
+%\usepackage{mathptmx}
+%\usepackage{txfonts}
 
-% For revisions
-\newcommand{\revisions}{}
-\newcommand{\revisionstwo}{}
+% Use vector fonts, so it zooms properly in on-screen viewing software
+% Don't change these lines unless you know what you are doing
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
 
+%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
+
+% Only include extra packages if you really need them. Common packages are:
+\usepackage{graphicx}	% Including figure files
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+
+\usepackage{microtype}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+
+% Please keep new commands to a minimum, and use \newcommand not \def to avoid
+% overwriting existing commands. Example:
+%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
+
+% Title of the paper, and the short title which is used in the headers.
+% Keep the title short and informative.
 \title[]
@@
   The University of Sydney, NSW 2006, Australia}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
+% These dates will be filled out by the publisher
 \date{}
 
+% Enter the current year, for the copyright statements etc.
+\pubyear{2016}
+
+% Don't change these lines
+\begin{document}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
 \maketitle
 
-\label{firstpage}
-
+% Abstract of the paper
 \begin{abstract}
-
 \end{abstract}
 
+% Select between one and six entries from the list of approved keywords.
+% Don't make up new ones.
 \begin{keywords}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
+Obscuration of a light source by foreground material is a common
+phenomenon in astronomy, and appears on scales ranging from
+{\bf blah blah blah...}
+
+When the obscuring material is in motion as observed from Earth,
+the observed brightness of an unresolved source will fluctuate with time
+as different parts of the source are blocked.
+
+In this paper we describe
+
+\section{Hypothesis Space}
+Our modelling assumptions are intended as a compromize between flexibility
+(so we can potentially infer the presence of complex structures)
+and computational tractability.
+
+Consider a coordinate system $(x,y)$ in units of the star's radius.
+The surface brightness profile
+$S(x, y)$ of the star uses the limb darkening profile
+\begin{align}
+S(x, y) &\propto
+    \left\{
+        \begin{array}{lr}
+            1 - b\left(1 - \sqrt{1 - (x^2 + y^2)}\right),   & x^2+y^2 \leq 1\\
+            0, & \textnormal{otherwise}
+        \end{array}
+    \right.
+\end{align}
+where $b$ is a limb darkening parameter.
+
+The density profile of the obscuring material is composed of a sum of
+$N$ circular ``blobs'' based on the blob profile
+used by \citet{lensing2}. A single blob of width $w$ and total ``mass'' $M$
+(the integral of the density profile),
+positioned at the origin, would have density profile
+\begin{align}
+\rho(x, y) &= \left\{
+        \begin{array}{lr}
+            \frac{2M}{\pi w^2}\left(1 - \frac{r^2}{w^2}\right), & r \leq w\\
+            0, & \textnormal{otherwise}
+        \end{array}\right.
+\end{align}
+where $r = \sqrt{x^2 + y^2}$. The total density profile of $N$ blobs,
+with masses $\{M_i\}$ and centers $\{(x_i, y_i)\}$, is
+\begin{align}
+\rho(x, y) &= \sum_{i=1}^N
+        \left\{
+        \begin{array}{lr}
+            \frac{2M_i}{\pi w_i^2}
+                \left(1 - \frac{r_i^2}{w_i^2}\right), & r_i \leq w_i\\
+            0, & \textnormal{otherwise}
+        \end{array}\right.
+\end{align}
+where $r_i = \sqrt{(x - x_i)^2 + (y - y_i)^2}$ is the distance of a point
+in the $x-y$ plane from the central position $(x_i, y_i)$ of blob $i$.
+
+If the blob density is taken as the optical depth, then the overall image
+of the star is
+\begin{align}
+I(x, y) &= S(x, y)e^{-\rho(x,y)}
+\end{align}
+and the observed total flux of the star is
+\begin{align}
+F &= \int_{-\infty}^{\infty}\int_{-\infty}^{\infty}
+        I(x, y) \, dx \, dy\\
+  &= \int_{-\infty}^{\infty}\int_{-\infty}^{\infty}
+        S(x, y)e^{-\rho(x,y)} \, dx \, dy.
+\end{align}
+We define the normalizing constant of the star's surface brightness profile
+such that the total flux of the star would be 1 in the absence of any
+obscuration.
+
+\subsection{Motion of the obscurers}
+As the obscuring blobs are in motion, we need to be able to calculate the
+flux of the star {\em as a function of time}. If the obscurers
+are initially centered around $(x_0, 0)$ and move to the right
+at speed $v$, the observed flux of the star at time $t > 0$ will be
+\begin{align}
+F(t) &= \int_{-\infty}^{\infty}\int_{-\infty}^{\infty}
+          S(x, y)e^{-\rho\left(x - (x_0 + vt), y\right)} \, dx \, dy.
+\end{align}
+which we recognize as the convolution of $S$ with $e^{-\rho}$, evaluated
+at $(x_0 + vt, 0)$:
+\begin{align}
+F(t) &= \left.\left(S * e^{-\rho}\right)\right|_{(x_0 + vt, 0)}.
+\end{align}
+This formulation is computationally convenient. Instead of having to
+simulate the motion of the blobs, we can instead convolve the image of
+the star with the image of the blobs, and evaluate the result at a series
+of points corresponding to the timestamps in the data.
+The convolution can be done using Fast Fourier Transforms.
+
+\section{Prior information}
+In this section we list the assumed prior information, that is,
+the joint prior distribution for the unknown hyperparameters
+$\boldsymbol{\alpha}$, parameters $\boldsymbol{\theta}$,
+and data $\boldsymbol{D}$. The joint prior distribution is usually factorized
+as follows:
+\begin{align}
+p(\boldsymbol{\alpha}, \boldsymbol{\theta}, \boldsymbol{D})
+    &= p(\boldsymbol{\alpha})p(\boldsymbol{\theta}|\boldsymbol{\alpha})
+        p(\boldsymbol{D} | \boldsymbol{\theta}, \boldsymbol{\alpha})\\
+    &= p(\boldsymbol{\alpha})p(\boldsymbol{\theta}|\boldsymbol{\alpha})
+        p(\boldsymbol{D} | \boldsymbol{\theta}).
+\end{align}
+
+\subsection{The limb darkening parameter}
+
+\section{Demonstration on `easy' simulated data}
+
+\section{Demonstration on `hard' simulated data}
+
+\section{Application to KIC*}
 
@@
 
-\begin{thebibliography}{99}
-\end{thebibliography}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+
+% The best way to enter references is to use BibTeX:
+
+\bibliographystyle{mnras}
+\bibliography{references} % if your bibtex file is called example.bib
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
+
+%\appendix
+%\section{Some extra material}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Don't change these lines
+\bsp	% typesetting comment
+\label{lastpage}
 \end{document}
+
+% End of mnras_template.tex

### 2016-11-07 doc/Paper2/ms.tex
Title

--- 2015-11-29 Papers/Paper2/ms.tex
@@
-\documentclass[useAMS,usenatbib]{mn2e}
+% mnras_template.tex
+%
+% LaTeX template for creating an MNRAS paper
+%
+% v3.0 released 14 May 2015
+% (version numbers match those of mnras.cls)
+%
+% Copyright (C) Royal Astronomical Society 2015
+% Authors:
+% Keith T. Smith (Royal Astronomical Society)
 
-\voffset=-0.8in
+% Change log
+%
+% v3.0 May 2015
+%    Renamed to match the new package name
+%    Version number matches mnras.cls
+%    A few minor tweaks to wording
+% v1.0 September 2013
+%    Beta testing only - never publicly released
+%    First version: a simple (ish) template for creating an MNRAS paper
 
-% Packages:
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{xspace}
-%\usepackage{dsfont}
-\usepackage[utf8]{inputenc}
-\usepackage{float}
-\usepackage{color}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Basic setup. Most papers should leave these options alone.
+\documentclass[a4paper,fleqn,usenatbib]{mnras}
 
-\usepackage{epstopdf}
+% MNRAS is set in Times font. If you don't have this installed (most LaTeX
+% installations will be fine) or prefer the old Computer Modern fonts, comment
+% out the following line
+\usepackage{newtxtext,newtxmath}
+% Depending on your LaTeX fonts installation, you might get better results with one of these:
+%\usepackage{mathptmx}
+%\usepackage{txfonts}
 
-% For revisions
-\newcommand{\revisions}{}
-\newcommand{\revisionstwo}{}
+% Use vector fonts, so it zooms properly in on-screen viewing software
+% Don't change these lines unless you know what you are doing
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
 
+%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
+
+% Only include extra packages if you really need them. Common packages are:
+\usepackage{graphicx}	% Including figure files
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+
+\usepackage{microtype}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+
+% Please keep new commands to a minimum, and use \newcommand not \def to avoid
+% overwriting existing commands. Example:
+%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
+
+% Title of the paper, and the short title which is used in the headers.
+% Keep the title short and informative.
 \title[]
-{The mass of the substructure in the ``Jackpot'' Gravitational Lens}
+{Constraints on the masses of substructures in $x$ lens galaxies}
 
-\author[Brewer, Huijser and Lewis]{%
+\author[Brewer and Lewis]{%
   Brendon~J.~Brewer$^{1}$\thanks{To whom correspondence should be addressed. Email: {\tt bj.brewer@auckland.ac.nz}},
-  David Huijser$^{1}$,
   Geraint F. Lewis$^2$
@@
 \end{keywords}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
 

### 2016-11-15 doc/Paper2/ms.tex
Prior table

@@
 
+\section{Prior Distribution}
+The joint prior distribution for the hyperparameters, parameters, and the
+data is summarised in Table~\ref{tab:priors}.
+
+\begin{table*}
+\begin{tabular}{|l|l|l|}
+\hline
+Quantity	&	Meaning		& Prior\\
+\hline
+{\bf Numbers of Blobs}\\
+\hline
+$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
+$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
+\hline
+{\bf Source hyperparameters} ($\boldsymbol{\alpha}_{\rm src}$)\\
+\hline
+$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times${\tt imageWidth})\\
+$R_{\rm src}$   &	Typical distance of blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & LogUniform(0.01$\times${\tt imageWidth}, 10$\times${\tt imageWidth})\\
+$\mu_{\rm src}$ &	Typical flux of source blobs	& $\ln(\mu_{\rm src}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
+$W_{\rm max}^{\rm src}$ &		Maximum width of source blobs	& LogUniform(0.001$\times${\tt imageWidth}, {\tt imageWidth})\\
+$W_{\rm min}^{\rm src}$ &		Minimum width of source blobs	& Uniform(0, $W_{\rm max}^{\rm src}$)\\
+\hline
+{\bf Lens hyperparameters} ($\boldsymbol{\alpha}_{\rm lens}$)\\
+\hline
+$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times${\tt imageWidth})\\
+$R_{\rm lens}$  &	Typical distance of blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& LogUniform(0.01$\times${\tt imageWidth}, 10$\times${\tt imageWidth})\\
+$\mu_{\rm lens}$&	Typical mass of lens blobs	& $\ln(\mu_{\rm lens}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
+$W_{\rm max}^{\rm lens}$ &		Maximum width of lens blobs	& LogUniform(0.001$\times${\tt imageWidth}, {\tt imageWidth})\\
+$W_{\rm min}^{\rm lens}$ &		Minimum width of lens blobs	& Uniform(0, $W_{\rm max}^{\rm lens}$)\\
+\hline
+{\bf Source Blob Parameters} ($\boldsymbol{\theta}_i^{\rm src}$)\\
+\hline
+$(x_i^{\rm src}, y_i^{\rm src})$ & Blob position & Circular(location=$(x_c^{\rm src}, y_c^{\rm src})$, scale=$R_{\rm src}$)\\
+$A_i$  & Blob flux & Exponential(mean=$\mu_{\rm src}$)\\
+$w_i$  & Blob width & Uniform($W_{\rm min}^{\rm src}$, $W_{\rm max}^{\rm src}$)\\
+\hline
+{\bf Lens Blob Parameters} ($\boldsymbol{\theta}_i^{\rm lens}$)\\
+\hline
+$(x_i^{\rm lens}, y_i^{\rm lens})$ & Blob position & Circular(location=$(x_c^{\rm lens}, y_c^{\rm lens})$, scale=$R_{\rm lens}$) \\
+$M_i$  & Blob mass & Exponential(mean=$\mu_{\rm lens}$)\\
+$v_i$  & Blob width & Uniform($W_{\rm min}^{\rm lens}$, $W_{\rm max}^{\rm lens}$)\\
+\hline
+{\bf Smooth Lens Parameters} ($\boldsymbol{\theta}_{\rm SIE}$)\\
+\hline
+$b$ & SIE Einstein Radius & LogUniform(0.001$\times${\tt imageWidth}, {\tt imageWidth})\\
+$q$ & Axis ratio & Uniform(0, 0.95)\\
+$(x_c^{\rm SIE}, y_c^{\rm SIE})$ & Central position & iid Cauchy(location=$(0,0)$, scale=0.1$\times${\tt imageWidth})\\
+$\theta$ & Orientation angle & Uniform$(0, \pi)$\\
+$\gamma$ & External shear & Cauchy$(0, 0.05)T(0, \infty)$\\
+$\theta_\gamma$ & External shear angle & Uniform$(0, \pi)$\\
+\hline
+{\bf Noise Parameters} ($\boldsymbol{\sigma}$)\\
+\hline
+$\sigma_0$ & Constant component of noise variance & $\ln(\sigma_0) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
+$\sigma_1$ & Coefficient for variance increasing with flux &
+$\ln(\sigma_1) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
+\hline
+{\bf Data} ($\boldsymbol{D}$)\\
+\hline
+$D_{ij}$ & Pixel intensities & Normal$(m_{ij}, s_{ij}^2 + \sigma_0^2 + \sigma_1m_{ij})$
+\end{tabular}
+\caption{The prior distribution for all hyperparameters, parameters, and the
+data, in our model. Uniform$(a, b)$ is a uniform
+distribution between $a$ and $b$. LogUniform$(a, b)$ is a log-uniform
+distribution (with density $f(x) \propto 1/x$, sometimes erroneously called
+a Jeffreys prior) between $a$ and $b$. The notation $T(\alpha, \beta)$ after
+a distribution denotes truncation to the interval $[\alpha, \beta]$. The
+constant {\tt imageWidth} is the geometric mean of the image dimensions in
+the $x$ and $y$ directions. {\color{blue} THIS WILL NEED TO BE UPDATED}
+\label{tab:priors}}
+\end{table*}
+
 \section*{Acknowledgements}

### 2016-11-16 doc/Paper2/ms.tex
Sections
Center for eResearch

@@
 
+\section{Einstein Ring 0047-2808}
+
+\section{The Jackpot}
+
+\section{Cosmic Horseshoe HST Image}
+
 \section*{Acknowledgements}
 It is a pleasure to thank Matt Auger (Cambridge) for valuable discussion and
-providing the data. Barkana
+providing the jackpot data. Barkana
 
-This work was funded by a Marsden Fast Start grant from the Royal Society of
-New Zealand.
+This work was supported by a Marsden Fast Start grant from the Royal Society of
+New Zealand. We also made use of resources provided by the Centre for
+eResearch at the University of Auckland.
 

### 2016-11-17 doc/Paper2/ms.tex
A tad of writing, and two references

@@
 \begin{abstract}
+We present inferences of the lens mass profile and source surface brightness
+profile for a selection of galaxy-galaxy gravitational lens systems,
+allowing for the possibility of substructures.
+In the ``jackpot'' system (SDSSJ0946+1006) we find X,
+
 \end{abstract}
@@
 \section{The Jackpot}
+\citep{sonnenfeldJackpot}
+\citep{vegettiJackpot}
 
@@
 
-This work was supported by a Marsden Fast Start grant from the Royal Society of
-New Zealand. We also made use of resources provided by the Centre for
-eResearch at the University of Auckland.
+This work was funded by a Marsden Fast Start grant from the Royal Society of
+New Zealand.
 

### 2016-11-18 doc/Paper2/ms.tex
self cite

@@
 
+\citet{lensing2} presented a model of the prior information used to perform
+inference from an image of a lensed galaxy. In this paper, we used a slightly
+modified model.
+
 \section{Prior Distribution}
@@
 
-This work was funded by a Marsden Fast Start grant from the Royal Society of
-New Zealand.
+This work was supported by a Marsden Fast Start grant from the Royal Society of
+New Zealand. We also made use of resources provided by the Centre for
+eResearch at the University of Auckland.
 
